### 2020-08-28 latex-article/article.tex
Added Latex Article and Slides templates

\documentclass[11pt]{article}

\title{Title}
% \subtitle{Subtitle}
\date{\today}
\author{Kyle Butts}
% \institue{}

\input{preamble.tex}

% Set-up Bibliography ------------------------------
\usepackage[
    citestyle= authoryear,
    style= authoryear, 
    natbib= true, 
    backend= biber
]{biblatex}
\addbibresource{references.bib}

\begin{document}

% --------------------------------------------------
% Title Page ---------------------------------------
\maketitle
\begin{abstract}
    Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\end{abstract}

\newpage

% --------------------------------------------------
% Paper --------------------------------------------
\section{Introduction}

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.\footnote{This is a test.}

See below for Theorem \ref{residue_thm}, for the regression specification Equation \ref{fe_reg}, and for Table \ref{summ_stat} \citep{Eigen1971}.

\section{Econometric Model}

\subsection{Principal Specification}

\begin{theorem}[Example Theorem]\label{residue_thm}
    This is an example theorem \[ 
        y = f(X) + \varepsilon 
    \]
\end{theorem}

\begin{equation}\label{fe_reg}
    y = f(X) + \varepsilon = X \beta + \psi_i + \nu_t + \varepsilon_{i,t} 
\end{equation}

\begin{table}[tp] \centering 
\caption{Summary Statistics}
\label{summ_stat}
    \begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
    \hline 
    \hline \\[-1.8ex] 
    Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\ 
    \hline \\[-1.8ex] 
    rating & 30 & 64.633 & 12.173 & 40 & 58.8 & 71.8 & 85 \\ 
    complaints & 30 & 66.600 & 13.315 & 37 & 58.5 & 77 & 90 \\ 
    privileges & 30 & 53.133 & 12.235 & 30 & 45 & 62.5 & 83 \\ 
    learning & 30 & 56.367 & 11.737 & 34 & 47 & 66.8 & 75 \\ 
    raises & 30 & 64.633 & 10.397 & 43 & 58.2 & 71 & 88 \\ 
    critical & 30 & 74.767 & 9.895 & 49 & 69.2 & 80 & 92 \\ 
    advance & 30 & 42.933 & 10.289 & 25 & 35 & 47.8 & 72 \\ 
    \hline \\[-1.8ex] 
    \end{tabular}

    \textit{Notes:} Using R base dataframe attitude \\ 
\end{table}

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\begin{table}[tb] \centering 
    \caption{Regression Results} 
    \label{reg1}

    \begin{tabular}{@{\extracolsep{5pt}}lcc} 
    \hline 
    \hline \\[-1.8ex] 
    & \multicolumn{2}{c}{\textit{Dependent variable: Overall Rating}} \\ 
    \cline{2-3} 
    \\[-1.8ex] & (1) & (2)\\ 
    \hline \\[-1.8ex] 
    Handling of Complaints & 0.692$^{***}$ (0.149) & 0.682$^{***}$ (0.129) \\ 
    No Special Privileges & $-$0.104 (0.135) & $-$0.103 (0.129) \\ 
    Opportunity to Learn & 0.249 (0.160) & 0.238$^{*}$ (0.139) \\ 
    Performance-Based Raises & $-$0.033 (0.202) &  \\ 
    Too Critical & 0.015 (0.147) &  \\ 
    Advancement & 11.011 (11.704) & 11.258 (7.318) \\ 
    \hline \\[-1.8ex] 
    Observations & 30 & 30 \\ 
    R$^{2}$ & 0.715 & 0.715 \\ 
    Adjusted R$^{2}$ & 0.656 & 0.682 \\ 
    \hline 
    \hline \\[-1.8ex] 
    \textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
    \end{tabular} 
\end{table}

% --------------------------------------------------
% Bibliography -------------------------------------
\newpage~\newpage
\printbibliography

\end{document}

### 2020-08-28 latex-slides/slides.tex
Added Latex Article and Slides templates

\documentclass{beamer}
% Metropolis Theme ---------------------------------
\usetheme{metropolis} % Use metropolis theme

% Title --------------------------------------------
\title{Title}
\subtitle{Subtitle}
\date{\today}
\author{Kyle Butts}
% \institue{}

% xcolor and define colors -------------------------
\usepackage{xcolor}
\definecolor{blue}{RGB}{0,114,178}
\definecolor{red}{HTML}{EB0E09}
\definecolor{yellow}{RGB}{240,228,66}
\definecolor{green}{RGB}{0,158,115}
\definecolor{maroon}{HTML}{AF3335}
\definecolor{purple}{HTML}{7E90B8}

% CU Boulder colors ---------------------------------
\definecolor{buff-gold}{HTML}{CFB87C}
\definecolor{buff-grey}{HTML}{565A5C}
\definecolor{buff-lightgrey}{HTML}{A2A4A3}
\definecolor{buff-black}{HTML}{000000}

% Beamer Options -------------------------------------

% Background
\definecolor{mybackground}{HTML}{ECECEC}
\setbeamercolor{background canvas}{bg= mybackground}

% \alert
\setbeamercolor{alerted text}{fg= buff-gold!80!black}

% Frame title
\setbeamercolor{frametitle}{bg= buff-black}
\setbeamercolor{title}{fg= buff-grey}

% Button 
\setbeamercolor{button}{bg= buff-gold}

% Enumitem ------------------------------------------
% Allow to remove indent w/ \begin{itemize}[leftmargin= *]
\usepackage{enumitem}
\setlist[itemize]{label= \textbullet}

% \begin{columns} -----------------------------------
\usepackage{multicol}

% Math Font -----------------------------------------
\usepackage[libertine]{newtxmath}

% ---------------------------------------------------
\begin{document}
\maketitle

\begin{frame}{Bullet Points}\label{main1}
    \begin{itemize}
        \item Can emphasize with \alert{the alert command}

        \item To include things in appendix, you must first label the slide and the appendix slide and then include a hyperlink:

        \hyperlink{appendix1}{\beamergotobutton{Appendix}}
    \end{itemize}
\end{frame}

\begin{frame}{Table}

    % Adjust Font Size to make table fit
    {\fontsize{8}{10}\selectfont

        \begin{table}[!htbp] \centering 
            \caption{Regression Results} 
            \label{}

            \begin{tabular}{@{\extracolsep{5pt}}lcc} 
            \hline 
            \hline \\[-1.8ex] 
            & \multicolumn{2}{c}{\textit{Dependent variable: Overall Rating}} \\ 
            \cline{2-3} 
            \\[-1.8ex] & (1) & (2)\\ 
            \hline \\[-1.8ex] 
            Handling of Complaints & 0.692$^{***}$ (0.149) & 0.682$^{***}$ (0.129) \\ 
            No Special Privileges & $-$0.104 (0.135) & $-$0.103 (0.129) \\ 
            Opportunity to Learn & 0.249 (0.160) & 0.238$^{*}$ (0.139) \\ 
            Performance-Based Raises & $-$0.033 (0.202) &  \\ 
            Too Critical & 0.015 (0.147) &  \\ 
            Advancement & 11.011 (11.704) & 11.258 (7.318) \\ 
            \hline \\[-1.8ex] 
            Observations & 30 & 30 \\ 
            R$^{2}$ & 0.715 & 0.715 \\ 
            Adjusted R$^{2}$ & 0.656 & 0.682 \\ 
            \hline 
            \hline \\[-1.8ex] 
            \textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
            \end{tabular} 
        \end{table}
    }

\end{frame}

% Use 16:9 ratio for figures
\begin{frame}{Figure}
    \begin{center}
        % \includegraphics[width= .95\linewidth]{fig1.png}
    \end{center}
\end{frame}

\begin{frame}{Figure with comments}
    \begin{columns}[T] % align columns
    \begin{column}{.62\textwidth}
        % \includegraphics[width= \linewidth]{fig2.png}
    \end{column}%

    \begin{column}{.38\textwidth}
        % Horizontal Bar
        {\color{buff-gold}\rule{\linewidth}{4pt}}

        \begin{itemize}[leftmargin=0cm]
            \item Point 1 about the figure to the left. Columns are a bit narrow
            \item Point 2
        \end{itemize}
    \end{column}%
    \end{columns}
\end{frame}

\begin{frame}{Two Columns general}
    \begin{columns}[T] % T = vertical align columns at the top
    \begin{column}{.50\textwidth}
        {\color{buff-gold}\rule{\linewidth}{4pt}}
        Column 1
    \end{column}

    \hfill

    \begin{column}{.50\textwidth}
        {\color{buff-gold}\rule{\linewidth}{4pt}}
        Column 2
    \end{column}
    \end{columns}
\end{frame}

%%% Appendix
\section{Appendix}

\begin{frame}{Appendix Slide}\label{appendix1}

    % Adjust Font Size to make table fit
    {\fontsize{9}{10}\selectfont

        \begin{table}[!htbp] \centering 
        \caption{Summary Statistics}
        \label{appendix_summ_stat}
            \begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
            \hline 
            \hline \\[-1.8ex] 
            Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\ 
            \hline \\[-1.8ex] 
            rating & 30 & 64.633 & 12.173 & 40 & 58.8 & 71.8 & 85 \\ 
            complaints & 30 & 66.600 & 13.315 & 37 & 58.5 & 77 & 90 \\ 
            privileges & 30 & 53.133 & 12.235 & 30 & 45 & 62.5 & 83 \\ 
            learning & 30 & 56.367 & 11.737 & 34 & 47 & 66.8 & 75 \\ 
            raises & 30 & 64.633 & 10.397 & 43 & 58.2 & 71 & 88 \\ 
            critical & 30 & 74.767 & 9.895 & 49 & 69.2 & 80 & 92 \\ 
            advance & 30 & 42.933 & 10.289 & 25 & 35 & 47.8 & 72 \\ 
            \hline \\[-1.8ex] 
            \end{tabular}

            \textit{Notes:} Using R base dataframe attitude \\ 
        \end{table}

    }

    \hyperlink{main1}{\beamergotobutton{Back to Main}}
\end{frame}
\end{document}

### 2020-08-28 r-snippets/snippets.R
Added RStudio Snippets

@@ -1,0 +1,24 @@
+snippet banner
+bannerCommenter::banner("${1:title}", bandChar = "-", fold= TRUE, rightSideHashes= 4, minHashes= 80)
+
+snippet endhead
+## -----------------------------------------------------------------------------
+
+snippet introblock
+`r paste0("## -----------------------------------------------------------------------------\n", 
+		  "## ", format(Sys.time(), "%Y-%m-%d"), "_\n## Kyle Butts, CU Boulder Economics \n",
+		  "## \n", "## \n", 
+		  "## -----------------------------------------------------------------------------", sep="")`
+
+snippet func
+function() {
+	# Display what the function is doing
+	usethis::ui_todo("")
+	cat("\n")
+	
+	
+	
+	# Display what the function successfully finished
+	cat("\n")
+	usethis::ui_done("")
+}	

### 2020-09-04 matlab-scheme/schemer_export.m
Added matlab schemes, 1 dark and 1 light

@@ -1,0 +1,677 @@
+%SCHEMER_EXPORT Export current MATLAB color scheme to text file
+%   If this is your first time using SCHEMER_EXPORT, please ensure you
+%   read the IMPORTANT NOTE at the bottom of the help section before using
+%   this function.
+%
+%   SCHEMER_EXPORT() with no input will prompt the user to locate a
+%   destination file via the GUI, and will save the current color scheme
+%   to this location. Please read the IMORTANT NOTE below
+%   before running this script or it may not work correctly.
+%   The MATLAB preference options which are exported are:
+%   - All settings in the Color pane of Preferences
+%   - All settings in the Color > Programming Tools pane
+%   - From Editor/Debugger > Display pane, the following:
+%      - Highlight current line (whether to highlight, and the colour)
+%      - Right-hand text limit (colour and thickness, whether on/off)
+%   The output format is the same as used in MATLAB's preferences file,
+%   which is found at FULLFILE(PREFDIR,'matlab.prf').
+%
+%   SCHEMER_EXPORT(FILENAME) exports the relevant MATLAB preferences
+%   to the file FILENAME.
+%
+%   SCHEMER_EXPORT(FILENAME, FLAG_MODE) controls which settings are output
+%   into the preference file FILENAME. Along with the colour settings for
+%   MATLAB syntax highlighting, one can also export the boolean preferences
+%   (such as whether cells and non-local variables, etc, should be coloured
+%   differently to the regular backgound and text); and one can also export
+%   the colour settings for syntax highlighting in other languages
+%   supported by MATLAB.
+%
+%   The FLAG_MODE settings available are:
+%     0 - neither booleans, nor additional languages are exported
+%     1 - boolean settings are exported, but not additional languages
+%     2 - additional language colours are exported, but not boolean settings
+%     3 - both booleans and additional languages are exported
+%
+%   By default FLAG_MODE is set to 1, so boolean settings will be
+%   exported, but the settings for syntax highlighting in additional
+%   languages will not be.
+%
+%   The colour settings for all MATLAB syntax highlighting will always be
+%   exported, even for syntax options which are currently disabled, and
+%   regardless of whether the boolean settings are being exported. This is
+%   because users loading your exported color scheme may want syntax
[…]

### 2020-09-04 matlab-scheme/schemer_import.m

@@ -1,0 +1,712 @@
+%SCHEMER_IMPORT Import a MATLAB color scheme
+%   SCHEMER_IMPORT() with no input will prompt the user to locate the
+%   color theme source file via the GUI.
+%
+%   SCHEMER_IMPORT(FILENAME) imports the color scheme options given in
+%   the file FILENAME.
+%
+%   SCHEMER_IMPORT(FILENAME, INCLUDEBOOLS) can control whether boolean
+%   preferences are included in import (default: FALSE). If INCLUDEBOOLS
+%   is set to true, boolean preference options such as whether to
+%   highlight autofixable errors, or to show variables with shared scope in
+%   a different colour will also be overridden, should they be set in the
+%   input file.
+%
+%   SCHEMER_IMPORT(INCLUDEBOOLS, FILENAME), with a boolean or numeric input
+%   followed by a string input, will also work as above because the input
+%   order is reversible.
+%
+%   SCHEMER_IMPORT(INCLUDEBOOLS) with a single boolean input will open the
+%   GUI to pick the file, and will load boolean preferences in accordance
+%   with INCLUDEBOOLS.
+%
+%   RET = SCHEMER_IMPORT(...) returns 1 on success, 0 on user
+%   cancellation at input file selection screen, -1 on fopen error, and -2
+%   on any other error.
+%
+%   NOTE:
+%   The file to import can either be a color scheme file as generated by
+%   SCHEMER_EXPORT, or an entire MATLAB preferences file such as the file
+%   you will find located at FULLFILE(PREFDIR,'matlab.prf'). This could be
+%   a MATLAB preferences file taken from a different computer or previous
+%   MATLAB installation. However, if you are importing from a matlab.prf
+%   file instead of a color scheme .prf file you should be aware that any
+%   colour preferences which have been left as the defaults on preference
+%   panels which the user has not visited on the origin system of the
+%   matlab.prf file will not be present in the file, and hence not updated
+%   on import.
+%
+%   The MATLAB preference options which will be overwritten by
+%   SCHEMER_IMPORT are:
+%   - All settings in the Color pane of Preferencs
+%   - All colour settings in the Color > Programming Tools pane, but no
+%     checkboxes
+%   - From Editor/Debugger > Display pane, the following:
+%      - Highlight current line (colour, but not whether to)
+%      - Right-hand text limit (colour and thickness, but not on/off)
+%   - From Editor/Debugger > Language, the syntax highlighting colours for
+%     each language.
+%
+%   Once the current colour preferences are overridden they cannot be
[…]

### 2020-09-27 ggplot_theme/examples.Rmd
Created theme_kyle.R with example plots

---
title: "Example Plots"
author: "Kyle F. Butts"
date: "9/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(gapminder)
library(sf)
```

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, prompt = FALSE, tidy = TRUE, comment = NA, message = FALSE, warning = FALSE)

library(tidyverse)
library(gapminder)

source("theme_kyle.R")
```

# Change over time

## Single line chart
```{r, tidy = FALSE, fig.cap = "Life expectancy in Argentina, 1952-2007 single line chart."}
df <- filter(gapminder, country == "Argentina") %>%
	mutate(year = as.Date(paste(year, "-01-01", sep = "", format = "%Y-%b-%d")))

ggplot(df, aes(x = year, y = lifeExp)) +
	geom_line(colour = "#fc6721", size = 1) +
	geom_point(colour = "#fc6721", size = 2) +
	scale_x_date(breaks = df$year, date_labels = "%Y") +
	scale_y_continuous(limits = c(0, 80)) +
	labs(
	title = "Life expectancy in Argentina, 1952-2007",
	subtitle = "A positive growth in years",
	caption = "Source: Gapminder.org  |  @traffordDataLab",
	x = "Year",
	y = "Age (years)"
	) +
	theme_kyle(title_pos = "center")
```

## Multiple line chart
```{r, tidy = FALSE, fig.cap = "Life expectancy in Argentina and Italy, 1952-2007 multple line chart."}
df <- filter(gapminder, country %in% c("Argentina", "Italy")) %>% 
	mutate(year = as.Date(paste(year, "-01-01", sep = "", format='%Y-%b-%d')))

ggplot(df, aes(x = year, y = gdpPercap, colour = country)) +
	geom_line(size = 1) +
	geom_point(size = 2) +
	scale_colour_manual(values = c("Argentina" = "#fc6721", "Italy" = "#E7B800")) + 
	scale_x_date(breaks = df$year, date_labels = "%Y") +
	scale_y_continuous(limits = c(0, 30000), labels = scales::dollar) +
	labs(
		title = "Life expectancy in Argentina and Italy",
		caption = "Source: Gapminder.org  |  @traffordDataLab",
		x = NULL,
		y = "GDP per capita ($)",
		colour = NULL
	) +
	theme_kyle(title_pos = "center")
```

## Bar chart (vertical)
```{r, tidy = FALSE, fig.cap = "GDP per capita in Egypt, 1952-2007 vertical bar chart."}
df <- filter(gapminder, country == "Egypt") %>% 
	mutate(year = as.Date(paste(year, "-01-01", sep = "", format='%Y-%b-%d')))

ggplot(df, aes(x = year, y = gdpPercap)) +
	geom_col(fill = "#fc6721", alpha = 0.8) +
	scale_x_date(breaks = df$year, date_labels = "%Y") +
	scale_y_continuous(expand = c(0, 0), labels = scales::dollar) + 
	labs(
		title = "GDP per capita in Egypt, 1952-2007", 
		caption = "Source: Gapminder.org  |  @traffordDataLab",
		x = NULL, 
		y = "GDP per capita ($)", 
		fill = NULL
	) + 
	theme_kyle(title_pos = "center") + 
	theme(panel.grid.major.x = element_blank())
```

## Stacked area chart
```{r, tidy = FALSE, fig.cap = "GDP per capita by country, 1952-2007 stacked area chart."}
df <- gapminder %>% 
	filter(country %in% c("France", "Germany", "Ireland", "Italy", "New Zealand")) %>% 
	mutate(year = as.Date(paste(year, "-01-01", sep = "", format='%Y-%b-%d')))

ggplot(df, aes(x = year, y = gdpPercap, fill = country)) +
	geom_area(color = "white") +
	scale_fill_paletteer_d("nord::aurora") + 
	scale_x_date(breaks = df$year, date_labels = "%Y") +
	scale_y_continuous(expand = c(0, 0), labels = scales::dollar) +
	labs(
		title = "GDP per capita by country, 1952-2007",
	   caption = "Source: Gapminder.org  |  @traffordDataLab",
	   x = NULL,
	   y = "GDP per capita ($)",
	   fill = NULL) +
	theme_kyle(title_pos = "center")
```

# Correlation

## Scatterplot
```{r, tidy = FALSE, fig.cap = "Life Expectancy and Income, 2007 scatterplot."}
ggplot(filter(gapminder, year == 2007), aes(x = gdpPercap, y = lifeExp)) +
	geom_point(colour = "#fc6721", fill = "white") +
	scale_x_log10(labels = scales::dollar) +
	labs(
		title = "Life Expectancy and Income, 2007",
		caption = "Source: Gapminder.org  |  @traffordDataLab",
		x = "GDP per capita ($)",
		y = "Age (years)"
	) +
	theme_kyle(title_pos = "center", slides = FALSE)
```

## Bubble chart

```{r, tidy = FALSE, fig.cap = "Life Expectancy and Income, 2007 bubble chart."}
ggplot(filter(gapminder, year == 2007), aes(x = gdpPercap, y = lifeExp)) +
	scale_x_log10(labels = scales::dollar) +
	geom_point(aes(size = pop, fill = continent), shape = 21, colour = "white", alpha = 0.6) +
	scale_fill_paletteer_d("nord::aurora") + 
	scale_size_continuous(range = c(1, 20)) +
	labs(
		title = "Life Expectancy and Income, 2007",
		caption = "Source: Gapminder.org  |  @traffordDataLab",
		x = "GDP per capita ($)",
		y = "Age (years)",
		fill = "Continent"
	) +
	guides(size = FALSE) +
	theme_kyle(title_pos = "center", slides = TRUE)
```

## Facet Wrap

```{r, tidy = FALSE, fig.cap = "Life Expectancy and Income, 2007 bubble chart."}
ggplot(
		gapminder %>% filter(year == 2007) %>% filter(continent %in% c("Americas", "Asia", "Europe")), 
		aes(x = gdpPercap, y = lifeExp)
	) +
	scale_x_log10(labels = scales::dollar) +
	geom_point(aes(size = pop, fill = continent), shape = 21, colour = "white", alpha = 0.6) +
	facet_wrap(~ continent) +
	scale_fill_paletteer_d("nord::aurora") + 
	scale_size_continuous(range = c(1, 20)) +
	labs(
		title = "Life expectancy and income, 2007",
		x = "GDP per capita ($)",
		y = "Age (years)",
		fill
	) +
	guides(size = FALSE) +
	theme_kyle(title_pos = "center") +
	theme(panel.grid.major.x = element_blank(),
	    legend.position = "bottom", 
	) + 
	theme(
		axis.text.x = element_text(angle = 30, hjust = 1),
		# panel.spacing = grid::unit(1, "lines")
	)
```

# Deviation

# Distribution

## Histogram
```{r, tidy = FALSE, fig.cap = "Life expectancy distribution, 2007 histogram."}
ggplot(filter(gapminder, year == 2007), aes(x = lifeExp)) +
  geom_histogram(binwidth = 1, fill = "#fc6721", colour = "white", alpha = 0.8) +
  scale_y_continuous(breaks = scales::pretty_breaks()) +
  labs(title = "Life expectancy distribution, 2007",
       caption = "Source: Gapminder.org  |  @traffordDataLab",
       x = "Age (years)",
       y = "") +
  theme_kyle(title_pos = "center")

```

## Density plot
```{r, tidy = FALSE, fig.cap = "Life expectancy distribution, 2007 density plot."}
ggplot(filter(gapminder, year == 2007), aes(x = lifeExp)) + 
  geom_density(aes(fill = continent), size = 0.1, alpha = 0.5) +
  labs(title = "",
       subtitle = "Life expectancy distribution, 2007",
       caption = "Source: Gapminder.org  |  @traffordDataLab",
       x = "Age (years)",
       y = "",
       fill = NULL) +
  theme_kyle(title_pos = "center") +
  theme(panel.grid.major.x = element_blank())
```

## Ridgeline plot
```{r, tidy = FALSE, fig.cap = "Life expectancy distribution, 2007 ridgeline plot."}
library(ggridges)
df <- gapminder %>% filter(year == 2007 & continent != "Oceania")
ggplot(df, aes(x = lifeExp, y = fct_rev(continent), fill = continent)) +
  geom_density_ridges(colour = "#bdbdbd", size = 0.5, alpha = 0.5) +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_discrete(expand = c(0,0)) +
  scale_fill_brewer(palette = "Set2") +
  labs(title = "Life expectancy distribution, 2007",
       caption = "Source: Gapminder.org  |  @traffordDataLab",
       x = "Age (years)",
       y = "") +
  theme_kyle(title_pos = "center") +
  theme(panel.grid.major.x = element_blank(),
        legend.position = "none")
```

# Spatial

## Choropleth map
```{r, tidy = FALSE, fig.cap = "Life expectancy, 2007 choropleth map."}

nc <- st_read(system.file("shape/nc.shp", package="sf"))

ggplot(nc) + 
	geom_sf(aes(fill = BIR79)) + 
	coord_sf(datum = NA) +
	labs(
		title = "NC Births in 1979"
	) +
	theme_kyle(slides = FALSE, legend.position = "bottom") +
	scale_fill_gradientn(
		colours = brewer.pal(5, "Oranges"),
		name = "Number of Births",
		guide = guide_colourbar(
			direction = "horizontal",
			barheight = unit(2, units = "mm"),
			barwidth = unit(50, units = "mm"),
			title.position = 'top',
			title.hjust = 0.5,
			label.hjust = 0.5
		)
	)

```

# Color Palettes

## Categorical
```{r}
ggplot(data = tibble(id = 1:6, xmin = id, xmax = id + 1, ymin = 0, ymax = 1)) + 
	geom_rect(aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = as.factor(id))) +
	scale_fill_manual(values = palette_kyle_categorical)
```

```{r}
ggplot(data = tibble(id = 1:6, xmin = id, xmax = id + 1, ymin = 0, ymax = 1)) + 
	geom_rect(aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = as.factor(id))) +
	scale_fill_manual(values = palette_kyle_scale)
```

### 2020-09-27 ggplot_theme/theme_kyle.R

@@ -1,0 +1,161 @@
+# Load Showtext and font Fira Sans
+if(!require("showtext")) {
+	print("Install the package `showtext`.")
+} else {
+	library("showtext")
+	showtext_auto()
+	font_add_google("Fira Sans", "fira_sans")
+	font_add_google("Merriweather", "merriweather")
+}
+
+
+#' @param title_pos either "center" or "left" to align title and subtitle center of left respectively
+#' @param axis_title_pos either "center" or "left" to align title and subtitle center or left/top respectively
+#' @param slides if TRUE, use background #ECECEC or not
+theme_kyle <- function(title_pos = "center", axis_title_pos = "left", slides = FALSE, ...) {
+	
+	title_hjust <- switch(title_pos, "center" = 0.5, "left" = 0)
+	axis_title_hjust_y <- switch(axis_title_pos, "center" = 0.5, "left" = 0.95)
+	axis_title_hjust_x <- switch(axis_title_pos, "center" = 0.5, "left" = 0)
+	plot_bg = if_else(slides, "#ECECEC", "transparent")
+	plot_grid = if_else(slides, "grey85", "grey92")
+	
+	theme_bw(
+		base_size = 14,
+		base_family = "fira_sans"
+	) + 
+	theme(
+		## Title and Subtitle --------------------------------------------------
+		plot.title = ggplot2::element_text(
+			# Font
+			family = "merriweather", face = "bold", size = 18, 
+			colour = "#454545", 
+			# Center title
+			hjust = title_hjust,
+			# Margins
+			margin = ggplot2::margin(b = 10)
+		),
+		plot.subtitle = ggplot2::element_text(
+			# Font
+			family = "merriweather", face = "italic", size = 12, 
+			colour = "#454545", 
+			# Center subtitle 
+			hjust = title_hjust,
+			# Margins
+			margin = ggplot2::margin(b = 5)
+		),
+		plot.title.position = "plot",
+		
+		## Caption -------------------------------------------------------------
+		plot.caption = ggplot2::element_text(
+			# Font
+			size = 10, colour = "#454545",
+			# Right-align caption
+			hjust = 1,
+			# Margins
+			margin = ggplot2::margin(t = 20)
+		),
+		plot.caption.position = "plot",
+		
+		## Axis ----------------------------------------------------------------
+		# Axis title
[…]

### 2020-10-07 ggplot_theme/theme_kyle.R
Added subtitle/title margin and ability to pass extra options that contradict theme_kyle options without error

@@ -12,13 +12,14 @@ if(!require("showtext")) {
 #' @param title_pos either "center" or "left" to align title and subtitle center of left respectively
 #' @param axis_title_pos either "center" or "left" to align title and subtitle center or left/top respectively
 #' @param slides if TRUE, use background #ECECEC or not
-theme_kyle <- function(title_pos = "center", axis_title_pos = "left", slides = FALSE, ...) {
+theme_kyle <- function(title_pos = "center", axis_title_pos = "left", slides = FALSE, has_subtitle = FALSE, ...) {
 	
 	title_hjust <- switch(title_pos, "center" = 0.5, "left" = 0)
-	axis_title_hjust_y <- switch(axis_title_pos, "center" = 0.5, "left" = 0.95)
-	axis_title_hjust_x <- switch(axis_title_pos, "center" = 0.5, "left" = 0)
+	axis_title_hjust_y <- switch(axis_title_pos, "center" = 0.5, "left" = 1.0)
+	axis_title_hjust_x <- switch(axis_title_pos, "center" = 0.5, "left" = 0.0)
 	plot_bg = if_else(slides, "#ECECEC", "transparent")
 	plot_grid = if_else(slides, "grey85", "grey92")
+	title_margin = if_else(has_subtitle, "4", "16")
 	
 	theme_bw(
 		base_size = 14,
@@ -33,7 +34,7 @@ theme_kyle <- function(title_pos = "center", axis_title_pos = "left", slides = F
 			# Center title
 			hjust = title_hjust,
 			# Margins
-			margin = ggplot2::margin(b = 10)
+			margin = ggplot2::margin(b = title_margin, unit = "pt")
 		),
 		plot.subtitle = ggplot2::element_text(
 			# Font
@@ -42,7 +43,7 @@ theme_kyle <- function(title_pos = "center", axis_title_pos = "left", slides = F
 			# Center subtitle 
 			hjust = title_hjust,
 			# Margins
-			margin = ggplot2::margin(b = 5)
+			margin = ggplot2::margin(b = 16, unit = "pt")
 		),
 		plot.title.position = "plot",
 		
@@ -61,7 +62,7 @@ theme_kyle <- function(title_pos = "center", axis_title_pos = "left", slides = F
 		# Axis title
 		axis.title = ggplot2::element_text(
 			# Font
-			size = 13, colour = "#454545", face = "italic"
+			size = 12, colour = "#454545", face = "italic"
 		),
 		# Axis Title x/y
 		axis.title.y = ggplot2::element_text(
[…]

### 2020-10-11 latex-article/article.tex
Added Notes in Table as an example
Updated slide colors

@@
 
-\begin{table}[tp] \centering 
+\begin{table}
+    \caption{Column Width Resize Box Table}
+    \centering
+
+    \begin{center}
+    \resizebox{\columnwidth}{!}{
+        \begin{tabular}{@{\extracolsep{5pt}}lcccccccc}
+            \hline 
+            & & & \multicolumn{2}{c}{Market Access} & \multicolumn{2}{c}{Urban Weekly Wage} & \multicolumn{2}{c}{Nonurban Weekly Wage} \\
+            \cline{4-5} \cline{6-7} \cline{8-9}
+            Year & N & \% Urban & Mean & SD & Mean & SD & Mean & SD \\ \hline
+
+            % \input{summary.tex}
+
+            1940 & 16,875,829 & 0.66 & 10,708.21 & 14,819.55 & 33.22 & 19.66 & 25.23 & 16.56\\
+            1950 & 67,790 & 0.69 & 23,166.06 & 26,600.85 & 70.05 & 32.70 & 58.27 & 29.24\\
+            1960 & 1,338,491 & 0.66 & 40,328.17 & 45,385.47 & 124.11 & 77.55 & 99.37 & 59.01\\
+            1970 & 277,951 & 0.75 & 65,373.07 & 68,048.88 & 205.42 & 137.80 & 165.61 & 104.49\\
+            1980 & 1,907,836 & 0.73 & 73,223.43 & 74,906.62 & 408.83 & 284.44 & 340.82 & 220.68\\
+            1990 & 2,257,874 & 0.68 & 224,312.50 & 168,933.04 & 711.77 & 574.58 & 550.26 & 392.90\\
+            2000 & 2,581,741 & 0.73 & 288,195.77 & 199,100.92 & 1,010.36 & 1,022.77 & 754.10 & 649.57\\
+            2005 & 530,283 & 0.76 & 283,709.53 & 196,293.00 & 1,211.38 & 1,203.62 & 881.47 & 722.94\\
+            2010 & 530,359 & 0.76 & 273,754.31 & 195,220.04 & 1,306.70 & 1,281.34 & 972.40 & 817.94\\
+            2015 & 559,168 & 0.76 & 252,832.47 & 164,905.15 & 1,447.26 & 1,545.33 & 1,080.38 & 1,011.25\\
+
+            \hline
+
+            \multicolumn{9}{p{.8\textwidth}}{\textit{Notes.} Weekly wage is reported in 2015 \$.}
+        \end{tabular}
+    }
+    \end{center}
+\end{table}
+
+\begin{table}[tp] 
     \caption{Summary Statistics}
     \label{summ_stat}
-    \begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
+    \centering
+
+    \begin{tabular}{lccccccc} 
         \hline 
         \hline \\[-1.8ex] 
-    Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St.
-Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\
+        Statistic & N & Mean & St. Dev. & Min & Pctl(25) & Pctl(75) & Max\\ 
         \hline \\[-1.8ex] 
@@
 
-\begin{table}[tb] \centering 
+\begin{table}[tb] 
     \caption{Regression Results} 
     \label{reg1}
+    \centering
 

### 2020-11-05 latex-article/article.tex
Update title and added a few colors
Updated table examples and switched to \adjustbox

--- 2020-08-28 latex-article/article.tex
@@
 
-\title{Title}
+\title{\color{navyblue} Example Paper}
 % \subtitle{Subtitle}
-\date{\today}
-\author{Kyle Butts}
+\author{\normalsize Kyle Butts\\{\footnotesize Univ. of Colorado, Boulder}}
+\date{\footnotesize\today}
 % \institue{}
@@
 Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur: $\sum X_i$.
 Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.\footnote{This is a test.}
@@
 \begin{equation}\label{fe_reg}
-    y = f(X) + \varepsilon = X \beta + \psi_i + \nu_t + \varepsilon_{i,t} 
+    y = f(X) + \varepsilon = X \beta + \psi_i + \nu_t + w_{i,t} + \varepsilon_{i,t} 
 \end{equation}
 
-\begin{table}[tp] \centering 
+\[ 
+    \mathbb{E} \left\{ Y_i(1) - Y_i(0) \right\} = \mathbb{P} (\tau \vert D_i = 1) 
+\]
+
+\begin{table}[ht]
+    \caption{Column Width Resize Box Table}
+    \centering
+
+    \begin{adjustbox}{width = 1.2\textwidth, center}
+        \begin{tabular}{@{\extracolsep{5pt}}lrrrrrrrr}
+            % Head
+            \hline 
+            & & & \multicolumn{2}{c}{Market Access} & \multicolumn{2}{c}{Urban Weekly Wage} & \multicolumn{2}{c}{Nonurban Weekly Wage} \\
+            \cline{4-5} \cline{6-7} \cline{8-9}
+            Year & \multicolumn{1}{c}{N} & \% Urban & Mean & SD & Mean & SD & Mean & SD \\ 
+            \hline
+
+            % Body
+            \input{summary.tex}
+
+            % Notes 
+            \hline
+            \multicolumn{9}{p{.8\textwidth}}{\textit{Notes.} Weekly wage is reported in 2015 \$.}
+        \end{tabular}
+    \end{adjustbox}
+\end{table}
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+\begin{table}[tb] 
     \caption{Summary Statistics}
     \label{summ_stat}
-    \begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
+
+    \begin{adjustbox}{center}
+        \begin{tabular}{@{\extracolsep{10pt}}lrrr} 
+            % Head
+            \hline \hline
+            & \multicolumn{2}{c}{\textbf{Population}} & \\
+            \cline{2-3}
+            \textbf{Country} & 2016 & 2017 & \textbf{Change (\%)} \\
+
+            % Body
             \hline
-    \hline \\[-1.8ex] 
-    Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St.
-Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\
-    \hline \\[-1.8ex] 
-    rating & 30 & 64.633 & 12.173 & 40 & 58.8 & 71.8 & 85 \\ 
-    complaints & 30 & 66.600 & 13.315 & 37 & 58.5 & 77 & 90 \\ 
-    privileges & 30 & 53.133 & 12.235 & 30 & 45 & 62.5 & 83 \\ 
-    learning & 30 & 56.367 & 11.737 & 34 & 47 & 66.8 & 75 \\ 
-    raises & 30 & 64.633 & 10.397 & 43 & 58.2 & 71 & 88 \\ 
-    critical & 30 & 74.767 & 9.895 & 49 & 69.2 & 80 & 92 \\ 
-    advance & 30 & 42.933 & 10.289 & 25 & 35 & 47.8 & 72 \\ 
-    \hline \\[-1.8ex] 
+            China & 1,403,500,365 & 1,409,517,397 & +0.4\% \\
+            India & 1,324,171,354 & 1,339,180,127 & +1.1\% \\
+            United States & 322,179,605 & 324,459,463 & +0.7\% \\
+            Indonesia & 261,115,456 & 263,991,379 & +1.1\% \\
+            Brazil & 207,652,865 & 209,288,278 & +0.8\% \\
+            Pakistan & 193,203,476 & 197,015,955 & +2.0\% \\
+            Nigeria & 185,989,640 & 190,886,311 & +2.6\% \\
+            Bangladesh & 162,951,560 & 164,669,751 & +1.1\% \\
+            Russia & 146,864,513 & 143,989,754 & -2.0\% \\
+            Mexico & 127,540,423 & 129,163,276 & +1.3\% \\
+
+            % Notes
+            \hline \hline
+            \multicolumn{4}{p{.6\textwidth}}{\textit{Source.} \href{https://en.wikipedia.org/wiki/List_of_countries_by_population_(United_Nations)}{Wikipedia}.}
         \end{tabular} 
-
-    \textit{Notes:} Using R base dataframe attitude \\ 
+    \end{adjustbox}
 \end{table}
@@
 
-\begin{table}[tb] \centering 
+\begin{table}[tb] 
     \caption{Regression Results} 
@@
 
-    \begin{tabular}{@{\extracolsep{5pt}}lcc} 
+    \begin{adjustbox}{center}
+        \begin{tabular}{@{\extracolsep{15pt}}lcc} 
+            % Head
+            \hline \hline
+            & \multicolumn{2}{c}{\textit{Dependent variable:} \ Overall Rating} \\ 
+            \cline{2-3} 
+            & (1) & (2) \\ 
             \hline
-    \hline \\[-1.8ex] 
-    & \multicolumn{2}{c}{\textit{Dependent variable: Overall Rating}} \\ 
-    \cline{2-3} 
-    \\[-1.8ex] & (1) & (2)\\ 
-    \hline \\[-1.8ex] 
+
+            % Body
             Handling of Complaints & 0.692$^{***}$ (0.149) & 0.682$^{***}$ (0.129) \\ 
@@
             Advancement & 11.011 (11.704) & 11.258 (7.318) \\ 
-    \hline \\[-1.8ex] 
+            \hline 
             Observations & 30 & 30 \\ 
-    R$^{2}$ & 0.715 & 0.715 \\ 
             Adjusted R$^{2}$ & 0.656 & 0.682 \\
-    \hline 
-    \hline \\[-1.8ex] 
-    \textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+
+            % Notes
+            \hline \hline
+            \multicolumn{3}{p{.8\textwidth}}{\textit{Notes.} $^{*}$ p$< 0.1$; $^{**}$ p$< 0.05$; $^{***}$ p$< 0.01$} \\ 
+            \multicolumn{3}{p{.8\textwidth}}{Using R base dataframe attitude.} 
         \end{tabular} 
+    \end{adjustbox}
 \end{table}

### 2020-11-05 latex-article/article.tex
Added tabularx and adjustbox examples

@@
 \begin{table}[ht]
-    \caption{Column Width Resize Box Table}
+    \caption{Table Too Wide (adjustbox)}
     \centering
@@
     \begin{adjustbox}{width = 1.2\textwidth, center}
-        \begin{tabular}{@{\extracolsep{5pt}}lrrrrrrrr}
+        \begin{tabular}{@{} @{\extracolsep{5pt}} 
+                lrrrrrrrr 
+            @{}}
             % Head
@@
             % Notes 
-            \hline
-            \multicolumn{9}{p{.8\textwidth}}{\textit{Notes.} Weekly wage is reported in 2015 \$.}
+            \hline \hline \\[-5mm]
+            \multicolumn{9}{p{.8\textwidth}}{\hspace{.1\textwidth}\textit{Notes.} Weekly wage is reported in 2015 \$.}
         \end{tabular}
@@
 \begin{table}[tb] 
-    \caption{Summary Statistics}
+    \caption{Summary Statistics (tabularx)}
     \label{summ_stat}
@@
     \begin{adjustbox}{center}
-        \begin{tabular}{@{\extracolsep{10pt}}lrrr} 
+        \begin{tabularx}{\textwidth}{@{} 
+                >{\hsize=.8\hsize}L R R >{\hsize=.7\hsize}R 
+            @{}}
             % Head
@@
             % Notes
-            \hline \hline
-            \multicolumn{4}{p{.6\textwidth}}{\textit{Source.} \href{https://en.wikipedia.org/wiki/List_of_countries_by_population_(United_Nations)}{Wikipedia}.}
-        \end{tabular} 
+            \hline \hline \\[-5mm]
+            \multicolumn{4}{@{} L}{\small\textit{Source.} \href{https://en.wikipedia.org/wiki/List_of_countries_by_population_(United_Nations)}{Wikipedia}.}
+
+        \end{tabularx}
     \end{adjustbox}
@@
 \begin{table}[tb] 
-    \caption{Regression Results} 
+    \caption{Regression Results (Custom tabularx widths)} 
     \label{reg1}
@@
     \begin{adjustbox}{center}
-        \begin{tabular}{@{\extracolsep{15pt}}lcc} 
+        \begin{tabularx}{\textwidth}{@{} 
+                >{\hsize=.6\hsize}L >{\hsize=.4\hsize}R >{\hsize=.4\hsize}R 
+            @{}} 
             % Head
@@
             % Notes
-            \hline \hline
-            \multicolumn{3}{p{.8\textwidth}}{\textit{Notes.} $^{*}$ p$< 0.1$; $^{**}$ p$< 0.05$; $^{***}$ p$< 0.01$} \\ 
-            \multicolumn{3}{p{.8\textwidth}}{Using R base dataframe attitude.} 
-        \end{tabular} 
+            \hline \hline \\[-5mm]
+            \multicolumn{3}{@{} p{\textwidth}}{\small \textit{Notes.} $^{*}$ p$< 0.1$; $^{**}$ p$< 0.05$; $^{***}$ p$< 0.01$} \\ 
+            \multicolumn{3}{@{} p{\textwidth}}{\small Using R base dataframe attitude.
+dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+}
+        \end{tabularx} 
     \end{adjustbox}

### 2020-11-05 r-nice_tables/example.R
Made r-nice_tables with regtex

@@ -1,0 +1,28 @@
+library(texreg)
+setwd("~/Documents/templates/r-nice_tables/")
+
+df <- tibble(
+	treat = 1:20 > 10,
+	z = runif(20, -1, 1),
+	y = 5 * treat + 3 * z + 2 + rnorm(20, 0, 1^2)
+)
+
+m1 <- lm(y ~ treat, data = df)
+m2 <- lm(y ~ treat + z, data = df)
+
+# screenreg(list(m1, m2))
+
+tex <- texreg::texreg(
+	list(m1, m2), 
+	# file = "table1.tex",
+	center = FALSE, table = FALSE, tabular = FALSE,
+	custom.note = "", #stars = NULL, 
+	custom.model.names = c("(1)", "(2)"),
+	custom.coef.names = c("Intercept", "Treated", "Covariate"),
+	include.rsquared = F
+)
+
+tex <- stringr::str_replace(tex, stringr::regex("^\\n\\\\hline\\n.+\\n\\\\hline"), "")
+tex <- stringr::str_replace(tex, stringr::regex("\\\\hline$"), "")
+
+cat(tex, file = "table1.tex")

### 2020-11-10 latex-article/article.tex
"Added C function for tabularx"
Appendix Numbering

@@
 
-% --------------------------------------------------
 % Title Page ---------------------------------------
@@
 
+% Paper --------------------------------------------
+
 % --------------------------------------------------
-% Paper --------------------------------------------
 \section{Introduction}
+% --------------------------------------------------
 
@@
 
-See below for Theorem \ref{residue_thm}, for the regression specification Equation \ref{fe_reg}, and for Table \ref{summ_stat} \citep{Eigen1971}.
+See below for Theorem \ref{residue_thm}, for the regression specification Equation \ref{fe_reg}, and for Table \ref{summ_stat}, appendix table \ref{reg1}, and citation \citep{Eigen1971}.
 
+% --------------------------------------------------
 \section{Econometric Model}
+% --------------------------------------------------
 
+% --------------------------------------------------
 \subsection{Principal Specification}
+% --------------------------------------------------
 
@@
             @{}}
+
             % Head
@@
 
+% --------------------------------------------------
+\newpage
+\printbibliography
+% --------------------------------------------------
+
+% --------------------------------------------------
+\newpage
+\appendix
+\numberwithin{equation}{section}
+\numberwithin{figure}{section}
+\numberwithin{table}{section}
+\renewcommand{\thefigure}{\Alph{section}\arabic{figure}}
+\renewcommand{\thetable}{\Alph{section}\arabic{table}}
+% --------------------------------------------------
+
+% --------------------------------------------------
+\section{Additional Results}
+% --------------------------------------------------
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+% --------------------------------------------------
+\subsection{Regression Results}
+% --------------------------------------------------
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
 \begin{table}[tb] 
@@
 
-% --------------------------------------------------
-% Bibliography -------------------------------------
-\newpage~\newpage
-\printbibliography
-
 \end{document}

### 2020-11-11 ggplot_theme/theme_kyle.R
Added base_size option, and all fonts scale relative to base_size

@@ -12,7 +12,7 @@ if(!require("showtext")) {
 #' @param title_pos either "center" or "left" to align title and subtitle center of left respectively
 #' @param axis_title_pos either "center" or "left" to align title and subtitle center or left/top respectively
 #' @param slides if TRUE, use background #ECECEC or not
-theme_kyle <- function(title_pos = "center", axis_title_pos = "left", slides = FALSE, has_subtitle = FALSE, ...) {
+theme_kyle <- function(title_pos = "center", axis_title_pos = "left", slides = FALSE, has_subtitle = FALSE, base_size = 14, ...) {
 	
 	title_hjust <- switch(title_pos, "center" = 0.5, "left" = 0)
 	axis_title_hjust_y <- switch(axis_title_pos, "center" = 0.5, "left" = 1.0)
@@ -22,7 +22,7 @@ theme_kyle <- function(title_pos = "center", axis_title_pos = "left", slides = F
 	title_margin = if_else(has_subtitle, "4", "16")
 	
 	theme_bw(
-		base_size = 14,
+		base_size = base_size,
 		base_family = "fira_sans"
 	) + 
 	theme(
@@ -95,7 +95,9 @@ theme_kyle <- function(title_pos = "center", axis_title_pos = "left", slides = F
 		# Legend title
 		legend.title = ggplot2::element_text(
 			# Font
-			size = 12, colour = "#454545"
+			size = 12, colour = "#454545",
+			# Line spacing
+			lineheight = 1.2,
 		),
 		# Legend labels
 		legend.text = ggplot2::element_text(

### 2020-11-11 ggplot_theme/theme_kyle.R
theme_kyle function only in this file

@@ -149,17 +149,3 @@ theme_kyle <- function(title_pos = "center", axis_title_pos = "left", slides = F
 		...
 	)
 }
-
-# Colors from nord
-palette_kyle_categorical <- c("#5E81AC", "#BF616A", "#A3BE8C", "#EBCB8B",  "#B48EAD", "#D08770") 
-
-ggplot(data = tibble(id = 1:6, xmin = id, xmax = id + 1, ymin = 0, ymax = 1)) + 
-	geom_rect(aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = as.factor(id))) +
-	scale_fill_manual(values = palette_kyle_categorical)
-
-# Colors from RColorBrewer
-palette_kyle_oneway <- c("#FEEBE2", "#FCC5C0", "#FA9FB5", "#F768A1", "#DD3497", "#AE017E", "#7A0177")
-
-ggplot(data = tibble(id = 1:6, xmin = id, xmax = id + 1, ymin = 0, ymax = 1)) + 
-	geom_rect(aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = as.factor(id))) +
-	scale_fill_manual(values = palette_kyle_oneway)

### 2020-11-11 ggplot_theme/theme_kyle.R
Added base_size option, and all fonts scale relative to base_size

@@ -25,126 +25,124 @@ theme_kyle <- function(title_pos = "center", axis_title_pos = "left", slides = F
 		base_size = base_size,
 		base_family = "fira_sans"
 	) + 
-	theme(
-		## Title and Subtitle --------------------------------------------------
-		plot.title = ggplot2::element_text(
-			# Font
-			family = "merriweather", face = "bold", size = 18, 
-			colour = "#454545", 
-			# Center title
-			hjust = title_hjust,
-			# Margins
-			margin = ggplot2::margin(b = title_margin, unit = "pt")
-		),
-		plot.subtitle = ggplot2::element_text(
-			# Font
-			family = "merriweather", face = "italic", size = 12, 
-			colour = "#454545", 
-			# Center subtitle 
-			hjust = title_hjust,
-			# Margins
-			margin = ggplot2::margin(b = 16, unit = "pt")
-		),
-		plot.title.position = "plot",
-		
-		## Caption -------------------------------------------------------------
-		plot.caption = ggplot2::element_text(
-			# Font
-			size = 10, colour = "#454545",
-			# Right-align caption
-			hjust = 1,
-			# Margins
-			margin = ggplot2::margin(t = 20)
-		),
-		plot.caption.position = "plot",
-		
-		## Axis ----------------------------------------------------------------
-		# Axis title
-		axis.title = ggplot2::element_text(
-			# Font
-			size = 12, colour = "#454545", face = "italic"
-		),
-		# Axis Title x/y
-		axis.title.y = ggplot2::element_text(
-			# Right-align y axis title
-			hjust = axis_title_hjust_y,
-			# Margins
-			margin = ggplot2::margin(r = 10)
-		),
-		axis.title.x = ggplot2::element_text(
-			# Left-align x axis title
-			hjust = axis_title_hjust_x,
-			# Margins
-			margin = ggplot2::margin(t = 10)
-		),
-		# Axis labels
-		axis.text = ggplot2::element_text(
-			# Font
-			size = 10, colour = "#212121"
-		),
-		# Axis Lines
-		axis.line = element_line(
-			colour = "grey40"
-		),
-		panel.grid = element_line(
-			colour = plot_grid
-		),
-		
-
-		## Legend -------------------------------------------------------------
-		# Legend title
-		legend.title = ggplot2::element_text(
-			# Font
-			size = 12, colour = "#454545",
-			# Line spacing
-			lineheight = 1.2,
-		),
[…]

### 2020-11-12 CU_research_computing/run.sh
Added CU Research Computing example bash script

@@ -1,0 +1,22 @@
+#!/bin/bash
+
+#SBATCH --nodes=1
+#SBATCH --ntasks=1
+#SBATCH --mem=48gb
+#SBATCH --time=00:01:00
+#SBATCH --job-name=x
+#SBATCH --output=x-%j.out
+
+cd /projects/kybu6659/templates/R/
+
+module purge
+
+echo "Loading Anaconda"
+source /curc/sw/anaconda3/latest
+echo "Loading environment"
+# conda activate rstudio
+conda activate r-spatial
+
+
+Rscript template.R
+

### 2020-11-17 latex-article/article.tex
Put citations in preamble

@@
 \title{\color{navyblue} Example Paper}
-% \subtitle{Subtitle}
 \author{\normalsize Kyle Butts\\{\footnotesize Univ. of Colorado, Boulder}}
 \date{\footnotesize\today}
-% \institue{}
 
+% Include Theme
 \input{preamble.tex}
 
-% Set-up Bibliography ------------------------------
-\usepackage[
-    citestyle= authoryear,
-    style= authoryear, 
-    natbib= true, 
-    backend= biber
-]{biblatex}
+% Set-up Bibliography
 \addbibresource{references.bib}
@@
 
-See below for Theorem \ref{residue_thm}, for the regression specification Equation \ref{fe_reg}, and for Table \ref{summ_stat}, appendix table \ref{reg1}, and citation \citep{Eigen1971}.
+See below for Theorem \ref{residue_thm}, for the regression specification Equation \ref{fe_reg}, and for Table \ref{summ_stat}, appendix table \ref{reg1}, and citation \citet{Eigen1971}.
 

### 2020-11-17 ggplot_theme/theme_kyle.R
Fixed relative size for title and subtitle

@@ -29,7 +29,7 @@ theme_kyle <- function(title_pos = "center", axis_title_pos = "left", slides = F
 			## Title and Subtitle --------------------------------------------------
 			plot.title = ggplot2::element_text(
 				# Font
-				family = "merriweather", face = "bold", size = 18, 
+				family = "merriweather", face = "bold", size = rel(1.285), 
 				colour = "#454545", 
 				# Center title
 				hjust = title_hjust,
@@ -38,7 +38,7 @@ theme_kyle <- function(title_pos = "center", axis_title_pos = "left", slides = F
 			),
 			plot.subtitle = ggplot2::element_text(
 				# Font
-				family = "merriweather", face = "italic", size = 12, 
+				family = "merriweather", face = "italic", size = rel(.86), 
 				colour = "#454545", 
 				# Center subtitle 
 				hjust = title_hjust,

### 2020-11-23 latex-article/article.tex
Landscape Table Support
Updated Margins
Added Three Part Table

@@
 
-% Title Page ---------------------------------------
+% Title Page -------------------------------------------------------------------
 \maketitle
@@
 
-% Paper --------------------------------------------
+% Paper ------------------------------------------------------------------------
 
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 \section{Introduction}
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 
@@
 
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 \section{Econometric Model}
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 \subsection{Principal Specification}
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 
@@
 
-    \begin{adjustbox}{width = 1.2\textwidth, center}
+    \begin{adjustbox}{width = 1.1\textwidth, center}
+        \begin{threeparttable}
             \begin{tabular}{@{} @{\extracolsep{5pt}} 
@@
                 % Head
-            \hline 
+                \toprule
                 & & & \multicolumn{2}{c}{Market Access} & \multicolumn{2}{c}{Urban Weekly Wage} & \multicolumn{2}{c}{Nonurban Weekly Wage} \\
-            \cline{4-5} \cline{6-7} \cline{8-9}
+                \cmidrule{4-5} \cmidrule{6-7} \cmidrule{8-9}
                 Year & \multicolumn{1}{c}{N} & \% Urban & Mean & SD & Mean & SD & Mean & SD \\ 
@@
 
-            % Notes 
-            \hline \hline \\[-5mm]
-            \multicolumn{9}{p{.8\textwidth}}{\hspace{.1\textwidth}\textit{Notes.} Weekly wage is reported in 2015 \$.}
+                \bottomrule
             \end{tabular}
-    \end{adjustbox}
-\end{table}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-\begin{table}[tb] 
-    \caption{Summary Statistics (tabularx)}
-    \label{summ_stat}
-
-    \begin{adjustbox}{center}
-        \begin{tabularx}{\textwidth}{@{} 
-                >{\hsize=.8\hsize}L R R >{\hsize=.7\hsize}R 
-            @{}}
-
-            % Head
-            \hline \hline
-            & \multicolumn{2}{c}{\textbf{Population}} & \\
-            \cline{2-3}
-            \textbf{Country} & 2016 & 2017 & \textbf{Change (\%)} \\
-
-            % Body
-            \hline
-            China & 1,403,500,365 & 1,409,517,397 & +0.4\% \\
-            India & 1,324,171,354 & 1,339,180,127 & +1.1\% \\
-            United States & 322,179,605 & 324,459,463 & +0.7\% \\
-            Indonesia & 261,115,456 & 263,991,379 & +1.1\% \\
-            Brazil & 207,652,865 & 209,288,278 & +0.8\% \\
-            Pakistan & 193,203,476 & 197,015,955 & +2.0\% \\
-            Nigeria & 185,989,640 & 190,886,311 & +2.6\% \\
-            Bangladesh & 162,951,560 & 164,669,751 & +1.1\% \\
-            Russia & 146,864,513 & 143,989,754 & -2.0\% \\
-            Mexico & 127,540,423 & 129,163,276 & +1.3\% \\
 
             % Notes 
-            \hline \hline \\[-5mm]
-            \multicolumn{4}{@{} L}{\small\textit{Source.} \href{https://en.wikipedia.org/wiki/List_of_countries_by_population_(United_Nations)}{Wikipedia}.}
-
-        \end{tabularx}
+            \begin{tablenotes}
+                \item \textit{Notes.} Weekly wage is reported in 2015 \$.
+            \end{tablenotes}
+        \end{threeparttable}    
     \end{adjustbox}
@@
 
-% --------------------------------------------------
+% in Preamble:
+% \usepackage{pdflscape} - rotates page left-side up in pdf
+% \usepackage{lscape} - does not rotate page, only figure/table
+
+\begin{landscape}
+%\thispagestyle{empty}
+\thispagestyle{lscaped}
+
+\begin{table}[h!]
+    \caption{Landscape Table}
+    \centering
+
+    \begin{adjustbox}{width = 1.2\textwidth, center}
+        \begin{threeparttable}
+        \begin{tabular}{@{} @{\extracolsep{5pt}} 
+                lrrrrrrrr 
+            @{}}
+            % Head
+            \toprule
+            & & & \multicolumn{2}{c}{Market Access} & \multicolumn{2}{c}{Urban Weekly Wage} & \multicolumn{2}{c}{Nonurban Weekly Wage} \\
+            \cmidrule{4-5} \cmidrule{6-7} \cmidrule{8-9}
+            Year & \multicolumn{1}{c}{N} & \% Urban & Mean & SD & Mean & SD & Mean & SD \\ 
+            \hline
+
+            % Body
+            \input{summary.tex}
+
+            \bottomrule
+        \end{tabular}
+
+        % Notes
+        \begin{tablenotes}\footnotesize
+            \item \textit{Notes.} Weekly wage is reported in 2015 \$.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor
+        \end{tablenotes}
+        \end{threeparttable}
+    \end{adjustbox}
+\end{table}
+\end{landscape}
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+\begin{table}[tb] 
+    \caption{Summary Statistics (tabularx)}
+    \label{summ_stat}
+
+    \begin{adjustbox}{center}
+        \begin{threeparttable}
+            \begin{tabularx}{\textwidth}{@{} 
+                    >{\hsize=.9\hsize}R >{\hsize=1.1\hsize}R >{\hsize=1.1\hsize}R >{\hsize=.9\hsize}R
+                @{}}
+
+                % Head
+                \toprule
+                & \multicolumn{2}{c}{\textbf{Population}} & \\
+                \cmidrule{2-3}
+                \textbf{Country} & 2016 & 2017 & \textbf{Change (\%)} \\
+
+                % Body
+                \hline
+                China & 1,403,500,365 & 1,409,517,397 & +0.4\% \\
+                India & 1,324,171,354 & 1,339,180,127 & +1.1\% \\
+                United States & 322,179,605 & 324,459,463 & +0.7\% \\
+                Indonesia & 261,115,456 & 263,991,379 & +1.1\% \\
+                Brazil & 207,652,865 & 209,288,278 & +0.8\% \\
+                Pakistan & 193,203,476 & 197,015,955 & +2.0\% \\
+                Nigeria & 185,989,640 & 190,886,311 & +2.6\% \\
+                Bangladesh & 162,951,560 & 164,669,751 & +1.1\% \\
+                Russia & 146,864,513 & 143,989,754 & -2.0\% \\
+                Mexico & 127,540,423 & 129,163,276 & +1.3\% \\
+
+                \bottomrule
+            \end{tabularx}
+
+            % Notes
+            \begin{tablenotes}\setlength\labelsep{0pt}\small
+                \item \textit{Source:} \href{https://en.wikipedia.org/wiki/List_of_countries_by_population_(United_Nations)}{Wikipedia}.
+            \end{tablenotes}
+        \end{threeparttable}
+    \end{adjustbox}
+\end{table}
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+% ------------------------------------------------------------------------------
 \newpage
-\printbibliography
-% --------------------------------------------------
+\printbibliography%
+% ------------------------------------------------------------------------------
 
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 \newpage
@@
 \renewcommand{\thetable}{\Alph{section}\arabic{table}}
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 \section{Additional Results}
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 
@@
 
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 \subsection{Regression Results}
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 
@@
             & \multicolumn{2}{c}{\textit{Dependent variable:} \ Overall Rating} \\ 
-            \cline{2-3} 
+            \cmidrule{2-3} 
             & (1) & (2) \\ 

### 2021-03-24 latex-slides/slides.tex
Added \imageframe to slides LaTex template
Added block example and Table of Contents when using section
Updated Slides
Add easy boxes

@@
-\documentclass{beamer}
+\documentclass[aspectratio=43]{beamer}
+% \documentclass[aspectratio=169]{beamer}
+
 % Metropolis Theme ---------------------------------
@@
 
-% xcolor and define colors -------------------------
-\usepackage{xcolor}
-\definecolor{blue}{RGB}{0,114,178}
-\definecolor{red}{HTML}{EB0E09}
-\definecolor{yellow}{RGB}{240,228,66}
-\definecolor{green}{RGB}{0,158,115}
-\definecolor{maroon}{HTML}{AF3335}
-\definecolor{purple}{HTML}{7E90B8}
+\input{preamble.tex}
 
-% CU Boulder colors ---------------------------------
-\definecolor{buff-gold}{HTML}{CFB87C}
-\definecolor{buff-grey}{HTML}{565A5C}
-\definecolor{buff-lightgrey}{HTML}{A2A4A3}
-\definecolor{buff-black}{HTML}{000000}
+% Set-up Bibliography ------------------------------
+\addbibresource{references.bib}
 
-% Beamer Options -------------------------------------
+\begin{document}
 
-% Background
-\definecolor{mybackground}{HTML}{ECECEC}
-\setbeamercolor{background canvas}{bg= mybackground}
+% --------------------------------------------------
+\maketitle
+% --------------------------------------------------
 
-% \alert
-\setbeamercolor{alerted text}{fg= buff-gold!80!black}
+% --------------------------------------------------
+\section{Common Items}
+% --------------------------------------------------
 
-% Frame title
-\setbeamercolor{frametitle}{bg= buff-black}
-\setbeamercolor{title}{fg= buff-grey}
-
-% Button 
-\setbeamercolor{button}{bg= buff-gold}
-
-% Enumitem ------------------------------------------
-% Allow to remove indent w/ \begin{itemize}[leftmargin= *]
-\usepackage{enumitem}
-\setlist[itemize]{label= \textbullet}
-
-% \begin{columns} -----------------------------------
-\usepackage{multicol}
-
-% Math Font -----------------------------------------
-\usepackage[libertine]{newtxmath}
-
-% ---------------------------------------------------
-\begin{document}
-\maketitle
-
-\begin{frame}{Bullet Points}\label{main1}
+\begin{frame}{Bullet Points \& Button}\label{main1}
     \begin{itemize}
@@
 
+\begin{frame}{Citations}
+    Topic 1: Spatial Frictions
+    \begin{citecolor}
+        [\citet{Fajgelbaum_Morales_Serrato_Zidar_2018}, \citet{Hsieh_Moretti_2019}, and \citet{Moretti_2011}]
+    \end{citecolor}
+
+    Topic 2: Blah 
+    \begin{citecolor}
+        [\citet{Suárez_Serrato_Zidar_2016}]
+    \end{citecolor}
+\end{frame}
+
+\begin{frame}{Blocks}
+    \begin{block}{Regression Specification}
+        \[
+            y_{it} = X_{it} \beta + \mu_i + \varepsilon_{it}
+        \]
+    \end{block}
+\end{frame}
+
+% --------------------------------------------------
+\section{Table}
+% --------------------------------------------------
+
 \begin{frame}{Table}
@@
     {\fontsize{8}{10}\selectfont
-
     \begin{table}[!htbp] \centering 
@@
 
-            \begin{tabular}{@{\extracolsep{5pt}}lcc} 
-            \hline 
-            \hline \\[-1.8ex] 
+        \begin{tabularx}{\linewidth}{@{} LCC @{}} 
+            \hline \hline \\
             & \multicolumn{2}{c}{\textit{Dependent variable: Overall Rating}} \\ 
@@
             \hline \\[-1.8ex] 
-            Handling of Complaints & 0.692$^{***}$ (0.149) & 0.682$^{***}$ (0.129) \\ 
-            No Special Privileges & $-$0.104 (0.135) & $-$0.103 (0.129) \\ 
+            \marktopleft{ex1} Handling of Complaints & 0.692$^{***}$ (0.149) & 0.682$^{***}$ (0.129) \\ 
+            No Special Privileges & $-$0.104 (0.135) & $-$0.103 (0.129) \markbottomright{ex1}  \\ 
             Opportunity to Learn & 0.249 (0.160) & 0.238$^{*}$ (0.139) \\ 
@@
             Adjusted R$^{2}$ & 0.656 & 0.682 \\ 
-            \hline 
-            \hline \\[-1.8ex] 
+            \hline \hline
+
             \textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-            \end{tabular} 
+        \end{tabularx} 
     \end{table}
@@
 
-% Use 16:9 ratio for figures
+% --------------------------------------------------
+\section{Figures}
+% --------------------------------------------------
+
+% 4:3 ratio or else it will have white space
+\imageframe{img/kanagawa.jpg}
+
+% Use 4:3 ratio for figures
 \begin{frame}{Figure}
     \begin{center}
-        % \includegraphics[width= .95\linewidth]{fig1.png}
+        \includegraphics[width= .95\linewidth]{img/kanagawa.jpg}
     \end{center}
@@
     \begin{column}{.62\textwidth}
-        % \includegraphics[width= \linewidth]{fig2.png}
+        \includegraphics[width= \linewidth]{img/kanagawa.jpg}
     \end{column}%
@@
         % Horizontal Bar
-        {\color{buff-gold}\rule{\linewidth}{4pt}}
+        {\color{accent}\rule{\linewidth}{3pt}}
 
         \begin{itemize}[leftmargin=0cm]
-            \item Point 1 about the figure to the left. Columns are a bit narrow
+            \item Point 1 about the figure to the left. This really only works for 16:9 aspect ratio
             \item Point 2
@@
     \begin{column}{.50\textwidth}
-        {\color{buff-gold}\rule{\linewidth}{4pt}}
+        {\color{accent}\rule{\linewidth}{3pt}}
         Column 1
@@
     \begin{column}{.50\textwidth}
-        {\color{buff-gold}\rule{\linewidth}{4pt}}
+        {\color{accent}\rule{\linewidth}{3pt}}
         Column 2
@@
 
-%%% Appendix
-\section{Appendix}
+% --------------------------------------------------
+\begin{frame}[allowframebreaks]{References}
+    \printbibliography
+\end{frame}
+% --------------------------------------------------
+
+% --------------------------------------------------
+\appendix
+% --------------------------------------------------
 
@@
 
-        \begin{table}[!htbp] \centering 
+        \begin{table}
+            \centering 
             \caption{Summary Statistics}
             \label{appendix_summ_stat}
-            \begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
+
+            \begin{tabularx}{\linewidth}{@{} LCCCCCCC @{}} 
                 \hline 
@@
                 advance & 30 & 42.933 & 10.289 & 25 & 35 & 47.8 & 72 \\ 
-            \hline \\[-1.8ex] 
-            \end{tabular}
+                \hline \\
 
-            \textit{Notes:} Using R base dataframe attitude \\ 
+                \multicolumn{8}{p{.8\textwidth}}{\textit{Notes:} Using R base dataframe attitude}
+            \end{tabularx}
+
         \end{table}

### 2021-04-24 latex-teaching/notes.tex
Teaching Notes Template

\documentclass[11pt]{article}

\title{Class Notes}
\author{\normalsize Kyle Butts\\{\footnotesize Univ. of Colorado, Boulder}}
\date{\footnotesize\today}

% Include Theme
\input{preamble.tex}

% Set Theme Colors (for colors look at preamble.tex or define your own)
\colorlet{accent}{indigo}
\colorlet{heading}{indigo!70!black}
\colorlet{emphasis}{indigo}

\begin{document}

\maketitle

\section{Normal Distribution}

This is another paragraph, contains some text to test the paragraph
interlining, paragraph indentation and \itemtag[red]{Marginal Utility} is some other features. Also, is easy to see how new paragraphs are defined by simply entering a 
double blank space.

\itemtag{Marginal Utility} is \outoffive{Rating}{4}

\subsection{Large of Law Numbers}

There are custom boxes for definitions and examples:

\begin{def_box}[accent]
    \textbf{Definition} My definition text here
\end{def_box}

\begin{example_box}[accent]{Bandwidth and noise}
    A band limited signal cannot be time limited and a time-limited signal cannot be band limited and options.
\end{example_box}

These boxes can be put in any color desired:

\begin{def_box}[dark-maroon]
    \textbf{Definition} My definition text here
\end{def_box}

\begin{example_box}[dark-maroon]{Bandwidth and noise}
    A band limited signal cannot be time limited and a time-limited signal cannot be band limited and options.
\end{example_box}

\end{document}

### 2021-07-07 latex-article/article.tex
Change citation style to econ.bst
Finish change to econ.bst
Add E, P, 1, Cov, Var commands
Fixed obselete package problem with Utopia
Update title page and reorganized preamble

@@
-\documentclass[11pt]{article}
-
-\title{\color{navyblue} Example Paper}
-\author{\normalsize Kyle Butts\\{\footnotesize Univ. of Colorado, Boulder}}
-\date{\footnotesize\today}
+\documentclass[12pt]{article}
 
@@
 
-% Set-up Bibliography
-\addbibresource{references.bib}
+% \maketitle info
+\title{Example Paper}
+\author{
+    \href{https://kylebutts.com/}{Kyle Butts}\thanks{University of Colorado, Boulder. Email: \href{mailto:buttskyle96@gmail.com}{buttskyle96@gmail.com}.} % \ and Other Author
+}
+\date{\today}
+
+% pdf info
+\hypersetup{pdftitle={Example Paper}, pdfauthor={Kyle Butts}}
 
@@
 Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+
+    \par~\par\noindent
+    JEL-Classification: 
+    \par\noindent
+    Keywords: 
+    \par
 \end{abstract}
@@
     This is an example theorem \[ 
-        y = f(X) + \varepsilon 
+        \hat{\beta}=\frac{\sum_{\ell}e_{\ell}z_{\ell}y_{\ell}^{\perp}}{\sum_{\ell}e_{\ell}z_{\ell}x_{\ell}^{\perp}}
     \]
@@
 
+Example numbered and non-numbered equations
 \begin{equation}\label{fe_reg}
@@
 \[ 
-    \mathbb{E} \left\{ Y_i(1) - Y_i(0) \right\} = \mathbb{P} (\tau \vert D_i = 1) 
+    \expec{Y_i(1) - Y_i(0)} = \prob{\tau \ \vert \ \one(D_i = 1)} 
 \]
@@
 
-                \bottomrule
+                \\\bottomrule
             \end{tabular}
@@
 \newpage
-\printbibliography%
+\bibliography{references.bib}
 % ------------------------------------------------------------------------------

### 2021-07-07 latex-article/article.tex
Update footnotes

@@
 
-See below for Theorem \ref{residue_thm}, for the regression specification Equation \ref{fe_reg}, and for Table \ref{summ_stat}, appendix table \ref{reg1}, and citation \citet{Eigen1971}.
+See below for Theorem \ref{thm:residue_thm}, for the regression specification (\ref{eq:fe_reg}), and for \autoref{tab:summ_stat}, appendix \autoref{tab:reg1}, and citation \citet{Eigen1971}.
 
@@
 
-\begin{theorem}[Example Theorem]\label{residue_thm}
+\begin{theorem}[Example Theorem]\label{thm:residue_thm}
     This is an example theorem \[ 
@@
 Example numbered and non-numbered equations
-\begin{equation}\label{fe_reg}
+\begin{equation}\label{eq:fe_reg}
     y = f(X) + \varepsilon = X \beta + \psi_i + \nu_t + w_{i,t} + \varepsilon_{i,t} 
@@
     \caption{Summary Statistics (tabularx)}
-    \label{summ_stat}
+    \label{tab:summ_stat}
 
@@
     \caption{Regression Results (Custom tabularx widths)} 
-    \label{reg1}
+    \label{tab:reg1}
 

### 2021-07-26 latex-teaching/notes.tex
Cleaned up

@@
 \colorlet{emphasis}{indigo}
+
+\newcommand{\foo}{\color{heading}\makebox[0pt]{\textbullet}\hskip-0.5pt\vrule width 1pt\hspace{\labelsep}}
+
+\newtcolorbox[blend into=figures]{myfigure}[2][]{
+    enhanced,
+    attach boxed title to top left={
+        yshift=0.2mm
+    },
+    top=1.5em,
+    colback=white,
+    colframe=white,
+    fonttitle=\bfseries,
+    boxed title style={
+        sharp corners,
+        size=small,
+        colback=indigo,
+        colframe=indigo
+    },
+    borderline north={0.5mm}{0mm}{line width=3pt},
+    float, title=#2, #1
+}
 
@@
 
+\begin{myfigure}{Duck}
+    \includegraphics{example-image-duck}
+
+    \tcblower
+    \textbf{Notes:} A band limited signal cannot be time limited and a time-limited signal cannot be band limited and options.
+\end{myfigure}
+
+\begin{table}
+    \renewcommand\arraystretch{2}
+    \caption{Timeline}
+
+    \begin{tabular}{@{}r <{\hskip 2pt} !{\foo} >{\raggedright\arraybackslash} p{10cm}@{}}
+    \addlinespace[1.5ex]
+    1947 & AT and T Bell Labs develop the idea of cellular phones\\
+    1968 & Xerox Palo Alto Research Centre envisage the 'Dynabook\\
+    1971 & Busicom 'Handy-LE' Calculator\\
+    1973 & First mobile handset invented by Martin Cooper\\
+    1978 & Parker Bros. Merlin Computer Toy\\
+    1981 & Osborne 1 Portable Computer\\
+    1982 & Grid Compass 1100 Clamshell Laptop\\
+    1983 & TRS-80 Model 100 Portable PC\\
+    1984 & Psion Organiser Handheld Computer\\
+    1991 & Psion Series 3 Minicomputer\\
+    \end{tabular}
+\end{table}
+
 \end{document}

### 2021-07-26 matlab-scheme/schemer_export.m

@@ -1,677 +1,0 @@
-%SCHEMER_EXPORT Export current MATLAB color scheme to text file
-%   If this is your first time using SCHEMER_EXPORT, please ensure you
-%   read the IMPORTANT NOTE at the bottom of the help section before using
-%   this function.
-%
-%   SCHEMER_EXPORT() with no input will prompt the user to locate a
-%   destination file via the GUI, and will save the current color scheme
-%   to this location. Please read the IMORTANT NOTE below
-%   before running this script or it may not work correctly.
-%   The MATLAB preference options which are exported are:
-%   - All settings in the Color pane of Preferences
-%   - All settings in the Color > Programming Tools pane
-%   - From Editor/Debugger > Display pane, the following:
-%      - Highlight current line (whether to highlight, and the colour)
-%      - Right-hand text limit (colour and thickness, whether on/off)
-%   The output format is the same as used in MATLAB's preferences file,
-%   which is found at FULLFILE(PREFDIR,'matlab.prf').
-%
-%   SCHEMER_EXPORT(FILENAME) exports the relevant MATLAB preferences
-%   to the file FILENAME.
-%
-%   SCHEMER_EXPORT(FILENAME, FLAG_MODE) controls which settings are output
-%   into the preference file FILENAME. Along with the colour settings for
-%   MATLAB syntax highlighting, one can also export the boolean preferences
-%   (such as whether cells and non-local variables, etc, should be coloured
-%   differently to the regular backgound and text); and one can also export
-%   the colour settings for syntax highlighting in other languages
-%   supported by MATLAB.
-%
-%   The FLAG_MODE settings available are:
-%     0 - neither booleans, nor additional languages are exported
-%     1 - boolean settings are exported, but not additional languages
-%     2 - additional language colours are exported, but not boolean settings
-%     3 - both booleans and additional languages are exported
-%
-%   By default FLAG_MODE is set to 1, so boolean settings will be
-%   exported, but the settings for syntax highlighting in additional
-%   languages will not be.
-%
-%   The colour settings for all MATLAB syntax highlighting will always be
-%   exported, even for syntax options which are currently disabled, and
-%   regardless of whether the boolean settings are being exported. This is
-%   because users loading your exported color scheme may want syntax
[…]

### 2021-07-26 matlab-scheme/schemer_import.m

@@ -1,712 +1,0 @@
-%SCHEMER_IMPORT Import a MATLAB color scheme
-%   SCHEMER_IMPORT() with no input will prompt the user to locate the
-%   color theme source file via the GUI.
-%
-%   SCHEMER_IMPORT(FILENAME) imports the color scheme options given in
-%   the file FILENAME.
-%
-%   SCHEMER_IMPORT(FILENAME, INCLUDEBOOLS) can control whether boolean
-%   preferences are included in import (default: FALSE). If INCLUDEBOOLS
-%   is set to true, boolean preference options such as whether to
-%   highlight autofixable errors, or to show variables with shared scope in
-%   a different colour will also be overridden, should they be set in the
-%   input file.
-%
-%   SCHEMER_IMPORT(INCLUDEBOOLS, FILENAME), with a boolean or numeric input
-%   followed by a string input, will also work as above because the input
-%   order is reversible.
-%
-%   SCHEMER_IMPORT(INCLUDEBOOLS) with a single boolean input will open the
-%   GUI to pick the file, and will load boolean preferences in accordance
-%   with INCLUDEBOOLS.
-%
-%   RET = SCHEMER_IMPORT(...) returns 1 on success, 0 on user
-%   cancellation at input file selection screen, -1 on fopen error, and -2
-%   on any other error.
-%
-%   NOTE:
-%   The file to import can either be a color scheme file as generated by
-%   SCHEMER_EXPORT, or an entire MATLAB preferences file such as the file
-%   you will find located at FULLFILE(PREFDIR,'matlab.prf'). This could be
-%   a MATLAB preferences file taken from a different computer or previous
-%   MATLAB installation. However, if you are importing from a matlab.prf
-%   file instead of a color scheme .prf file you should be aware that any
-%   colour preferences which have been left as the defaults on preference
-%   panels which the user has not visited on the origin system of the
-%   matlab.prf file will not be present in the file, and hence not updated
-%   on import.
-%
-%   The MATLAB preference options which will be overwritten by
-%   SCHEMER_IMPORT are:
-%   - All settings in the Color pane of Preferencs
-%   - All colour settings in the Color > Programming Tools pane, but no
-%     checkboxes
-%   - From Editor/Debugger > Display pane, the following:
-%      - Highlight current line (colour, but not whether to)
-%      - Right-hand text limit (colour and thickness, but not on/off)
-%   - From Editor/Debugger > Language, the syntax highlighting colours for
-%     each language.
-%
-%   Once the current colour preferences are overridden they cannot be
[…]

### 2021-07-26 r-snippets/snippets.R

@@ -1,3 +1,9 @@
+snippet introblock
+	`r paste0("## .R --------------------------------------------------------------------------", 
+	"\n## Kyle Butts, CU Boulder Economics \n",
+	"## \n", "## \n", sep="")`
+
+
 snippet banner
 bannerCommenter::banner("${1:title}", bandChar = "-", fold= TRUE, rightSideHashes= 4, minHashes= 80)
 

### 2021-07-28 latex-slides/slides.tex
Large update to latex slides

@@
 % \documentclass[aspectratio=169]{beamer}
-
-% Metropolis Theme ---------------------------------
-\usetheme{metropolis} % Use metropolis theme
 
@@
 
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 \maketitle
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 \section{Common Items}
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 
-\begin{frame}{Bullet Points \& Button}\label{main1}
+\begin{frame}{Components}{Bullet Points \& Button}\label{main1}
+    This section highlights commonly used components and their theming
+
     \begin{itemize}
@@
 
+        \vspace{5mm}
         \hyperlink{appendix1}{\beamergotobutton{Appendix}}
@@
 
-\begin{frame}{Citations}
+\begin{frame}{Components}{Numbered Lists}
+    You can also use numbered items that look a bit more professional
+
+    \begin{enumerate}
+        \item Pretty good
+
+        \item To include things in appendix
+    \end{enumerate}
+\end{frame}
+
+\begin{frame}{Components}{Citations}
     Topic 1: Spatial Frictions
@@
 
+    \vspace{5mm}
     Topic 2: Blah 
@@
 
-\begin{frame}{Blocks}
+\begin{frame}{Components}{Blocks}
     \begin{block}{Regression Specification}
+        The main specificaiton is as follows:
+
         \[
@@
 
-% --------------------------------------------------
+\begin{frame}{Components}{Colors}
+    {\color{navy} Test sentence with \textbackslash color\{navy\}}\newline
+    {\color{kelly} Test sentence with \textbackslash color\{kelly\}}\newline
+    {\color{ruby} Test sentence with \textbackslash color\{ruby\}}\newline
+    {\color{alice} Test sentence with \textbackslash color\{alice\}}\newline
+    {\color{daisy} Test sentence with \textbackslash color\{daisy\}}\newline
+    {\color{coral} Test sentence with \textbackslash color\{coral\}}\newline
+    {\color{jet} Test sentence with \textbackslash color\{jet\}}\newline
+    {\color{asher} Test sentence with \textbackslash color\{asher\}}\newline
+\end{frame}
+
+\begin{frame}{Components}{Two Columns general}
+    \begin{columns}[T] % T = vertical align columns at the top
+    \begin{column}{.50\textwidth}
+        {\color{accent}\rule{\linewidth}{2pt}}
+        Column 1
+
+        \begin{enumerate}
+            \item Bullet points for this column that can go over lines
+            \item b
+            \item c
+        \end{enumerate}
+    \end{column}
+
+    \hfill
+
+    \begin{column}{.50\textwidth}
+        {\color{accent}\rule{\linewidth}{2pt}}
+        Column 2
+
+        \begin{enumerate}
+            \item a
+            \item b
+            \item c
+        \end{enumerate}
+    \end{column}
+    \end{columns}
+\end{frame}
+
+\begin{frame}{Components}{Example of tikz figure}
+
+\begin{figure}
+\begin{center}
+\begin{tikzpicture}[node distance=1.5cm]
+    % nodes %
+    \node[text centered] (d) {$D$};
+    \node[below right of = d, text centered] (x) [draw, shape=circle, line width = 1] {$X$};
+    \node[above right of = x, text centered] (y) {$Y$};
+    \node[below of = x, text centered, purple] (z) {$Z$};
+
+    % edges %
+    \path[->, line width= 1] 
+        (d) edge (y)
+        (x) edge (d)
+        (x) edge (y);
+    \path[->, line width= 1, purple]
+        (z) edge [out=135, in=260, looseness=0.5] node[left, black] {$\text{Good variation in D}$} (d)
+        (z) edge [out=45, in=280, looseness=0.5] (y);
+\end{tikzpicture}
+\end{center}
+\end{figure}
+
+\end{frame}
+
+% ------------------------------------------------------------------------------
 \section{Table}
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 
-\begin{frame}{Table}
+\begin{frame}
 
 % Adjust Font Size to make table fit   
-    {\fontsize{8}{10}\selectfont
-    \begin{table}[!htbp] \centering 
+\begin{table}[!htbp]
     \caption{Regression Results} 
@@
 
-        \begin{tabularx}{\linewidth}{@{} LCC @{}} 
-            \hline \hline \\
+    \begin{adjustbox}{max width = \textwidth, width = 0.75\textwidth, center}
+        \begin{threeparttable}
+            \begin{tabular}{@{} lcc @{}} 
+                \toprule
                 & \multicolumn{2}{c}{\textit{Dependent variable: Overall Rating}} \\ 
-            \cline{2-3} 
-            \\[-1.8ex] & (1) & (2)\\ 
-            \hline \\[-1.8ex] 
-            \marktopleft{ex1} Handling of Complaints & 0.692$^{***}$ (0.149) & 0.682$^{***}$ (0.129) \\ 
-            No Special Privileges & $-$0.104 (0.135) & $-$0.103 (0.129) \markbottomright{ex1}  \\ 
+                \cline{2-3} \\
+                & (1) & (2)\\ 
+                \midrule
+
+                \marktopleft{ex1}Handling of Complaints & 0.692$^{***}$ (0.149) & 0.682$^{***}$ (0.129) \markbottomright{ex1} \\ 
+                No Special Privileges & $-$0.104 (0.135) & $-$0.103 (0.129)  \\ 
                 Opportunity to Learn & 0.249 (0.160) & 0.238$^{*}$ (0.139) \\ 
@@
                 R$^{2}$ & 0.715 & 0.715 \\ 
-            Adjusted R$^{2}$ & 0.656 & 0.682 \\ 
-            \hline \hline
+                \bottomrule
 
-            \textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-        \end{tabularx} 
+            \end{tabular} 
+            % Notes 
+            \begin{tablenotes}
+                \item \textit{Notes.} $^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01.
+            \end{tablenotes}
+        \end{threeparttable}
+    \end{adjustbox}
 \end{table}
-    }
-
 \end{frame}
 
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 \section{Figures}
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 
-% 4:3 ratio or else it will have white space
+% 4:3 ratio for figures
+% or else it will have white space
 \imageframe{img/kanagawa.jpg}
 
-% Use 4:3 ratio for figures
-\begin{frame}{Figure}
+\begin{frame}{Figure}{}
     \begin{center}
-        \includegraphics[width= .95\linewidth]{img/kanagawa.jpg}
+        \resizebox{0.9\columnwidth}{!}{%
+            \includegraphics{img/kanagawa.jpg}
+        }
     \end{center}
@@
 
-\begin{frame}{Figure with comments}
-    \begin{columns}[T] % align columns
-    \begin{column}{.62\textwidth}
-        \includegraphics[width= \linewidth]{img/kanagawa.jpg}
-    \end{column}%
-
-    \begin{column}{.38\textwidth}
-        % Horizontal Bar
-        {\color{accent}\rule{\linewidth}{3pt}}
-
-        \begin{itemize}[leftmargin=0cm]
-            \item Point 1 about the figure to the left. This really only works for 16:9 aspect ratio
-            \item Point 2
-        \end{itemize}
-    \end{column}%
-    \end{columns}
-\end{frame}
-
-\begin{frame}{Two Columns general}
-    \begin{columns}[T] % T = vertical align columns at the top
-    \begin{column}{.50\textwidth}
-        {\color{accent}\rule{\linewidth}{3pt}}
-        Column 1
-    \end{column}
-
-    \hfill
-
-    \begin{column}{.50\textwidth}
-        {\color{accent}\rule{\linewidth}{3pt}}
-        Column 2
-    \end{column}
-    \end{columns}
-\end{frame}
-
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 \begin{frame}[allowframebreaks]{References}
@@
 \end{frame}
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 \appendix
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 
@@
 
-    % Adjust Font Size to make table fit
-    {\fontsize{9}{10}\selectfont
-
 \begin{table}
-            \centering 
     \caption{Summary Statistics}
     \label{appendix_summ_stat}
-
-            \begin{tabularx}{\linewidth}{@{} LCCCCCCC @{}} 
-                \hline 
-                \hline \\[-1.8ex] 
+    \begin{adjustbox}{max width = \textwidth, width = 0.8 \textwidth, center}
+        \begin{threeparttable}
+            \begin{tabular}{@{} lccccccc @{}} 
+                \toprule
                 Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St.
@@
                 advance & 30 & 42.933 & 10.289 & 25 & 35 & 47.8 & 72 \\ 
-                \hline \\
-
-                \multicolumn{8}{p{.8\textwidth}}{\textit{Notes:} Using R base dataframe attitude}
-            \end{tabularx}
-
+                \bottomrule
+            \end{tabular} 
+            % Notes 
+            \begin{tablenotes}
+                \item \textit{Notes.} Using R base dataframe attitude.
+            \end{tablenotes}
+        \end{threeparttable}
+    \end{adjustbox}
 \end{table}
-
-    }
 

### 2021-07-28 latex-slides/slides.tex
Add purple color

@@
     {\color{navy} Test sentence with \textbackslash color\{navy\}}\newline
+    {\color{purple} Test sentence with \textbackslash color\{purple\}}\newline
     {\color{kelly} Test sentence with \textbackslash color\{kelly\}}\newline

### 2021-09-02 r-snippets/snippets.R
Cleaned up

@@ -1,30 +1,0 @@
-snippet introblock
-	`r paste0("## .R --------------------------------------------------------------------------", 
-	"\n## Kyle Butts, CU Boulder Economics \n",
-	"## \n", "## \n", sep="")`
-
-
-snippet banner
-bannerCommenter::banner("${1:title}", bandChar = "-", fold= TRUE, rightSideHashes= 4, minHashes= 80)
-
-snippet endhead
-## -----------------------------------------------------------------------------
-
-snippet introblock
-`r paste0("## -----------------------------------------------------------------------------\n", 
-		  "## ", format(Sys.time(), "%Y-%m-%d"), "_\n## Kyle Butts, CU Boulder Economics \n",
-		  "## \n", "## \n", 
-		  "## -----------------------------------------------------------------------------", sep="")`
-
-snippet func
-function() {
-	# Display what the function is doing
-	usethis::ui_todo("")
-	cat("\n")
-	
-	
-	
-	# Display what the function successfully finished
-	cat("\n")
-	usethis::ui_done("")
-}	

### 2021-09-02 latex-article/article.tex
Small update to article

@@
 \author{
-    \href{https://kylebutts.com/}{Kyle Butts}\thanks{University of Colorado, Boulder. Email: \href{mailto:buttskyle96@gmail.com}{buttskyle96@gmail.com}.} % \ and Other Author
+    \href{https://kylebutts.com/}{Kyle Butts}\thanks{University of Colorado, Boulder. Email: \href{mailto:buttskyle96@gmail.com}{buttskyle96@gmail.com}.} % and Other Author
 }
@@
 Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur: $\sum X_i$.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.\footnote{This is a test.}
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.\footnote{This is an example footnote.}
 
@@
             \begin{tabular}{@{} @{\extracolsep{5pt}} 
-                    lrrrrrrrr 
+                    l*{8}{r} 
                 @{}}
@@
 
-                \\\bottomrule
+                \bottomrule
             \end{tabular}
@@
     \begin{adjustbox}{center}
-        \begin{tabularx}{\textwidth}{@{} 
+        \begin{threeparttable}
+            \begin{tabular}{\textwidth}{@{} 
                     >{\hsize=.6\hsize}L >{\hsize=.4\hsize}R >{\hsize=.4\hsize}R 
@@
                 % Head
-            \hline \hline
+                \toprule
                 & \multicolumn{2}{c}{\textit{Dependent variable:} \ Overall Rating} \\ 
@@
 
+                \bottomrule
+            \end{tabular}
+
             % Notes
-            \hline \hline \\[-5mm]
-            \multicolumn{3}{@{} p{\textwidth}}{\small \textit{Notes.} $^{*}$ p$< 0.1$; $^{**}$ p$< 0.05$; $^{***}$ p$< 0.01$} \\ 
-            \multicolumn{3}{@{} p{\textwidth}}{\small Using R base dataframe attitude.
+            \begin{tablenotes}\setlength\labelsep{0pt}\small
+                \item {\small \textit{Notes.} $^{*}$ p$< 0.1$; $^{**}$ p$< 0.05$; $^{***}$ p$< 0.01$}
+                \item {\small Using R base dataframe attitude.
 dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
@@
 }
-        \end{tabularx} 
+            \end{tablenotes}
+        \end{threeparttable}
     \end{adjustbox}

### 2021-09-07 latex-slides/slides.tex
Update slides template

--- 2021-07-28 latex-slides/slides.tex
@@
 % Title --------------------------------------------
-\title{Title}
-\subtitle{Subtitle}
+\title{What is the Effect of X on Y?}
+\subtitle{Evidence from a Personal Anecdote}
 \date{\today}
 \author{Kyle Butts}
-% \institue{}
 
@@
 % ------------------------------------------------------------------------------
+\begin{frame}
 \maketitle
+
+% \vspace{2.5mm}
+% {\footnotesize $^*$ A bit of extra info here. Add an asterich to title or author}
+\end{frame}
 % ------------------------------------------------------------------------------
@@
     {\color{coral} Test sentence with \textbackslash color\{coral\}}\newline
+    {\color{cranberry} Test sentence with \textbackslash color\{cranbery\}}\newline
+    {\color{slate} Test sentence with \textbackslash color\{slate\}}\newline
     {\color{jet} Test sentence with \textbackslash color\{jet\}}\newline
@@
 
-\begin{frame}{Components}{Two Columns general}
-    \begin{columns}[T] % T = vertical align columns at the top
+\begin{frame}{Components}{Two Columns}
+    \begin{columns}[T]
+    \vspace{0pt}
     \begin{column}{.50\textwidth}
+        \vspace{0pt}
         {\color{accent}\rule{\linewidth}{2pt}}
@@
         \end{enumerate}
+
+        \vspace*{50mm} % Ensures columns are up top; delete if you want columns centered on page
     \end{column}
@@
 
-        \begin{enumerate}
+        \begin{itemize}
             \item a
@@
             \item c
-        \end{enumerate}
+        \end{itemize}
     \end{column}
@@
 
-\begin{frame}{Components}{Example of tikz figure}
+\begin{frame}{Components}{Two Columns with Figure}
+    \begin{columns}[T]
+    \vspace{0pt}
+    \begin{column}{.60\textwidth}
+        \includegraphics[width=\textwidth]{img/kanagawa.jpg}
 
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}[node distance=1.5cm]
-    % nodes %
-    \node[text centered] (d) {$D$};
-    \node[below right of = d, text centered] (x) [draw, shape=circle, line width = 1] {$X$};
-    \node[above right of = x, text centered] (y) {$Y$};
-    \node[below of = x, text centered, purple] (z) {$Z$};
+        \vspace*{50mm} % Ensures columns are up top; delete if you want columns centered on page
+    \end{column}
 
-    % edges %
-    \path[->, line width= 1] 
-        (d) edge (y)
-        (x) edge (d)
-        (x) edge (y);
-    \path[->, line width= 1, purple]
-        (z) edge [out=135, in=260, looseness=0.5] node[left, black] {$\text{Good variation in D}$} (d)
-        (z) edge [out=45, in=280, looseness=0.5] (y);
-\end{tikzpicture}
-\end{center}
-\end{figure}
+    \hfill
 
+    \begin{column}{.40\textwidth}
+        \begin{itemize}
+            \item A point about the figure that is potentially important.
+            \item Another point about the figure that is also potentially important.
+        \end{itemize}
+    \end{column}
+    \end{columns}
 \end{frame}
@@
 
-    \begin{adjustbox}{max width = \textwidth, width = 0.75\textwidth, center}
+    \begin{adjustbox}{max width = \textwidth, width = 0.5\textwidth, center}
         \begin{threeparttable}
-            \begin{tabular}{@{} lcc @{}} 
+            \begin{tabular}{@{} l *{2}{r} @{}} 
                 \toprule
@@
 
-                \marktopleft{ex1}Handling of Complaints & 0.692$^{***}$ (0.149) & 0.682$^{***}$ (0.129) \markbottomright{ex1} \\ 
-                No Special Privileges & $-$0.104 (0.135) & $-$0.103 (0.129)  \\ 
-                Opportunity to Learn & 0.249 (0.160) & 0.238$^{*}$ (0.139) \\ 
-                Performance-Based Raises & $-$0.033 (0.202) &  \\ 
-                Too Critical & 0.015 (0.147) &  \\ 
-                Advancement & 11.011 (11.704) & 11.258 (7.318) \\ 
-                \hline \\[-1.8ex] 
+                \only<1>{
+                    Handling of Complaints & 0.692$^{***}$& 0.682$^{***}$ \\ 
+                    &  (0.149) & (0.129) \\
+                }
+                \only<2>{
+                    \marktopleft{ex1}Handling of Complaints & 0.692$^{***}$& 0.682$^{***}$ \\ 
+                    &  (0.149) & (0.129) \markbottomright{ex1} \\
+                }
+                No Special Privileges & -0.104 & $-$0.103  \\ 
+                & (0.135) & (0.129) \\
+                Opportunity to Learn & 0.249 & 0.238$^{*}$ \\ 
+                & (0.160) & (0.139) \\
+                Performance-Based Raises & -0.033 &  \\ 
+                & (0.202) & \\
+                Too Critical & 0.015 &  \\ 
+                & (0.147) & \\
+                Advancement & 11.011 & 11.258 \\ 
+                & (11.704) & (7.318) \\
+
+                \midrule 
                 Observations & 30 & 30 \\ 
@@
             \begin{tablenotes}
-                \item \textit{Notes.} $^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01.
+                \item \textit{Notes.} $^{*} p<0.1$; $^{**} p<0.05$; $^{***} p<0.01$.
             \end{tablenotes}
@@
 \end{table}
+
+{\small
+Use \textbackslash marktopleft\{name\} and \textbackslash markbottomright\{name\} to create box.
+}
 \end{frame}
@@
 \imageframe{img/kanagawa.jpg}
+
+\begin{frame}{Figure}{Full-size Figures}
+    You can use the command \textbackslash imageframe\{img-path\} and it will create a full-frame of a picture.
+
+    \begin{itemize}
+        \item Ideally, your figure is the same aspect as the frame $4:3$ or $16:9$ or else there will be white space in one of the directions.
+    \end{itemize}
+\end{frame}
 

### 2021-09-28 latex-article/article.tex
Fix tabularx problem
Update article and slides

@@
 \author{
-    \href{https://kylebutts.com/}{Kyle Butts}\thanks{University of Colorado, Boulder. Email: \href{mailto:buttskyle96@gmail.com}{buttskyle96@gmail.com}.} % and Other Author
+    Author One\thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.} \ and Author Two\thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.}
 }
@@
     \par~\par\noindent
-    JEL-Classification: 
+    {\color{asher}JEL-Classification:} ...
     \par\noindent
-    Keywords: 
-    \par
+    {\color{asher}Keywords:} ...
+    \par\vspace{-2.5mm}
 \end{abstract}
@@
 \begin{table}[tb] 
-    \caption{Summary Statistics (tabularx)}
+    \caption{Table Too Narrow (tabularx)}
     \label{tab:summ_stat}
@@
 \begin{table}[tb] 
-    \caption{Regression Results (Custom tabularx widths)} 
+    \caption{Regression Results} 
     \label{tab:reg1}
@@
         \begin{threeparttable}
-            \begin{tabular}{\textwidth}{@{} 
-                    >{\hsize=.6\hsize}L >{\hsize=.4\hsize}R >{\hsize=.4\hsize}R 
+            \begin{tabular}{@{} 
+                    lrr
                 @{}}

### 2022-04-05 latex-slides/slides.tex
Add \begin{transitionframe}
Update article and slides
Fixes
- Fix subtitle requirement
- Add color commands
- Add bgColor boxes

@@
 \title{What is the Effect of X on Y?}
-\subtitle{Evidence from a Personal Anecdote}
 \date{\today}
@@
 
+\begin{transitionframe}
+Transitioning Sentence
+\end{transitionframe}
+
 \begin{frame}{Components}{Bullet Points \& Button}\label{main1}
@@
         \item Can emphasize with \alert{the alert command}
+
+        \begin{itemize}
+            \item This allows you to draw attention to specific words/phrases
+        \end{itemize}
 
@@
 \begin{frame}{Components}{Colors}
-    {\color{navy} Test sentence with \textbackslash color\{navy\}}\newline
-    {\color{purple} Test sentence with \textbackslash color\{purple\}}\newline
-    {\color{kelly} Test sentence with \textbackslash color\{kelly\}}\newline
-    {\color{ruby} Test sentence with \textbackslash color\{ruby\}}\newline
-    {\color{alice} Test sentence with \textbackslash color\{alice\}}\newline
-    {\color{daisy} Test sentence with \textbackslash color\{daisy\}}\newline
-    {\color{coral} Test sentence with \textbackslash color\{coral\}}\newline
-    {\color{cranberry} Test sentence with \textbackslash color\{cranbery\}}\newline
-    {\color{slate} Test sentence with \textbackslash color\{slate\}}\newline
-    {\color{jet} Test sentence with \textbackslash color\{jet\}}\newline
-    {\color{asher} Test sentence with \textbackslash color\{asher\}}\newline
+  \navy{Test sentence with \textbackslash navy\{...\}}
+
+  \purple{Test sentence with \textbackslash purple\{...\}}
+
+  \kelly{Test sentence with \textbackslash kelly\{...\}}
+
+  \ruby{Test sentence with \textbackslash ruby\{...\}}
+
+  \alice{Test sentence with \textbackslash alice\{...\}}
+
+  \daisy{Test sentence with \textbackslash daisy\{...\}}
+
+  \coral{Test sentence with \textbackslash coral\{...\}}
+
+  \cranberry{Test sentence with \textbackslash color\{cranbery\}}
+
+  \slate{Test sentence with \textbackslash color\{slate\}}
+
+  \jet{Test sentence with \textbackslash color\{jet\}}
+
+  \asher{Test sentence with \textbackslash color\{asher\}}
+\end{frame}
+
+\begin{frame}{Components}{Colored Boxes}
+  \bgNavy{Test word} with \textbackslash bgNavy\{...\}
+
+  \vspace{2.5mm}
+  \bgPurple{Test word} with \textbackslash bgPurple\{...\}
+
+  \vspace{2.5mm}
+  \bgKelly{Test word} with \textbackslash bgKelly\{...\}
+
+  \vspace{2.5mm}
+  \bgRuby{Test word} with \textbackslash bgRuby\{...\}
+
+  \vspace{2.5mm}
+  \bgAlice{Test word} with \textbackslash bgAlice\{...\}
+
+  \vspace{2.5mm}
+  \bgDaisy{Test word} with \textbackslash bgDaisy\{...\}
+
+  \vspace{2.5mm}
+  \bgCoral{Test word} with \textbackslash bgCoral\{...\}
+
+  \vspace{2.5mm}
+  \bgCranberry{Test word} with \textbackslash bgCranberry\{...\}
 \end{frame}

### 2023-03-22 latex-article/article.tex
Update article template
Update article

@@
 \author{
-    Author One\thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.} \ and Author Two\thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.}
+    Author One%
+    \thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.} \ and Author Two%
+    \thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.}
 }
@@
 
+% Conditionally include comments. Switch to \togglefalse
+\newtoggle{INCLUDECOMMENTS}
+\toggletrue{INCLUDECOMMENTS}
+% \togglefalse{INCLUDECOMMENTS}
+
+\newcommand{\kyle}[1]{\iftoggle{INCLUDECOMMENTS}{{\color{cranberry}\textbf{Kyle:} #1}}{}}
+
 \begin{document}
@@
 \begin{abstract}
-    Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
 
@@
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur: $\sum X_i$.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.\footnote{This is an example footnote.}
-
-See below for Theorem \ref{thm:residue_thm}, for the regression specification (\ref{eq:fe_reg}), and for \autoref{tab:summ_stat}, appendix \autoref{tab:reg1}, and citation \citet{Eigen1971}.
-
 % ------------------------------------------------------------------------------
-\section{Econometric Model}
+\newpage~\bibliography{references.bib}
 % ------------------------------------------------------------------------------
@@
 % ------------------------------------------------------------------------------
-\subsection{Principal Specification}
-% ------------------------------------------------------------------------------
-
-\begin{theorem}[Example Theorem]\label{thm:residue_thm}
-    This is an example theorem \[ 
-        \hat{\beta}=\frac{\sum_{\ell}e_{\ell}z_{\ell}y_{\ell}^{\perp}}{\sum_{\ell}e_{\ell}z_{\ell}x_{\ell}^{\perp}}
-    \]
-\end{theorem}
-
-Example numbered and non-numbered equations
-\begin{equation}\label{eq:fe_reg}
-    y = f(X) + \varepsilon = X \beta + \psi_i + \nu_t + w_{i,t} + \varepsilon_{i,t} 
-\end{equation}
-
-\[ 
-    \expec{Y_i(1) - Y_i(0)} = \prob{\tau \ \vert \ \one(D_i = 1)} 
-\]
-
-\begin{table}[ht]
-    \caption{Table Too Wide (adjustbox)}
-    \centering
-
-    \begin{adjustbox}{width = 1.1\textwidth, center}
-        \begin{threeparttable}
-            \begin{tabular}{@{} @{\extracolsep{5pt}} 
-                    l*{8}{r} 
-                @{}}
-                % Head
-                \toprule
-                & & & \multicolumn{2}{c}{Market Access} & \multicolumn{2}{c}{Urban Weekly Wage} & \multicolumn{2}{c}{Nonurban Weekly Wage} \\
-                \cmidrule{4-5} \cmidrule{6-7} \cmidrule{8-9}
-                Year & \multicolumn{1}{c}{N} & \% Urban & Mean & SD & Mean & SD & Mean & SD \\ 
-                \hline
-
-                % Body
-                \input{summary.tex}
-
-                \bottomrule
-            \end{tabular}
-
-            % Notes 
-            \begin{tablenotes}
-                \item \textit{Notes.} Weekly wage is reported in 2015 \$.
-            \end{tablenotes}
-        \end{threeparttable}    
-    \end{adjustbox}
-\end{table}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-% in Preamble:
-% \usepackage{pdflscape} - rotates page left-side up in pdf
-% \usepackage{lscape} - does not rotate page, only figure/table
-
-\begin{landscape}
-%\thispagestyle{empty}
-\thispagestyle{lscaped}
-
-\begin{table}[h!]
-    \caption{Landscape Table}
-    \centering
-
-    \begin{adjustbox}{width = 1.2\textwidth, center}
-        \begin{threeparttable}
-        \begin{tabular}{@{} @{\extracolsep{5pt}} 
-                lrrrrrrrr 
-            @{}}
-            % Head
-            \toprule
-            & & & \multicolumn{2}{c}{Market Access} & \multicolumn{2}{c}{Urban Weekly Wage} & \multicolumn{2}{c}{Nonurban Weekly Wage} \\
-            \cmidrule{4-5} \cmidrule{6-7} \cmidrule{8-9}
-            Year & \multicolumn{1}{c}{N} & \% Urban & Mean & SD & Mean & SD & Mean & SD \\ 
-            \hline
-
-            % Body
-            \input{summary.tex}
-
-            \bottomrule
-        \end{tabular}
-
-        % Notes
-        \begin{tablenotes}\footnotesize
-            \item \textit{Notes.} Weekly wage is reported in 2015 \$.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor
-        \end{tablenotes}
-        \end{threeparttable}
-    \end{adjustbox}
-\end{table}
-\end{landscape}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-\begin{table}[tb] 
-    \caption{Table Too Narrow (tabularx)}
-    \label{tab:summ_stat}
-
-    \begin{adjustbox}{center}
-        \begin{threeparttable}
-            \begin{tabularx}{\textwidth}{@{} 
-                    >{\hsize=.9\hsize}R >{\hsize=1.1\hsize}R >{\hsize=1.1\hsize}R >{\hsize=.9\hsize}R
-                @{}}
-
-                % Head
-                \toprule
-                & \multicolumn{2}{c}{\textbf{Population}} & \\
-                \cmidrule{2-3}
-                \textbf{Country} & 2016 & 2017 & \textbf{Change (\%)} \\
-
-                % Body
-                \hline
-                China & 1,403,500,365 & 1,409,517,397 & +0.4\% \\
-                India & 1,324,171,354 & 1,339,180,127 & +1.1\% \\
-                United States & 322,179,605 & 324,459,463 & +0.7\% \\
-                Indonesia & 261,115,456 & 263,991,379 & +1.1\% \\
-                Brazil & 207,652,865 & 209,288,278 & +0.8\% \\
-                Pakistan & 193,203,476 & 197,015,955 & +2.0\% \\
-                Nigeria & 185,989,640 & 190,886,311 & +2.6\% \\
-                Bangladesh & 162,951,560 & 164,669,751 & +1.1\% \\
-                Russia & 146,864,513 & 143,989,754 & -2.0\% \\
-                Mexico & 127,540,423 & 129,163,276 & +1.3\% \\
-
-                \bottomrule
-            \end{tabularx}
-
-            % Notes
-            \begin{tablenotes}\setlength\labelsep{0pt}\small
-                \item \textit{Source:} \href{https://en.wikipedia.org/wiki/List_of_countries_by_population_(United_Nations)}{Wikipedia}.
-            \end{tablenotes}
-        \end{threeparttable}
-    \end{adjustbox}
-\end{table}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-% ------------------------------------------------------------------------------
-\newpage
-\bibliography{references.bib}
-% ------------------------------------------------------------------------------
-
-% ------------------------------------------------------------------------------
-\newpage
-\appendix
+\newpage~\appendix
 \numberwithin{equation}{section}
@@
 
-% ------------------------------------------------------------------------------
-\section{Additional Results}
-% ------------------------------------------------------------------------------
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-% ------------------------------------------------------------------------------
-\subsection{Regression Results}
-% ------------------------------------------------------------------------------
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-\begin{table}[tb] 
-    \caption{Regression Results} 
-    \label{tab:reg1}
-
-    \begin{adjustbox}{center}
-        \begin{threeparttable}
-            \begin{tabular}{@{} 
-                    lrr
-                @{}}
-
-                % Head
-                \toprule
-                & \multicolumn{2}{c}{\textit{Dependent variable:} \ Overall Rating} \\ 
-                \cmidrule{2-3} 
-                & (1) & (2) \\ 
-                \hline
-
-                % Body
-                Handling of Complaints & 0.692$^{***}$ (0.149) & 0.682$^{***}$ (0.129) \\ 
-                No Special Privileges & $-$0.104 (0.135) & $-$0.103 (0.129) \\ 
-                Opportunity to Learn & 0.249 (0.160) & 0.238$^{*}$ (0.139) \\ 
-                Performance-Based Raises & $-$0.033 (0.202) &  \\ 
-                Too Critical & 0.015 (0.147) &  \\ 
-                Advancement & 11.011 (11.704) & 11.258 (7.318) \\ 
-                \hline 
-                Observations & 30 & 30 \\ 
-                Adjusted R$^{2}$ & 0.656 & 0.682 \\
-
-                \bottomrule
-            \end{tabular}
-
-            % Notes
-            \begin{tablenotes}\setlength\labelsep{0pt}\small
-                \item {\small \textit{Notes.} $^{*}$ p$< 0.1$; $^{**}$ p$< 0.05$; $^{***}$ p$< 0.01$}
-                \item {\small Using R base dataframe attitude.
-dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-}
-            \end{tablenotes}
-        \end{threeparttable}
-    \end{adjustbox}
-\end{table}
-
 \end{document}

### 2023-03-22 latex-article/example.tex
Update article

\documentclass[12pt]{article}

% Include Theme
\input{preamble.tex}

% \maketitle info
\title{Example Paper}
\author{
    Author One%
    \thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.} \ and Author Two%
    \thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.}
}
\date{\today}

% pdf info
\hypersetup{pdftitle={Example Paper}, pdfauthor={Kyle Butts}}

% Conditionally include comments. Switch to \togglefalse
\newtoggle{INCLUDECOMMENTS}
\toggletrue{INCLUDECOMMENTS}
% \togglefalse{INCLUDECOMMENTS}

\newcommand{\kyle}[1]{\iftoggle{INCLUDECOMMENTS}{{\color{cranberry}\textbf{Kyle:} #1}}{}}

\begin{document}

% Title Page -------------------------------------------------------------------
\maketitle
\begin{abstract}
  Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

  \par~\par\noindent
  {\color{asher}JEL-Classification:} ...
  \par\noindent
  {\color{asher}Keywords:} ...
  \par\vspace{-2.5mm}
\end{abstract}

\newpage

% Paper ------------------------------------------------------------------------

% ------------------------------------------------------------------------------
\section{Introduction}
% ------------------------------------------------------------------------------

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur: $\sum X_i$. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.\footnote{This is an example footnote.}

\kyle{I'm including this comment for coauthors. If I switch above to \texttt{togglefalse}, this will dissapear}

See below for Theorem \ref{thm:residue_thm}, for the regression specification (\ref{eq:fe_reg}), and for \autoref{tab:summ_stat}, appendix \autoref{tab:reg1}, and citation \citet{Eigen1971}.

% ------------------------------------------------------------------------------
\section{Section Header}
% ------------------------------------------------------------------------------

% ------------------------------------------------------------------------------
\subsection{Subsection}
% ------------------------------------------------------------------------------

\begin{theorem}[Example Theorem]\label{thm:residue_thm}
  This is an example theorem \[
    \hat{\beta}=\frac{\sum_{\ell}e_{\ell}z_{\ell}y_{\ell}^{\perp}}{\sum_{\ell}e_{\ell}z_{\ell}x_{\ell}^{\perp}}
  \]
\end{theorem}

Jibberish math to show off symbols:

\begin{equation}\label{eq:fe_reg}
  y = f(X) + \varepsilon = X \beta + \psi_i + \nu_t + w_{i,t} + \varepsilon_{i,t}
\end{equation}

Has iriure invenire no, vidit tamquam ad nec, sea unum efficiantur no. In fugit eruditi quaerendum qui. Eleifend interpretaris mel id. Cu tation veniam habemus ius. Prima tritani duo ei, est iuvaret dignissim an, efficiendi adversarium per ut. Sit eu lucilius postulant, ut nam falli vitae theophrastus. Vel ex audire referrentur.

Tibique reformidans ut eum, oratio singulis efficiantur eam eu. Modus simul quo cu, id populo essent urbanitas nec. Cum agam aeterno cu, soleat iuvaret posidonium mel cu. Eirmod noluisse ad vix.

\[
  \condexpec{Y_i(1) - Y_i(0)}{\one(D_i = 1)} = \prob{\tau}
\]

\begin{table}[ht]
  \caption{Table Too Wide (adjustbox)}
  \centering

  \begin{threeparttable}
    \begin{adjustbox}{width = 1.1\textwidth, center}
      \begin{tabular}{@{} @{\extracolsep{5pt}}
          l*{8}{r}
          @{}}
        % Head
        \toprule
        & & & \multicolumn{2}{c}{Market Access} & \multicolumn{2}{c}{Urban Weekly Wage} & \multicolumn{2}{c}{Nonurban Weekly Wage} \\
        \cmidrule{4-5} \cmidrule{6-7} \cmidrule{8-9}
        Year & \multicolumn{1}{c}{N} & \% Urban & Mean & SD & Mean & SD & Mean & SD \\
        \hline

        % Body
        \input{summary.tex}

        \bottomrule
      \end{tabular}
    \end{adjustbox}

    % Notes 
    \begin{tablenotes}
      \item \textit{Notes.} Weekly wage is reported in 2015 \$.
    \end{tablenotes}
  \end{threeparttable}
\end{table}

Lorem ipsum dolor sit amet, mei no electram definiebas. Usu nibh brute laoreet ad. Discere habemus referrentur nam ea, sanctus principes accommodare vim ea, his an quis legendos. Id omnis option eum, sit ad agam quando putant. Per elit impetus corpora ut, nam quot mutat soleat ei. No falli scaevola sit, an vix civibus philosophia. Stet posse omittantur ei per, eum no magna dicit recteque.

Paulo mundi quodsi cu eum. Cu unum bonorum invenire pri, quem rebum detracto quo cu, sea legere legendos at. Eu his meis constituam reformidans, an nec bonorum maiestatis, dicat omittam honestatis cum an. Te sed porro deserunt imperdiet, discere inciderint instructior ea sea. Autem mentitum copiosae mei te.

Has debet mentitum ei, ne mel ullum electram, ei est putant iracundia concludaturque. Ne modus debet suscipit eam. Mea sapientem tincidunt accommodare ea. Illum voluptaria id mea. Duo ei facilis sapientem consulatu, utinam gloriatur cu eos.

Ex diam paulo inimicus nec. Nam ea mazim singulis, ius omnis modus ad. Cu ius summo referrentur, audire iuvaret dignissim id sed. Mei an volutpat gubergren, ne eos graece albucius reformidans, usu modo indoctum no.

Fastidii scriptorem ea per, offendit ponderum at vel, sumo intellegebat ei eos. Sea movet legendos et, sea simul petentium sadipscing cu, his audire deterruisset ne. Te commune conclusionemque has, ad ignota molestiae pro, pri te mutat euripidis adipiscing. Vel novum percipit ad, officiis recteque referrentur mel ut, quaerendum referrentur quo et. Sea dicit nonumy inermis et, vis eros dolorum in, no ius natum magna officiis. Cu natum ancillae hendrerit vim, eos ei possit habemus lucilius.

Et sea vitae legere efficiendi, recusabo dissentiunt theophrastus id eum. Eam at munere integre vivendo. Meis regione necessitatibus pro in, ut vis autem labores. At purto disputationi his.

Mundi nobis dignissim eu has, oratio salutandi pro ut. Ei vocibus electram sit, ad pri dolor feugiat molestie. An brute option recteque vim. Qui percipit oporteat perfecto ne. Ut mel summo nonumes expetenda, prompta percipit accusamus mel ex, cu possit option fabulas est.

An hinc tation facilisis vim, vim id diam euismod voluptatibus, modo putent vel no. Elit quaeque luptatum has in, ne vis errem deleniti inimicus, at quo ancillae concludaturque. Ut ius tempor aperiam nostrum. Elitr vulputate ne nec. Ex rebum principes deterruisset mea, quo at unum graeco.

\begin{figure}
  \caption{Event-timing}

  \begin{adjustbox}{center}
    \begin{tikzpicture}
      \draw (0,0) -- (11,0);
      \foreach \x in {0.8,4,5.5,7,10.2}
      \draw(\x cm,3pt) -- (\x cm, -3pt);
      \draw (0.8,0) node[below=3pt] {$T_0$};
      \draw (4,0) node[below=3pt] {$T_1$};
      \draw (5.5,0) node[below=3pt] {$0$};
      \draw (7,0) node[below=3pt] {$T_2$};
      \draw (10.2,0) node[below=3pt] {$T_3$};
      \draw (2.35,0) node[above=6pt, align=center]
      {\begin{tabular}{c}Estimation \\Window\end{tabular}};
    \end{tikzpicture}

  \end{adjustbox}
  {\footnotesize \emph{Notes:} This is an example figure in the paper}
\end{figure}

Stet nulla ubique quo an, sit nibh vituperata ut, ei qui electram dignissim. Nec tota minimum ex. Malis mucius epicurei ex nam, has saepe tincidunt te. Eos ei dicit denique ullamcorper, te dicam conceptam sea.

Nec et libris feugiat, ut vis dolor suavitate. An pro hendrerit deterruisset, nam velit comprehensam te. Tation minimum ut his. At illum dicat sed, ex atomorum delicatissimi concludaturque nec, mea menandri referrentur ei. Bonorum quaestio imperdiet mea ei. Ferri ponderum voluptatibus ei est, cu atqui paulo patrioque mei, vim ex nobis postea eligendi.

Ne eam animal sententiae contentiones, his no fierent incorrupte. Etiam eripuit patrioque eum ne. Quo ei duis autem aperiam, et purto temporibus has. Et posse ignota per. Ei solum tempor argumentum qui.

\begin{table}[tb]
  \caption{Table Too Narrow (tabularx)}
  \label{tab:summ_stat}

  \begin{threeparttable}
    \begin{adjustbox}{center}
      \begin{tabularx}{\textwidth}{@{}
          >{\hsize=.9\hsize}R >{\hsize=1.1\hsize}R >{\hsize=1.1\hsize}R >{\hsize=.9\hsize}R
          @{}}

        % Head
        \toprule
        & \multicolumn{2}{c}{\textbf{Population}} & \\
        \cmidrule{2-3}
        \textbf{Country} & 2016          & 2017          & \textbf{Change (\%)} \\

        % Body
        \hline
        China            & 1,403,500,365 & 1,409,517,397 & +0.4\%               \\
        India            & 1,324,171,354 & 1,339,180,127 & +1.1\%               \\
        United States    & 322,179,605   & 324,459,463   & +0.7\%               \\
        Indonesia        & 261,115,456   & 263,991,379   & +1.1\%               \\
        Brazil           & 207,652,865   & 209,288,278   & +0.8\%               \\
        Pakistan         & 193,203,476   & 197,015,955   & +2.0\%               \\
        Nigeria          & 185,989,640   & 190,886,311   & +2.6\%               \\
        Bangladesh       & 162,951,560   & 164,669,751   & +1.1\%               \\
        Russia           & 146,864,513   & 143,989,754   & -2.0\%               \\
        Mexico           & 127,540,423   & 129,163,276   & +1.3\%               \\

        \bottomrule
      \end{tabularx}
    \end{adjustbox}

    % Notes
    \begin{tablenotes}\setlength\labelsep{0pt}\small
      \item \textit{Source:} \href{https://en.wikipedia.org/wiki/List_of_countries_by_population_(United_Nations)}{Wikipedia}.
    \end{tablenotes}
  \end{threeparttable}

\end{table}

Per cu offendit vituperata dissentiet, pro vocibus mandamus deterruisset eu, habeo libris reprehendunt qui et. Omnis saepe referrentur et qui, at duo ipsum eripuit numquam. At eam vocent euismod. Tation graeci interesset et est, ea essent definitiones mei. His ne lobortis persequeris, usu te vide invenire, usu ad tempor dissentias.

Sit id possit nemore, partem apeirian intellegam mea ut. Qui ei etiam dissentias. Alienum disputando pro ea, ex vero mandamus omittantur est, insolens electram an eum. Possit omittam vis et, in his cibo impetus. Eos te minim alienum petentium, malorum eripuit bonorum mei ei.

% ------------------------------------------------------------------------------
\newpage
\bibliography{references.bib}
% ------------------------------------------------------------------------------

% ------------------------------------------------------------------------------
\newpage
\appendix
\numberwithin{equation}{section}
\numberwithin{figure}{section}
\numberwithin{table}{section}
\renewcommand{\thefigure}{\Alph{section}\arabic{figure}}
\renewcommand{\thetable}{\Alph{section}\arabic{table}}
% ------------------------------------------------------------------------------

% ------------------------------------------------------------------------------
\section{Additional Results}
% ------------------------------------------------------------------------------

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

% ------------------------------------------------------------------------------
\subsection{Regression Results}
% ------------------------------------------------------------------------------

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\begin{table}[tb]
  \caption{Regression Results}
  \label{tab:reg1}

  \begin{adjustbox}{center}
    \begin{threeparttable}
      \begin{tabular}{@{}
          lrr
          @{}}

        % Head
        \toprule
        & \multicolumn{2}{c}{\textit{Dependent variable:} \ Overall Rating} \\
        \cmidrule{2-3}
                                 & (1)                   & (2)                   \\
        \hline

        % Body
        Handling of Complaints   & 0.692$^{***}$ (0.149) & 0.682$^{***}$ (0.129) \\
        No Special Privileges    & $-$0.104 (0.135)      & $-$0.103 (0.129)      \\
        Opportunity to Learn     & 0.249 (0.160)         & 0.238$^{*}$ (0.139)   \\
        Performance-Based Raises & $-$0.033 (0.202)      &                       \\
        Too Critical             & 0.015 (0.147)         &                       \\
        Advancement              & 11.011 (11.704)       & 11.258 (7.318)        \\
        \hline
        Observations             & 30                    & 30                    \\
        Adjusted R$^{2}$         & 0.656                 & 0.682                 \\

        \bottomrule
      \end{tabular}

      % Notes
      \begin{tablenotes}\setlength\labelsep{0pt}\small
        \item {\small \textit{Notes.} $^{*}$ p$< 0.1$; $^{**}$ p$< 0.05$; $^{***}$ p$< 0.01$}
        \item {\small Using R base dataframe attitude. dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum. }
      \end{tablenotes}
    \end{threeparttable}
  \end{adjustbox}
\end{table}

\end{document}

### 2023-08-29 CU_research_computing/run.sh
Update slides

@@ -1,22 +1,0 @@
-#!/bin/bash
-
-#SBATCH --nodes=1
-#SBATCH --ntasks=1
-#SBATCH --mem=48gb
-#SBATCH --time=00:01:00
-#SBATCH --job-name=x
-#SBATCH --output=x-%j.out
-
-cd /projects/kybu6659/templates/R/
-
-module purge
-
-echo "Loading Anaconda"
-source /curc/sw/anaconda3/latest
-echo "Loading environment"
-# conda activate rstudio
-conda activate r-spatial
-
-
-Rscript template.R
-

### 2023-08-29 ggplot_theme/theme_kyle.R

@@ -1,149 +1,0 @@
-# Load Showtext and font Fira Sans
-if(!require("showtext")) {
-	print("Install the package `showtext`.")
-} else {
-	library("showtext")
-	showtext_auto()
-	font_add_google("Fira Sans", "fira_sans")
-	font_add_google("Merriweather", "merriweather")
-}
-
-
-#' @param title_pos either "center" or "left" to align title and subtitle center of left respectively
-#' @param axis_title_pos either "center" or "left" to align title and subtitle center or left/top respectively
-#' @param slides if TRUE, use background #ECECEC or not
-theme_kyle <- function(title_pos = "center", axis_title_pos = "left", slides = FALSE, has_subtitle = FALSE, base_size = 14, ...) {
-	
-	title_hjust <- switch(title_pos, "center" = 0.5, "left" = 0)
-	axis_title_hjust_y <- switch(axis_title_pos, "center" = 0.5, "left" = 1.0)
-	axis_title_hjust_x <- switch(axis_title_pos, "center" = 0.5, "left" = 0.0)
-	plot_bg = if_else(slides, "#ECECEC", "transparent")
-	plot_grid = if_else(slides, "grey85", "grey92")
-	title_margin = if_else(has_subtitle, "4", "16")
-	
-	theme_bw(
-		base_size = base_size,
-		base_family = "fira_sans"
-	) + 
-		theme(
-			## Title and Subtitle --------------------------------------------------
-			plot.title = ggplot2::element_text(
-				# Font
-				family = "merriweather", face = "bold", size = rel(1.285), 
-				colour = "#454545", 
-				# Center title
-				hjust = title_hjust,
-				# Margins
-				margin = ggplot2::margin(b = title_margin, unit = "pt")
-			),
-			plot.subtitle = ggplot2::element_text(
-				# Font
-				family = "merriweather", face = "italic", size = rel(.86), 
-				colour = "#454545", 
-				# Center subtitle 
-				hjust = title_hjust,
-				# Margins
-				margin = ggplot2::margin(b = 16, unit = "pt")
-			),
-			plot.title.position = "plot",
-			
-			## Caption -------------------------------------------------------------
-			plot.caption = ggplot2::element_text(
-				# Font
-				size = rel(0.72), colour = "#454545",
-				# Right-align caption
-				hjust = 1,
-				# Margins
-				margin = ggplot2::margin(t = 20)
-			),
-			plot.caption.position = "plot",
-			
-			## Axis ----------------------------------------------------------------
[…]

### 2023-08-29 latex-slides/slides.tex
Update slides
Update slide template

@@
-\documentclass[aspectratio=43]{beamer}
-% \documentclass[aspectratio=169]{beamer}
+\documentclass[aspectratio=169]{beamer}
+% \documentclass[aspectratio=43]{beamer}
+
+% Define `accent`/`accent2` colors for theme customization
+\definecolor{accent}{HTML}{006896}
+\definecolor{accent2}{HTML}{E64173}
+
+% Beamer theme
+\input{preamble.tex}
 
@@
 \author{Kyle Butts}
-
-\input{preamble.tex}
 
@@
 \begin{frame}{Components}{Blocks}
-    \begin{block}{Regression Specification}
+  \begin{block}{}
     The main specificaiton is as follows: 
+    $$
+      y_{it} = X_{it} \beta + \mu_i + \varepsilon_{it}
+    $$
+    With $\mu_i$ being unit fixed effects.
+  \end{block}
+\end{frame}
 
-        \[
-            y_{it} = X_{it} \beta + \mu_i + \varepsilon_{it}
-        \]
-    \end{block}
+\begin{frame}{Components}{Blocks}
+  \begin{purpleBlock}{}
+      This is a purple block
+  \end{purpleBlock}
+
+  \begin{cranberryBlock}{With Title}
+    This is a cranberry block
+  \end{cranberryBlock}
 \end{frame}
@@
   \navy{Test sentence with \textbackslash navy\{...\}}
+
+  \teal{Test sentence with \textbackslash teal\{...\}}
 
@@
   \cranberry{Test sentence with \textbackslash color\{cranbery\}}
-
-  \slate{Test sentence with \textbackslash color\{slate\}}
-
-  \jet{Test sentence with \textbackslash color\{jet\}}
-
-  \asher{Test sentence with \textbackslash color\{asher\}}
 \end{frame}
 
-\begin{frame}{Components}{Colored Boxes}
+\begin{frame}[plain]
   \bgNavy{Test word} with \textbackslash bgNavy\{...\}
@@
   \bgPurple{Test word} with \textbackslash bgPurple\{...\}
+
+  \vspace{2.5mm}
+  \bgOrange{Test word} with \textbackslash bgOrange\{...\}
+
+  \vspace{2.5mm}
+  \bgTeal{Test word} with \textbackslash bgTeal\{...\}
 
@@
     \vspace{0pt}
-    \begin{column}{.60\textwidth}
-        \includegraphics[width=\textwidth]{img/kanagawa.jpg}
+    \begin{column}{.6\textwidth}
+        \includegraphics[width=0.9\textwidth]{img/kanagawa.jpg}
 
@@
     \end{column}
-
     \hfill
-
-    \begin{column}{.40\textwidth}
+    \begin{column}{.4\textwidth}
         \begin{itemize}
@@
 
-\begin{frame}
+\begin{frame}{Table}
 
+\begin{columns}[T]
+  \vspace{0pt}
+  \begin{column}{.6\textwidth}
     % Adjust Font Size to make table fit   
     \begin{table}[!htbp]
-    \caption{Regression Results} 
+      % \caption{Regression Results} 
       \label{}
 
-    \begin{adjustbox}{max width = \textwidth, width = 0.5\textwidth, center}
+      \begin{adjustbox}{max width = \textwidth, width = 0.8 \textwidth, center}
           \begin{threeparttable}
@@
                   & (0.160) & (0.139) \\
-                Performance-Based Raises & -0.033 &  \\ 
-                & (0.202) & \\
-                Too Critical & 0.015 &  \\ 
-                & (0.147) & \\
-                Advancement & 11.011 & 11.258 \\ 
-                & (11.704) & (7.318) \\
 
@@
 
-{\small
-Use \textbackslash marktopleft\{name\} and \textbackslash markbottomright\{name\} to create box.
-}
+      \vspace*{50mm} % Ensures columns are up top; delete if you want columns centered on page
+  \end{column}
+  \hfill
+  \begin{column}{.4\textwidth}
+      \begin{itemize}
+          \item Use \texttt{\textbackslash marktopleft\{name\}} and \texttt{\textbackslash markbottomright\{name\}} within the table to create box.
+          \item Using \texttt{\textbackslash only} or \texttt{\textbackslash on} lets you conditionally display box
+      \end{itemize}
+  \end{column}
+\end{columns}
+
 \end{frame}
@@
 % or else it will have white space
-\imageframe{img/kanagawa.jpg}
+\imageframe{img/kanagawa_16_9.png}
 
 \begin{frame}{Figure}{Full-size Figures}
-    You can use the command \textbackslash imageframe\{img-path\} and it will create a full-frame of a picture.
+  You can use the command \texttt{\textbackslash imageframe\{img-path\}} and it will create a full-frame of a picture.
 
   \begin{itemize}
-        \item Ideally, your figure is the same aspect as the frame $4:3$ or $16:9$ or else there will be white space in one of the directions.
+    \item Ideally, your figure is the same aspect as the frame \texttt{4:3} or \texttt{16:9} or else there will be white space in one of the directions.
   \end{itemize}
@@
     \begin{center}
-        \resizebox{0.9\columnwidth}{!}{%
-            \includegraphics{img/kanagawa.jpg}
+        \resizebox{0.85\columnwidth}{!}{%
+            \includegraphics{img/kanagawa_16_9.png}
         }
@@
 \begin{frame}{Appendix Slide}\label{appendix1}
-
 \begin{table}
@@
     \label{appendix_summ_stat}
-    \begin{adjustbox}{max width = \textwidth, width = 0.8 \textwidth, center}
+    \begin{adjustbox}{max width = \textwidth, width = 0.7\textwidth, center}
         \begin{threeparttable}

### 2023-10-05 latex-slides/slides.tex
Small tweaks to latex slides
Update slides to have fallback colors
Update slides template (no warnings)

@@
-\documentclass[aspectratio=169]{beamer}
+\documentclass[aspectratio=169,t]{beamer}
 % \documentclass[aspectratio=43]{beamer}
+\input{preamble.tex}
 
@@
 \definecolor{accent}{HTML}{006896}
-\definecolor{accent2}{HTML}{E64173}
+\definecolor{accent2}{HTML}{695693}
 
-% Beamer theme
-\input{preamble.tex}
-
-% Title --------------------------------------------
 \title{What is the Effect of X on Y?}
@@
 
-% Set-up Bibliography ------------------------------
 \addbibresource{references.bib}
@@
     Topic 1: Spatial Frictions
-    \begin{citecolor}
+    \citecolor{
       [\citet{Fajgelbaum_Morales_Serrato_Zidar_2018}, \citet{Hsieh_Moretti_2019}, and \citet{Moretti_2011}]
-    \end{citecolor}
+    }
 
@@
     Topic 2: Blah 
-    \begin{citecolor}
+    \citecolor{
       [\citet{Suárez_Serrato_Zidar_2016}]
-    \end{citecolor}
+    }
 \end{frame}
@@
 \begin{frame}{Components}{Blocks}
-  \begin{block}{}
+  \begin{block}{Theorem 1}
     The main specificaiton is as follows: 
@@
     $$
-    With $\mu_i$ being unit fixed effects.
   \end{block}
@@
 
-\begin{frame}[plain]
+\begin{frame}{Components}{Background Colors}
   \bgNavy{Test word} with \textbackslash bgNavy\{...\}
 
-  \vspace{2.5mm}
   \bgPurple{Test word} with \textbackslash bgPurple\{...\}
 
-  \vspace{2.5mm}
   \bgOrange{Test word} with \textbackslash bgOrange\{...\}
 
-  \vspace{2.5mm}
   \bgTeal{Test word} with \textbackslash bgTeal\{...\}
 
-  \vspace{2.5mm}
   \bgKelly{Test word} with \textbackslash bgKelly\{...\}
 
-  \vspace{2.5mm}
   \bgRuby{Test word} with \textbackslash bgRuby\{...\}
 
-  \vspace{2.5mm}
   \bgAlice{Test word} with \textbackslash bgAlice\{...\}
 
-  \vspace{2.5mm}
   \bgDaisy{Test word} with \textbackslash bgDaisy\{...\}
 
-  \vspace{2.5mm}
   \bgCoral{Test word} with \textbackslash bgCoral\{...\}
 
-  \vspace{2.5mm}
   \bgCranberry{Test word} with \textbackslash bgCranberry\{...\}
@@
   \begin{columns}[T]
-    \vspace{0pt}
     \begin{column}{.50\textwidth}
@@
         \end{enumerate}
-
-        \vspace*{50mm} % Ensures columns are up top; delete if you want columns centered on page
     \end{column}
@@
         \includegraphics[width=0.9\textwidth]{img/kanagawa.jpg}
-
-        \vspace*{50mm} % Ensures columns are up top; delete if you want columns centered on page
     \end{column}
@@
 \begin{frame}{Table}
-
   \begin{columns}[T]
-  \vspace{0pt}
     \begin{column}{.6\textwidth}
@@
         % \caption{Regression Results}
-      \label{}
 
@@
       \end{table}
-
-      \vspace*{50mm} % Ensures columns are up top; delete if you want columns centered on page
     \end{column}
@@
   \end{columns}
-
 \end{frame}
@@
 \begin{frame}{Figure}{}
-    \begin{center}
-        \resizebox{0.85\columnwidth}{!}{%
+  \begin{adjustbox}{width = 0.7\textwidth, center}
     \includegraphics{img/kanagawa_16_9.png}
-        }
-    \end{center}
+  \end{adjustbox}
 \end{frame}
@@
 
-\begin{frame}{Appendix Slide}\label{appendix1}
+\begin{frame}{Appendix Slide}{\hyperlink{main1}{\beamergotobutton{Back to Main}}}\label{appendix1}
   \begin{table}
@@
           raises & 30 & 64.633 & 10.397 & 43 & 58.2 & 71 & 88 \\ 
-                critical & 30 & 74.767 & 9.895 & 49 & 69.2 & 80 & 92 \\ 
-                advance & 30 & 42.933 & 10.289 & 25 & 35 & 47.8 & 72 \\ 
           \bottomrule
         \end{tabular}
-            % Notes 
+
         \begin{tablenotes}
@@
   \end{table}
+\end{frame}
 
-    \hyperlink{main1}{\beamergotobutton{Back to Main}}
-\end{frame}
 \end{document}

### 2023-10-05 latex-article/article.tex
Update templates (no warnings!!)

--- 2021-09-28 latex-article/article.tex
@@
 
-% pdf info
-\hypersetup{pdftitle={Example Paper}, pdfauthor={Kyle Butts}}
+% Conditionally include comments. Switch to \togglefalse
+\newtoggle{INCLUDECOMMENTS}
+\toggletrue{INCLUDECOMMENTS}
+% \togglefalse{INCLUDECOMMENTS}
+\newcommand{\kyle}[1]{\iftoggle{INCLUDECOMMENTS}{{\color{cranberry}\textbf{Kyle:} #1}}{}}
 
@@
 
+\kyle{I'm including this comment for coauthors. If I switch above to \texttt{togglefalse}, this will dissapear}
+
 See below for Theorem \ref{thm:residue_thm}, for the regression specification (\ref{eq:fe_reg}), and for \autoref{tab:summ_stat}, appendix \autoref{tab:reg1}, and citation \citet{Eigen1971}.
 
+Colors: \navy{Navy}, \teal{Teal}, \purple{Purple}, \cranberry{Cranberry}, \orange{Orange}
+
 % ------------------------------------------------------------------------------
-\section{Econometric Model}
+\section{Section Header}
 % ------------------------------------------------------------------------------
@@
 % ------------------------------------------------------------------------------
-\subsection{Principal Specification}
+\subsection{Subsection}
 % ------------------------------------------------------------------------------
@@
 
-Example numbered and non-numbered equations
+Jibberish math to show off symbols:
+
 \begin{equation}\label{eq:fe_reg}
@@
 
+Has iriure invenire no, vidit tamquam ad nec, sea unum efficiantur no.
+In fugit eruditi quaerendum qui.
+Eleifend interpretaris mel id.
+Cu tation veniam habemus ius.
+Prima tritani duo ei, est iuvaret dignissim an, efficiendi adversarium per ut.
+Sit eu lucilius postulant, ut nam falli vitae theophrastus.
+Vel ex audire referrentur.
+
+Tibique reformidans ut eum, oratio singulis efficiantur eam eu. Modus simul quo cu, id populo essent urbanitas nec. Cum agam aeterno cu, soleat iuvaret posidonium mel cu. Eirmod noluisse ad vix.
+
 \[
-    \expec{Y_i(1) - Y_i(0)} = \prob{\tau \ \vert \ \one(D_i = 1)} 
+  \condexpec{Y_i(1) - Y_i(0)}{\one(D_i = 1)} = \prob{\tau}
 \]
@@
 
-    \begin{adjustbox}{width = 1.1\textwidth, center}
   \begin{threeparttable}
+    \begin{adjustbox}{width = \textwidth, center}
       \begin{tabular}{@{} @{\extracolsep{5pt}}
@@
       \end{tabular}
+    \end{adjustbox}
 
@@
   \end{threeparttable}
-    \end{adjustbox}
 \end{table}
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+Lorem ipsum dolor sit amet, mei no electram definiebas.
+Usu nibh brute laoreet ad.
+Discere habemus referrentur nam ea, sanctus principes accommodare vim ea, his an quis legendos.
+Id omnis option eum, sit ad agam quando putant.
+Per elit impetus corpora ut, nam quot mutat soleat ei.
+No falli scaevola sit, an vix civibus philosophia.
+Stet posse omittantur ei per, eum no magna dicit recteque.
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+Paulo mundi quodsi cu eum.
+Cu unum bonorum invenire pri, quem rebum detracto quo cu, sea legere legendos at.
+Eu his meis constituam reformidans, an nec bonorum maiestatis, dicat omittam honestatis cum an.
+Te sed porro deserunt imperdiet, discere inciderint instructior ea sea.
+Autem mentitum copiosae mei te.
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+Has debet mentitum ei, ne mel ullum electram, ei est putant iracundia concludaturque.
+Ne modus debet suscipit eam.
+Mea sapientem tincidunt accommodare ea.
+Illum voluptaria id mea.
+Duo ei facilis sapientem consulatu, utinam gloriatur cu eos.
 
-% in Preamble:
-% \usepackage{pdflscape} - rotates page left-side up in pdf
-% \usepackage{lscape} - does not rotate page, only figure/table
+Ex diam paulo inimicus nec.
+Nam ea mazim singulis, ius omnis modus ad.
+Cu ius summo referrentur, audire iuvaret dignissim id sed.
+Mei an volutpat gubergren, ne eos graece albucius reformidans, usu modo indoctum no.
 
-\begin{landscape}
-%\thispagestyle{empty}
-\thispagestyle{lscaped}
+Fastidii scriptorem ea per, offendit ponderum at vel, sumo intellegebat ei eos.
+Sea movet legendos et, sea simul petentium sadipscing cu, his audire deterruisset ne.
+Te commune conclusionemque has, ad ignota molestiae pro, pri te mutat euripidis adipiscing.
+Vel novum percipit ad, officiis recteque referrentur mel ut, quaerendum referrentur quo et.
+Sea dicit nonumy inermis et, vis eros dolorum in, no ius natum magna officiis.
+Cu natum ancillae hendrerit vim, eos ei possit habemus lucilius.
 
-\begin{table}[h!]
-    \caption{Landscape Table}
-    \centering
+Et sea vitae legere efficiendi, recusabo dissentiunt theophrastus id eum. Eam at munere integre vivendo. Meis regione necessitatibus pro in, ut vis autem labores. At purto disputationi his.
 
-    \begin{adjustbox}{width = 1.2\textwidth, center}
-        \begin{threeparttable}
-        \begin{tabular}{@{} @{\extracolsep{5pt}} 
-                lrrrrrrrr 
-            @{}}
-            % Head
-            \toprule
-            & & & \multicolumn{2}{c}{Market Access} & \multicolumn{2}{c}{Urban Weekly Wage} & \multicolumn{2}{c}{Nonurban Weekly Wage} \\
-            \cmidrule{4-5} \cmidrule{6-7} \cmidrule{8-9}
-            Year & \multicolumn{1}{c}{N} & \% Urban & Mean & SD & Mean & SD & Mean & SD \\ 
-            \hline
+Mundi nobis dignissim eu has, oratio salutandi pro ut.
+Ei vocibus electram sit, ad pri dolor feugiat molestie.
+An brute option recteque vim.
+Qui percipit oporteat perfecto ne.
+Ut mel summo nonumes expetenda, prompta percipit accusamus mel ex, cu possit option fabulas est.
 
-            % Body
-            \input{summary.tex}
+An hinc tation facilisis vim, vim id diam euismod voluptatibus, modo putent vel no.
+Elit quaeque luptatum has in, ne vis errem deleniti inimicus, at quo ancillae concludaturque.
+Ut ius tempor aperiam nostrum.
+Elitr vulputate ne nec.
+Ex rebum principes deterruisset mea, quo at unum graeco.
 
-            \bottomrule
-        \end{tabular}
+\begin{figure}
+  \caption{Event-timing}
 
-        % Notes
-        \begin{tablenotes}\footnotesize
-            \item \textit{Notes.} Weekly wage is reported in 2015 \$.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor
-        \end{tablenotes}
-        \end{threeparttable}
+  \begin{adjustbox}{center}
+    \begin{tikzpicture}
+      \draw (0,0) -- (11,0);
+      \foreach \x in {0.8,4,5.5,7,10.2}
+      \draw(\x cm,3pt) -- (\x cm, -3pt);
+      \draw (0.8,0) node[below=3pt] {$T_0$};
+      \draw (4,0) node[below=3pt] {$T_1$};
+      \draw (5.5,0) node[below=3pt] {$0$};
+      \draw (7,0) node[below=3pt] {$T_2$};
+      \draw (10.2,0) node[below=3pt] {$T_3$};
+      \draw (2.35,0) node[above=6pt, align=center]
+      {\begin{tabular}{c}Estimation \\Window\end{tabular}};
+    \end{tikzpicture}
+
   \end{adjustbox}
-\end{table}
-\end{landscape}
+  {\footnotesize \emph{Notes:} This is an example figure in the paper}
+\end{figure}
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+Stet nulla ubique quo an, sit nibh vituperata ut, ei qui electram dignissim.
+Nec tota minimum ex.
+Malis mucius epicurei ex nam, has saepe tincidunt te.
+Eos ei dicit denique ullamcorper, te dicam conceptam sea.
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+Nec et libris feugiat, ut vis dolor suavitate.
+An pro hendrerit deterruisset, nam velit comprehensam te.
+Tation minimum ut his.
+At illum dicat sed, ex atomorum delicatissimi concludaturque nec, mea menandri referrentur ei.
+Bonorum quaestio imperdiet mea ei.
+Ferri ponderum voluptatibus ei est, cu atqui paulo patrioque mei, vim ex nobis postea eligendi.
+
+Ne eam animal sententiae contentiones, his no fierent incorrupte.
+Etiam eripuit patrioque eum ne.
+Quo ei duis autem aperiam, et purto temporibus has.
+Et posse ignota per.
+Ei solum tempor argumentum qui.
 
@@
 
+  \begin{threeparttable}
     \begin{adjustbox}{center}
-        \begin{threeparttable}
       \begin{tabularx}{\textwidth}{@{}
@@
       \end{tabularx}
+    \end{adjustbox}
 
@@
   \end{threeparttable}
-    \end{adjustbox}
+
 \end{table}
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+Per cu offendit vituperata dissentiet, pro vocibus mus deterruisset eu, habeo libris reprehendunt qui et.
+Omnis saepe referrentur et qui, at duo ipsum eripuit numquam.
+At eam vocent euismod.
+Tation graeci interesset et est, ea essent definitiones mei.
+His ne lobortis persequeris, usu te vide invenire, usu ad tempor dissentias.
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+Sit id possit nemore, partem apeirian intellegam mea ut.
+Qui ei etiam dissentias.
+Alienum disputando pro ea, ex vero mandamus omittantur est, insolens electram an eum.
+Possit omittam vis et, in his cibo impetus.
+Eos te minim alienum petentium, malorum eripuit bonorum mei ei.
 

### 2023-10-05 latex-article/article.tex
Switch to .sty finally
Improve article template:
- Improve font choice (option for sans-serif and serif)
- IBM Plex mono for `\texttt` font
- New `\note` command from @pmichaillat.
  - This replaces `threeparttable`
- Math symbols to seperate file following @pmichaillat

@@
 \documentclass[12pt]{article}
+\usepackage{paper}
+\usepackage{math}
 
-% Include Theme
-\input{preamble.tex}
-
-% \maketitle info
 \title{Example Paper}
@@
 % \togglefalse{INCLUDECOMMENTS}
-\newcommand{\kyle}[1]{\iftoggle{INCLUDECOMMENTS}{{\color{cranberry}\textbf{Kyle:} #1}}{}}
+\newcommand{\kyle}[1]{\iftoggle{INCLUDECOMMENTS}{
+  \cranberry{\textbf{Kyle:} #1}
+}{}}
+
+\hfuzz=100pt
 
@@
 % Paper ------------------------------------------------------------------------
-
 % ------------------------------------------------------------------------------
@@
 % ------------------------------------------------------------------------------
-\subsection{Subsection}
+\subsection{Math Commands}
 % ------------------------------------------------------------------------------
+
+\kyle{I'm including this comment for coauthors. If I switch above to \texttt{togglefalse}, this will dissapear}
+
+Credit to \url{https://pascalmichaillat.org/d3/} for his math commands package
+
+The command \texttt{\textbackslash E[optional]\{optional\}\{optional\}} now lets you specify subscript, the inner term, and a second bracket to do conditional expectation.
+All three are optional and \textbackslash expec is a alias.
+$$\E \quad \E[i] \quad \E{X_i} \quad \E[i]{X_i} \quad \E{X_i}{n} \quad \E[i]{X_i}{n}$$
+
+\texttt{\textbackslash P}, \texttt{\textbackslash prob}, \texttt{\textbackslash cov}, and \texttt{\textbackslash var} work the same way too:
+$$\P \quad \P[i] \quad \P{X_i} \quad \P[i]{D_i} \quad \P{\bar{X}_n > \bar{X}}{\mu = \mu_0} \quad \P[\mathcal{F}]{X_i}{D_i = 1}$$
+$$\cov{X_n, Y_n} \quad \var[i](\bar{X}_n)$$
+
+\texttt{\textbackslash one} does an indicator. Same as above, but no conditional:
+$$\one{X_i > 0}$$
+
+We have \texttt{\textbackslash aslim}, \texttt{\textbackslash plim}, and \texttt{\textbackslash convd} for convergence symbols. There's also \texttt{\textbackslash iid}. Examples:
+$$\bar{x}_n \aslim \mu \quad \bar{x}_n \plim \mu \quad \bar{x}_n \convd N(0, 1)$$
+$$X_i \iid N(0, 1)$$
+
+To wrap things in automatically scaling wrappers, can use \texttt{\textbackslash bp} for parenthesis, \texttt{\textbackslash bc} for curly braces, and \texttt{\textbackslash bs} for square brackets:
+$$\bp{y_i} \quad \bc{y_i} \quad \bs{y_i}$$
+
+Similar to expectations, I have `upgraded' \texttt{\textbackslash min}, \texttt{\textbackslash inf}, \texttt{\textbackslash liminf}, \texttt{\textbackslash max}, \texttt{\textbackslash sup}, and \texttt{\textbackslash limsup} commands to use the optional `\texttt{[]}' for subscript:
+$$\min[i]{x_i} \quad \inf[i]{x_i} \quad \liminf[n \to \infty]{x_i}$$
+$$\max[i]{x_i} \quad \sup[i]{x_i} \quad \limsup[n \to \infty]{x_i}$$
+
+Theorem environments look nice.
+There are the following environments and their numbering resets automatically for appendices: \texttt{theorem}, \texttt{proposition}, \texttt{assumption}, \texttt{example}, \texttt{lemma}, \texttt{corollary}, \texttt{definition}, \texttt{remark}
 
@@
 
-Has iriure invenire no, vidit tamquam ad nec, sea unum efficiantur no.
-In fugit eruditi quaerendum qui.
-Eleifend interpretaris mel id.
-Cu tation veniam habemus ius.
-Prima tritani duo ei, est iuvaret dignissim an, efficiendi adversarium per ut.
-Sit eu lucilius postulant, ut nam falli vitae theophrastus.
-Vel ex audire referrentur.
-
-Tibique reformidans ut eum, oratio singulis efficiantur eam eu. Modus simul quo cu, id populo essent urbanitas nec. Cum agam aeterno cu, soleat iuvaret posidonium mel cu. Eirmod noluisse ad vix.
-
-\[
-  \condexpec{Y_i(1) - Y_i(0)}{\one(D_i = 1)} = \prob{\tau}
-\]
+Lorem ipsum dolor sit amet, mei no electram definiebas.
+Usu nibh brute laoreet ad.
+Discere habemus referrentur nam ea, sanctus principes accommodare vim ea, his an quis legendos.
+Id omnis option eum, sit ad agam quando putant.
+Per elit impetus corpora ut, nam quot mutat soleat ei.
+No falli scaevola sit, an vix civibus philosophia.
+Stet posse omittantur ei per, eum no magna dicit recteque.
 
@@
 
-  \begin{threeparttable}
   \begin{adjustbox}{width = \textwidth, center}
-      \begin{tabular}{@{} @{\extracolsep{5pt}}
-          l*{8}{r}
-          @{}}
+    \begin{tabular}{ 
+      @{} @{\extracolsep{5pt}} l*{8}{r} @{}
+    }
       % Head
@@
 
-    % Notes 
-    \begin{tablenotes}
-      \item \textit{Notes.} Weekly wage is reported in 2015 \$.
-    \end{tablenotes}
-  \end{threeparttable}
+  \note{Weekly wage is reported in 2015 \$.}
 \end{table}
-
-Lorem ipsum dolor sit amet, mei no electram definiebas.
-Usu nibh brute laoreet ad.
-Discere habemus referrentur nam ea, sanctus principes accommodare vim ea, his an quis legendos.
-Id omnis option eum, sit ad agam quando putant.
-Per elit impetus corpora ut, nam quot mutat soleat ei.
-No falli scaevola sit, an vix civibus philosophia.
-Stet posse omittantur ei per, eum no magna dicit recteque.
 
@@
 \appendix
-\numberwithin{equation}{section}
-\numberwithin{figure}{section}
-\numberwithin{table}{section}
-\renewcommand{\thefigure}{\Alph{section}\arabic{figure}}
-\renewcommand{\thetable}{\Alph{section}\arabic{table}}
 % ------------------------------------------------------------------------------

### 2023-10-05 latex-slides/slides.tex
Update templates (no warnings!!)
Switch to .sty finally
Improved slide format:
- Improved footnote numbering
- New `\note{}` command for better table
- New `\bottomleft{}` command for putting beamer buttons
- IBM Plex mono font for `\ttfamily`
- No page numbering on table of contents

@@
-\documentclass[aspectratio=169,t]{beamer}
-% \documentclass[aspectratio=43]{beamer}
-\input{preamble.tex}
+\documentclass[aspectratio=169,t,11pt]{beamer}
+% \documentclass[aspectratio=43,t,11pt]{beamer}
+\usepackage{slides,math}
 
@@
 \author{Kyle Butts}
-
 \addbibresource{references.bib}
-
 \begin{document}
@@
 % ------------------------------------------------------------------------------
-\begin{frame}
+\begin{frame}[noframenumbering,plain]
 \maketitle
@@
 
-\begin{transitionframe}
-  Transitioning Sentence
-\end{transitionframe}
-
 \begin{frame}{Components}{Bullet Points \& Button}\label{main1}
@@
 
-        \item To include things in appendix, you must first label the slide and the appendix slide and then include a hyperlink:
+    \item To include things in appendix, you must first label the slide and the appendix slide and then include a hyperlink.
+The command \texttt{\textbackslash bottomleft} will position in the bottom left corner nicely
+  \end{itemize}
 
-        \vspace{5mm}
-        \hyperlink{appendix1}{\beamergotobutton{Appendix}}
-    \end{itemize}
+  \bottomleft{\hyperlink{appendix1}{\beamergotobutton{Appendix}}}
 \end{frame}
@@
   \vspace{0pt}
-    \begin{column}{.6\textwidth}
-        \includegraphics[width=0.9\textwidth]{img/kanagawa.jpg}
+  \begin{column}{.5\textwidth}
+    \includegraphics[width=\textwidth]{img/kanagawa.jpg}
   \end{column}
   \hfill
-    \begin{column}{.4\textwidth}
+  \begin{column}{.48\textwidth}
     \begin{itemize}
@@
   \begin{columns}[T]
-    \begin{column}{.6\textwidth}
-      % Adjust Font Size to make table fit   
-      \begin{table}[!htbp]
-        % \caption{Regression Results}
-
-        \begin{adjustbox}{max width = \textwidth, width = 0.8 \textwidth, center}
-            \begin{threeparttable}
+  \begin{column}{.4\textwidth}
+    \begin{adjustbox}{max width = \textwidth, center}
       \begin{tabular}{@{} l *{2}{r} @{}} 
         \toprule
-                    & \multicolumn{2}{c}{\textit{Dependent variable: Overall Rating}} \\ 
-                    \cline{2-3} \\
         & (1) & (2)\\ 
@@
       \end{tabular}   
-                % Notes 
-                \begin{tablenotes}
-                    \item \textit{Notes.} $^{*} p<0.1$; $^{**} p<0.05$; $^{***} p<0.01$.
-                \end{tablenotes}
-            \end{threeparttable}
     \end{adjustbox}
-      \end{table}
+
+    \note{$^{*} p<0.1$; $^{**} p<0.05$; $^{***} p<0.01$.}
   \end{column}
   \hfill
-    \begin{column}{.4\textwidth}
+  \begin{column}{.5\textwidth}
     \begin{itemize}
@@
 % ------------------------------------------------------------------------------
-\begin{frame}[allowframebreaks]{References}
+\begin{frame}[allowframebreaks,noframenumbering]{References}
+  \thispagestyle{empty}
   \printbibliography
 \end{frame}
-% ------------------------------------------------------------------------------
-
-% ------------------------------------------------------------------------------
 \appendix
@@
 
-\begin{frame}{Appendix Slide}{\hyperlink{main1}{\beamergotobutton{Back to Main}}}\label{appendix1}
-  \begin{table}
-    \caption{Summary Statistics}
-    \label{appendix_summ_stat}
-    \begin{adjustbox}{max width = \textwidth, width = 0.7\textwidth, center}
-      \begin{threeparttable}
+\begin{frame}{Appendix Slide}{Summary Slides}\label{appendix1}
+  \begin{table}[t]
+    % \caption{Summary Statistics}\label{tab:summary_stats}
+    \begin{adjustbox}{width = 0.8\textwidth}
       \begin{tabular}{@{} lccccccc @{}} 
@@
       \end{tabular} 
+    \end{adjustbox}
 
-        \begin{tablenotes}
-            \item \textit{Notes.} Using R base dataframe attitude.
-        \end{tablenotes}
-      \end{threeparttable}
-    \end{adjustbox}
+    \note{0.8\textwidth}{Using R base dataframe \texttt{attitude}. R base dataframe attitude. R base dataframe attitude.}
   \end{table}
+
+  \bottomleft{\hyperlink{main1}{\beamerreturnbutton{Back}}}
+  % \bottomright{\hyperlink{main1}{\beamerreturnbutton{Back}}}
 \end{frame}

### 2023-10-05 latex-article/article.tex
Write more details in `article.tex`

--- 2023-03-22 latex-article/article.tex
@@
 
-% pdf info
-\hypersetup{pdftitle={Example Paper}, pdfauthor={Kyle Butts}}
-
 % Conditionally include comments. Switch to \togglefalse
@@
 % \togglefalse{INCLUDECOMMENTS}
+\newcommand{\kyle}[1]{\iftoggle{INCLUDECOMMENTS}{
+  \orange{\textbf{Kyle:} #1}
+}{}}
 
-\newcommand{\kyle}[1]{\iftoggle{INCLUDECOMMENTS}{{\color{cranberry}\textbf{Kyle:} #1}}{}}
+\hfuzz=100pt
 
@@
 \begin{abstract}
+  Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
 
@@
 
+Hi and welcome to my default paper template.
+I tried to make the theme minimal and beautiful while able to do all the things that I want it to do.
+These include making it easy to make figures/tables with notes; have powerful math commands; have nice readable typography; make co-authoring in a document easy; have a nice looking bibliography; and make appendices easy.\kyle{I'm including this comment for coauthors.
+If I switch above to \texttt{togglefalse}, this will dissapear.}  I'll show off these things, but make sure to check the source code alongside to see how simple it is to typset with this.
+
+See below for \autoref{thm:residue_thm}, the regression specification (\autoref{eq:fe_reg}), \autoref{tab:summ_stat}, \autoref{fig:event_timing}, appendix \autoref{tab:reg1}.
+Of course, make sure to touch up on your micro theory with \citet{mas1995microeconomic}.
+I also provide a set of colors: \navy{Navy}, \teal{Teal}, \purple{Purple}, \cranberry{Cranberry}, \orange{Orange}.
+
 % ------------------------------------------------------------------------------
-\newpage~\bibliography{references.bib}
+\section{Highlights}
 % ------------------------------------------------------------------------------
@@
 % ------------------------------------------------------------------------------
-\newpage~\appendix
-\numberwithin{equation}{section}
-\numberwithin{figure}{section}
-\numberwithin{table}{section}
-\renewcommand{\thefigure}{\Alph{section}\arabic{figure}}
-\renewcommand{\thetable}{\Alph{section}\arabic{table}}
+\subsection{Math Commands}
 % ------------------------------------------------------------------------------
 
+Theorem environments look nice.
+There are the following environments and their numbering resets automatically for appendices: \texttt{theorem}, \texttt{proposition}, \texttt{assumption}, \texttt{example}, \texttt{lemma}, \texttt{corollary}, \texttt{definition}, \texttt{remark}
+
+\begin{theorem}[Example Theorem]\label{thm:residue_thm}
+  This is an example theorem \[
+    \hat{\beta}=\frac{\sum_{\ell}e_{\ell}z_{\ell}y_{\ell}^{\perp}}{\sum_{\ell}e_{\ell}z_{\ell}x_{\ell}^{\perp}}
+  \]
+\end{theorem}
+
+Jibberish math to show off symbols:
+
+\begin{equation}\label{eq:fe_reg}
+  y = f(X) + \varepsilon = X \beta + \psi_i + \nu_t + w_{i,t} + \varepsilon_{i,t}
+\end{equation}
+
+I've included a file \texttt{math.sty} that has a set of math operators that I find useful.\footnote{Credit to \url{https://pascalmichaillat.org/d3/} for his math commands package which I took almost all of this from.}
+
+The command \texttt{\textbackslash E[optional]\{optional\}\{optional\}} now lets you specify subscript, the inner term, and a second bracket to do conditional expectation.
+All three are optional and \textbackslash expec is a alias.
+$$\E \quad \E[i] \quad \E{X_i} \quad \E[i]{X_i} \quad \E{X_i}{n} \quad \E[i]{X_i}{n}$$
+
+\texttt{\textbackslash P}, \texttt{\textbackslash prob}, \texttt{\textbackslash cov}, and \texttt{\textbackslash var} work the same way too:
+$$\P \quad \P[i] \quad \P{X_i} \quad \P[i]{D_i} \quad \P{\bar{X}_n > \bar{X}}{\mu = \mu_0} \quad \P[\mathcal{F}]{X_i}{D_i = 1}$$
+$$\cov{X_n, Y_n} \quad \var[i](\bar{X}_n)$$
+
+\texttt{\textbackslash one} does an indicator. Same as above, but no conditional:
+$$\one{X_i > 0}$$
+
+We have \texttt{\textbackslash aslim}, \texttt{\textbackslash plim}, and \texttt{\textbackslash convd} for convergence symbols. There's also \texttt{\textbackslash iid}. Examples:
+$$\bar{x}_n \aslim \mu \quad \bar{x}_n \plim \mu \quad \bar{x}_n \convd N(0, 1)$$
+$$X_i \iid N(0, 1)$$
+
+To wrap things in automatically scaling wrappers, can use \texttt{\textbackslash bp} for parenthesis, \texttt{\textbackslash bc} for curly braces, and \texttt{\textbackslash bs} for square brackets:
+$$\bp{y_i} \quad \bc{y_i} \quad \bs{y_i}$$
+
+Similar to expectations, I have `upgraded' \texttt{\textbackslash min}, \texttt{\textbackslash inf}, \texttt{\textbackslash liminf}, \texttt{\textbackslash max}, \texttt{\textbackslash sup}, and \texttt{\textbackslash limsup} commands to use the optional `\texttt{[]}' for subscript:
+$$\min[i]{x_i} \quad \inf[i]{x_i} \quad \liminf[n \to \infty]{x_i}$$
+$$\max[i]{x_i} \quad \sup[i]{x_i} \quad \limsup[n \to \infty]{x_i}$$
+
+% ------------------------------------------------------------------------------
+\subsection{Tables}
+% ------------------------------------------------------------------------------
+
+For tables, I use the \texttt{tabular} and \texttt{booktabs} packages.
+For table and figure notes, I use a custom \texttt{\textbackslash note} command.
+It uses \texttt{\textbackslash parbox} under the hood.
+You can use it in one of of four ways:
+\begin{enumerate}
+  \item \texttt{\textbackslash note\{text\}}
+  \item \texttt{\textbackslash note[Notes.]\{text\}}
+  \item \texttt{\textbackslash note\{0.6\textbackslash textwidth\}\{text\}}
+  \item \texttt{\textbackslash note[Notes.]\{0.6\textwidth\}\{text\}}
+\end{enumerate}
+
+In addition, I use the \texttt{adjustbox} package for resizing figures/tables.
+It automatically scales the figure/table proportionally, so things look right.
+For example, here's a table that's too wide.
+I use the \texttt{adjustbox} package to fix it.
+
+\begin{table}[ht]
+  \caption{Table Too Wide (adjustbox)}\label{tab:summ_stat}
+  \centering
+
+  \begin{adjustbox}{width = \textwidth, center}
+    \begin{tabular}{ 
+      @{} @{\extracolsep{5pt}} l*{8}{r} @{}
+    }
+      % Head
+      \toprule
+      & & & \multicolumn{2}{c}{Market Access} & \multicolumn{2}{c}{Urban Weekly Wage} & \multicolumn{2}{c}{Nonurban Weekly Wage} \\
+      \cmidrule{4-5} \cmidrule{6-7} \cmidrule{8-9}
+      Year & \multicolumn{1}{c}{N} & \% Urban & Mean & SD & Mean & SD & Mean & SD \\
+      \hline
+
+      % Body
+      \input{summary.tex}
+
+      \bottomrule
+    \end{tabular}
+  \end{adjustbox}
+
+  \note{Weekly wage is reported in 2015 \$.}
+\end{table}
+
+Figures also use the \texttt{\textbackslash note} and the \texttt{adjustbox} package. Here's an example figure:
+
+\begin{figure}[b!]
+  \caption{Event-timing}\label{fig:event_timing}
+  \begin{adjustbox}{width = 0.6\textwidth, center}
+    \begin{tikzpicture}
+      \draw (0,0) -- (11,0);
+      \foreach \x in {0.8,4,5.5,7,10.2}
+      \draw(\x cm,3pt) -- (\x cm, -3pt);
+      \draw (0.8,0) node[below=3pt] {$T_0$};
+      \draw (4,0) node[below=3pt] {$T_1$};
+      \draw (5.5,0) node[below=3pt] {$0$};
+      \draw (7,0) node[below=3pt] {$T_2$};
+      \draw (10.2,0) node[below=3pt] {$T_3$};
+      \draw (2.35,0) node[above=6pt, align=center]
+      {\begin{tabular}{c}Estimation \\Window\end{tabular}};
+    \end{tikzpicture}
+  \end{adjustbox}
+
+  \begin{center}
+    \note{0.6\textwidth}{This is an example figure in the paper}
+  \end{center}
+\end{figure}
+
+% ------------------------------------------------------------------------------
+\newpage
+\bibliography{references.bib}
+% ------------------------------------------------------------------------------
+
+% ------------------------------------------------------------------------------
+\newpage
+\appendix
+% ------------------------------------------------------------------------------
+
+% ------------------------------------------------------------------------------
+\section{Additional Results}
+% ------------------------------------------------------------------------------
+
+The appendix will automatically start numbering tables, figures, and theorem-like environments using the appendix section \textbackslash Alph (e.g. \autoref{tab:reg1}).
+
+% ------------------------------------------------------------------------------
+\subsection{Regression Results}
+% ------------------------------------------------------------------------------
+
+In this table example, the table is narrower than textwidth, so I adjust the \texttt{\textbackslash note} width.
+
+\begin{table}[h!]
+  \caption{Regression Results}
+  \label{tab:reg1}
+  \begin{center}
+    \begin{tabular}{@{} lrr @{}}
+      % Head
+      \toprule
+      & \multicolumn{2}{c}{\textit{Dependent variable:} \ Overall Rating} \\
+      \cmidrule{2-3}
+                                & (1)                   & (2)                   \\
+      \hline
+
+      % Body
+      Handling of Complaints   & 0.692$^{***}$ (0.149) & 0.682$^{***}$ (0.129) \\
+      No Special Privileges    & $-$0.104 (0.135)      & $-$0.103 (0.129)      \\
+      Opportunity to Learn     & 0.249 (0.160)         & 0.238$^{*}$ (0.139)   \\
+      Performance-Based Raises & $-$0.033 (0.202)      &                       \\
+      Too Critical             & 0.015 (0.147)         &                       \\
+      Advancement              & 11.011 (11.704)       & 11.258 (7.318)        \\
+      \hline
+      Observations             & 30                    & 30                    \\
+      Adjusted R$^{2}$         & 0.656                 & 0.682                 \\
+
+      \bottomrule
+    \end{tabular}
+
+    \note{0.68\textwidth}{Using R base dataframe attitude.
+dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.}
+    \note[]{0.68\textwidth}{$^{*}$ $p < 0.1$; $^{**}$ $p < 0.05$; $^{***}$ $p < 0.01$.}
+  \end{center}
+\end{table}
+
 \end{document}

### 2023-10-09 nice_tables/example.R
Clean up templates

@@ -1,28 +1,0 @@
-library(texreg)
-setwd("~/Documents/templates/r-nice_tables/")
-
-df <- tibble(
-	treat = 1:20 > 10,
-	z = runif(20, -1, 1),
-	y = 5 * treat + 3 * z + 2 + rnorm(20, 0, 1^2)
-)
-
-m1 <- lm(y ~ treat, data = df)
-m2 <- lm(y ~ treat + z, data = df)
-
-# screenreg(list(m1, m2))
-
-tex <- texreg::texreg(
-	list(m1, m2), 
-	# file = "table1.tex",
-	center = FALSE, table = FALSE, tabular = FALSE,
-	custom.note = "", #stars = NULL, 
-	custom.model.names = c("(1)", "(2)"),
-	custom.coef.names = c("Intercept", "Treated", "Covariate"),
-	include.rsquared = F
-)
-
-tex <- stringr::str_replace(tex, stringr::regex("^\\n\\\\hline\\n.+\\n\\\\hline"), "")
-tex <- stringr::str_replace(tex, stringr::regex("\\\\hline$"), "")
-
-cat(tex, file = "table1.tex")

### 2023-10-09 referee-response/responses.tex
Response letter to referee reports

\documentclass[12pt]{article}
% Should copy over the .sty files from latex-article
\usepackage{../latex-article/paper}
\usepackage{../latex-article/math}
\usepackage{referee-response}

% Conditionally display thoughts (hide by switching to `\boolfalse`)
\booltrue{INCLUDECOMMENTS}
\newcommand{\kyle}[1]{\coauthorComment[Kyle]{#1}}

% (hide by switching to `\boolfalse`)
\booltrue{INCLUDETODOS}

% Reference main document ------------------------------------------------------
% Note: I compile to `auxiliary/` to avoid cluttering the main directory. You might neeed to delete `auxiliary/`
% \usepackage{xr}
% \externaldocument[main-]{auxiliary/article}

\begin{document}

% Title ------------------------------------------------------------------------
\begin{center}
    {\large\bf Paper Title}

    \emph{Authors' Responses to Referee Comments}

    \emph{Journal} (\texttt{Review Number})
\end{center}
% ------------------------------------------------------------------------------

\noindent Thank you for the additional suggestions. The reviewer's comment is marked with a left border. Our responses follow below each comment.

\section*{Summary of Revisions}

% ------------------------------------------------------------------------------
\NewRef{Referee 1}{R1}
% ------------------------------------------------------------------------------

\begin{refcomment}
  Comment 
\end{refcomment}

\begin{todos}
  Thoughts / plan of action. These can be hidden by toggling \texttt{INCLUDETODOS} to \texttt{\textbackslash boolfalse}. 
\end{todos}

\begin{response}
  Response
\end{response}

\begin{refcomment}
  Comment 
\end{refcomment}

\begin{todos}
  Thoughts / plan of action. 
\end{todos}

\begin{response}
  Response
\end{response}

% ------------------------------------------------------------------------------
\NewRef{Referee 2}{R2}
% ------------------------------------------------------------------------------

\end{document}

### 2023-10-26 latex-article/article.tex
Updated article template
Clean up title page
Update tables for slides

@@
 
-\title{Example Paper}
+\title{Example Paper\thanks{\acknlowledgements}}
 \author{
-  Author One%
-  \thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.} \ and Author Two%
-  \thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.}
+  Author One\thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.} 
+  \ and 
+  Author Two\thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.}
 }
-\date{\today}
+\date{\textsc{\today}}
+\def\acknlowledgements{%
+  Acknlowedgements
+}
 
-% Conditionally include comments. Switch to \togglefalse
-\newtoggle{INCLUDECOMMENTS}
-\toggletrue{INCLUDECOMMENTS}
-% \togglefalse{INCLUDECOMMENTS}
-\newcommand{\kyle}[1]{\iftoggle{INCLUDECOMMENTS}{
-  \orange{\textbf{Kyle:} #1}
-}{}}
-
-\hfuzz=100pt
+% Conditionally display thoughts (hide by switching to `\boolfalse`)
+\booltrue{INCLUDECOMMENTS}
+\newcommand{\kyle}[1]{\coauthorComment[Kyle]{#1}}
 
@@
 \texttt{\textbackslash P}, \texttt{\textbackslash prob}, \texttt{\textbackslash cov}, and \texttt{\textbackslash var} work the same way too:
-$$\P \quad \P[i] \quad \P{X_i} \quad \P[i]{D_i} \quad \P{\bar{X}_n > \bar{X}}{\mu = \mu_0} \quad \P[\mathcal{F}]{X_i}{D_i = 1}$$
+$$\P \quad \P[i] \quad \P{X_i} \quad \P[i]{D_i} \quad \P{\bar{X}_n > \bar{X}}{\mu = \mu_0} \quad \P[\mu]{X}{D = 1}$$
 $$\cov{X_n, Y_n} \quad \var[i](\bar{X}_n)$$
@@
 \texttt{\textbackslash one} does an indicator. Same as above, but no conditional:
-$$\one{X_i > 0}$$
+$$\one{X_i > 0} \quad (Y_i, D_i) \indep X_i$$
 
-We have \texttt{\textbackslash aslim}, \texttt{\textbackslash plim}, and \texttt{\textbackslash convd} for convergence symbols. There's also \texttt{\textbackslash iid}. Examples:
-$$\bar{x}_n \aslim \mu \quad \bar{x}_n \plim \mu \quad \bar{x}_n \convd N(0, 1)$$
-$$X_i \iid N(0, 1)$$
+We have \texttt{\textbackslash asto}, \texttt{\textbackslash pto}, and \texttt{\textbackslash dto} for convergence symbols:
+$$\bar{x}_n \asto \mu \quad \bar{x}_n \pto \mu \quad \bar{x}_n \dto N(0, 1)$$
+
+There's also \texttt{\textbackslash iid} and \texttt{\textbackslash plim} for the probability limit operator:
+$$\plim_{n\to \infty} \frac{1}{n} X' X = S_{X'X} \quad X_i \iid N(0, 1)$$
 
@@
   \item \texttt{\textbackslash note\{0.6\textbackslash textwidth\}\{text\}}
-  \item \texttt{\textbackslash note[Notes.]\{0.6\textwidth\}\{text\}}
+  \item \texttt{\textbackslash note[Notes.]\{0.6\textbackslash textwidth\}\{text\}}
 \end{enumerate}
@@
       % Body
-      \input{summary.tex}
+      \input{tables/summary.tex}
 
@@
 
-  \note{Weekly wage is reported in 2015 \$.}
+  \note{Weekly wage is reported in 2015.}
 \end{table}

### 2023-10-26 latex-slides/slides.tex
Add \orange to slides
Update tables for slides

@@
-\documentclass[aspectratio=169,t,11pt]{beamer}
-% \documentclass[aspectratio=43,t,11pt]{beamer}
+\documentclass[aspectratio=169,t,11pt,table]{beamer}
 \usepackage{slides,math}
+% \geometry{paperwidth=168mm,paperheight=94.5mm}
 
 % Define `accent`/`accent2` colors for theme customization
+% I recommend changing the top slider on this: 
+% https://hslpicker.com/#1e9400
 \definecolor{accent}{HTML}{006896}
-\definecolor{accent2}{HTML}{695693}
+\definecolor{accent2}{HTML}{940034}
 
@@
 
-  \bottomleft{\hyperlink{appendix1}{\beamergotobutton{Appendix}}}
+  \bottomleft{
+    \hyperlink{appendix1}{\beamergotobutton{Appendix}}
+    \beamergotobutton{Button 2} 
+    \beamergotobutton{Button 3}
+  }
 \end{frame}
@@
 
+  \purple{Test sentence with \textbackslash purple\{...\}}
+
+  \orange{Test sentence with \textbackslash orange\{...\}}
+
   \teal{Test sentence with \textbackslash teal\{...\}}
-
-  \purple{Test sentence with \textbackslash purple\{...\}}
 
@@
   \cranberry{Test sentence with \textbackslash color\{cranbery\}}
-\end{frame}
-
-\begin{frame}{Components}{Background Colors}
-  \bgNavy{Test word} with \textbackslash bgNavy\{...\}
-
-  \bgPurple{Test word} with \textbackslash bgPurple\{...\}
-
-  \bgOrange{Test word} with \textbackslash bgOrange\{...\}
-
-  \bgTeal{Test word} with \textbackslash bgTeal\{...\}
-
-  \bgKelly{Test word} with \textbackslash bgKelly\{...\}
-
-  \bgRuby{Test word} with \textbackslash bgRuby\{...\}
-
-  \bgAlice{Test word} with \textbackslash bgAlice\{...\}
-
-  \bgDaisy{Test word} with \textbackslash bgDaisy\{...\}
-
-  \bgCoral{Test word} with \textbackslash bgCoral\{...\}
-
-  \bgCranberry{Test word} with \textbackslash bgCranberry\{...\}
 \end{frame}
@@
   \begin{columns}[T]
-  \vspace{0pt}
-  \begin{column}{.5\textwidth}
+    \begin{column}{.54\textwidth}
       \includegraphics[width=\textwidth]{img/kanagawa.jpg}
@@
     \hfill
-  \begin{column}{.48\textwidth}
+    \begin{column}{.46\textwidth}
       \begin{itemize}
@@
 
+\begin{frame}{Table with cell / row highlighting}{}
+  Use \texttt{\textbackslash cellcolor<\#>\{color\}} and \texttt{\textbackslash rowcolor<\#>\{color\}} to color cell / row. The \texttt{<\#>} is an optional overlay specification
+
+  \medskip
+  \begin{table}[h]
+    \centering
+    \begin{tabular}{lc}
+      \toprule
+      & (1) \\
+      \midrule
+      \rowcolor<2>{alice!15!white}Treatment dummy & \cellcolor<1>{accent!15!white} 0.0694* \\
+      \rowcolor<2>{alice!15!white}& (0.0401) \\
+      \rowcolor<3>{alice!15!white} Constant & -1.2238*** \\
+      \rowcolor<3>{alice!15!white} & (0.0764)  \\
+      \hline
+      Observations & 1,673  \\
+      R-squared & 0.0401 \\
+
+      \bottomrule
+    \end{tabular}
+  \end{table}
+\end{frame}
+
 \begin{frame}{Table}
@@
         \only<1>{
+          \marktopleft{ex1}Handling of Complaints & 0.692$^{***}$& 0.682$^{***}$ \\ 
+          &  (0.149) & (0.129) \markbottomright{ex1} \\
+        }
+        \only<2>{
           Handling of Complaints & 0.692$^{***}$& 0.682$^{***}$ \\ 
           &  (0.149) & (0.129) \\
-        }
-        \only<2>{
-          \marktopleft{ex1}Handling of Complaints & 0.692$^{***}$& 0.682$^{***}$ \\ 
-          &  (0.149) & (0.129) \markbottomright{ex1} \\
         }
@@
   \begin{itemize}
-  \item Ideally, your figure is the same aspect as the frame \texttt{4:3} or \texttt{16:9} or else there will be white space in one of the directions.
+  \item Ideally, your figure is the same aspect as the frame (\texttt{4:3} or \texttt{16:9}) or else there will be white space in one of the directions.
   \end{itemize}
@@
 \begin{frame}{Figure}{}
+  The \texttt{adjustbox} environment helps resize figures/tables
+
+  \medskip
   \begin{adjustbox}{width = 0.7\textwidth, center}
@@
 
-    \note{0.8\textwidth}{Using R base dataframe \texttt{attitude}. R base dataframe attitude. R base dataframe attitude.}
+    \note{0.8\textwidth}{Using R base dataframe \texttt{attitude}. I use my custom \texttt{\textbackslash note} command for notes}
   \end{table}
 
-  \bottomleft{\hyperlink{main1}{\beamerreturnbutton{Back}}}
+  \bottomleft{
+    \hyperlink{main1}{\beamerreturnbutton{Back}}}
   % \bottomright{\hyperlink{main1}{\beamerreturnbutton{Back}}}

### 2023-10-26 latex-slides/figures/plot_did2s_retail_slides.tex
Use real figure for slides

% Created by tikzDevice version 0.12.4 on 2023-10-26 11:29:03
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (722.70,406.52);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,406.52);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( -0.00,  0.00) rectangle (722.70,406.52);
\end{scope}
\begin{scope}
\path[clip] ( 77.13, 37.33) rectangle (706.70,364.33);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 77.13, 37.33) rectangle (706.70,364.33);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 77.13, 81.92) --
	(706.70, 81.92);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 77.13,141.38) --
	(706.70,141.38);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 77.13,200.83) --
	(706.70,200.83);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 77.13,260.29) --
	(706.70,260.29);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 77.13,319.74) --
	(706.70,319.74);

\path[draw=drawColor,line width= 0.4pt,line join=round] (223.11, 37.33) --
	(223.11,364.33);

\path[draw=drawColor,line width= 0.4pt,line join=round] (383.88, 37.33) --
	(383.88,364.33);

\path[draw=drawColor,line width= 0.4pt,line join=round] (544.64, 37.33) --
	(544.64,364.33);

\path[draw=drawColor,line width= 0.4pt,line join=round] (705.41, 37.33) --
	(705.41,364.33);

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 77.13, 52.19) --
	(706.70, 52.19);

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 77.13,111.65) --
	(706.70,111.65);

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 77.13,171.10) --
	(706.70,171.10);

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 77.13,230.56) --
	(706.70,230.56);

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 77.13,290.01) --
	(706.70,290.01);

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 77.13,349.47) --
	(706.70,349.47);

\path[draw=drawColor,line width= 0.8pt,line join=round] (142.72, 37.33) --
	(142.72,364.33);

\path[draw=drawColor,line width= 0.8pt,line join=round] (303.49, 37.33) --
	(303.49,364.33);

\path[draw=drawColor,line width= 0.8pt,line join=round] (464.26, 37.33) --
	(464.26,364.33);

\path[draw=drawColor,line width= 0.8pt,line join=round] (625.03, 37.33) --
	(625.03,364.33);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.9pt,dash pattern=on 4pt off 4pt ,line join=round] (-552.44,171.10) -- (1336.27,171.10);
\definecolor{drawColor}{RGB}{154,36,21}

\path[draw=drawColor,line width= 2.3pt,line join=round] (-552.44, 60.72) -- (1336.27,296.63);
\definecolor{fillColor}{RGB}{154,36,21}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.57,117.31) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.65,131.01) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (142.72,128.70) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.80,133.31) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (174.88,144.08) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (190.95,146.58) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (207.03,153.07) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (223.11,158.01) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (239.18,160.98) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (255.26,161.49) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (271.34,163.00) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (287.41,164.09) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (303.49,167.17) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (319.57,168.02) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (335.65,171.37) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (351.72,174.56) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (367.80,175.65) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (383.88,178.84) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (399.95,182.12) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (416.03,182.44) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (432.11,183.11) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (448.18,183.79) circle (  3.57);
\definecolor{drawColor}{RGB}{16,120,149}
\definecolor{fillColor}{RGB}{16,120,149}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (464.26,198.30) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (480.34,217.26) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (496.41,217.48) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (512.49,218.41) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (528.57,221.68) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (544.64,228.53) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (560.72,235.70) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (576.80,246.00) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (592.88,252.69) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (608.95,253.73) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (625.03,262.88) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (641.11,264.33) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (657.18,263.49) circle (  3.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (673.26,282.74) circle (  3.57);
\definecolor{drawColor}{RGB}{154,36,21}

\path[draw=drawColor,line width= 2.3pt,line join=round] (105.75,162.70) --
	(115.39,162.70);

\path[draw=drawColor,line width= 2.3pt,line join=round] (110.57,162.70) --
	(110.57, 69.77);

\path[draw=drawColor,line width= 2.3pt,line join=round] (105.75, 69.77) --
	(115.39, 69.77);

\path[draw=drawColor,line width= 2.3pt,line join=round] (121.82,160.92) --
	(131.47,160.92);

\path[draw=drawColor,line width= 2.3pt,line join=round] (126.65,160.92) --
	(126.65,102.86);

\path[draw=drawColor,line width= 2.3pt,line join=round] (121.82,102.86) --
	(131.47,102.86);

\path[draw=drawColor,line width= 2.3pt,line join=round] (137.90,148.24) --
	(147.55,148.24);

\path[draw=drawColor,line width= 2.3pt,line join=round] (142.72,148.24) --
	(142.72,109.27);

\path[draw=drawColor,line width= 2.3pt,line join=round] (137.90,109.27) --
	(147.55,109.27);

\path[draw=drawColor,line width= 2.3pt,line join=round] (153.98,149.75) --
	(163.62,149.75);

\path[draw=drawColor,line width= 2.3pt,line join=round] (158.80,149.75) --
	(158.80,116.33);

\path[draw=drawColor,line width= 2.3pt,line join=round] (153.98,116.33) --
	(163.62,116.33);

\path[draw=drawColor,line width= 2.3pt,line join=round] (170.05,156.09) --
	(179.70,156.09);

\path[draw=drawColor,line width= 2.3pt,line join=round] (174.88,156.09) --
	(174.88,130.94);

\path[draw=drawColor,line width= 2.3pt,line join=round] (170.05,130.94) --
	(179.70,130.94);

\path[draw=drawColor,line width= 2.3pt,line join=round] (186.13,155.38) --
	(195.78,155.38);

\path[draw=drawColor,line width= 2.3pt,line join=round] (190.95,155.38) --
	(190.95,137.10);

\path[draw=drawColor,line width= 2.3pt,line join=round] (186.13,137.10) --
	(195.78,137.10);

\path[draw=drawColor,line width= 2.3pt,line join=round] (202.21,159.81) --
	(211.85,159.81);

\path[draw=drawColor,line width= 2.3pt,line join=round] (207.03,159.81) --
	(207.03,146.44);

\path[draw=drawColor,line width= 2.3pt,line join=round] (202.21,146.44) --
	(211.85,146.44);

\path[draw=drawColor,line width= 2.3pt,line join=round] (218.28,163.34) --
	(227.93,163.34);

\path[draw=drawColor,line width= 2.3pt,line join=round] (223.11,163.34) --
	(223.11,152.98);

\path[draw=drawColor,line width= 2.3pt,line join=round] (218.28,152.98) --
	(227.93,152.98);

\path[draw=drawColor,line width= 2.3pt,line join=round] (234.36,165.64) --
	(244.01,165.64);

\path[draw=drawColor,line width= 2.3pt,line join=round] (239.18,165.64) --
	(239.18,155.44);

\path[draw=drawColor,line width= 2.3pt,line join=round] (234.36,155.44) --
	(244.01,155.44);

\path[draw=drawColor,line width= 2.3pt,line join=round] (250.44,166.18) --
	(260.08,166.18);

\path[draw=drawColor,line width= 2.3pt,line join=round] (255.26,166.18) --
	(255.26,156.61);

\path[draw=drawColor,line width= 2.3pt,line join=round] (250.44,156.61) --
	(260.08,156.61);

\path[draw=drawColor,line width= 2.3pt,line join=round] (266.51,166.69) --
	(276.16,166.69);

\path[draw=drawColor,line width= 2.3pt,line join=round] (271.34,166.69) --
	(271.34,159.06);

\path[draw=drawColor,line width= 2.3pt,line join=round] (266.51,159.06) --
	(276.16,159.06);

\path[draw=drawColor,line width= 2.3pt,line join=round] (282.59,167.77) --
	(292.24,167.77);

\path[draw=drawColor,line width= 2.3pt,line join=round] (287.41,167.77) --
	(287.41,160.78);

\path[draw=drawColor,line width= 2.3pt,line join=round] (282.59,160.78) --
	(292.24,160.78);

\path[draw=drawColor,line width= 2.3pt,line join=round] (298.67,170.88) --
	(308.31,170.88);

\path[draw=drawColor,line width= 2.3pt,line join=round] (303.49,170.88) --
	(303.49,163.70);

\path[draw=drawColor,line width= 2.3pt,line join=round] (298.67,163.70) --
	(308.31,163.70);

\path[draw=drawColor,line width= 2.3pt,line join=round] (314.75,171.61) --
	(324.39,171.61);

\path[draw=drawColor,line width= 2.3pt,line join=round] (319.57,171.61) --
	(319.57,164.94);

\path[draw=drawColor,line width= 2.3pt,line join=round] (314.75,164.94) --
	(324.39,164.94);

\path[draw=drawColor,line width= 2.3pt,line join=round] (330.82,174.39) --
	(340.47,174.39);

\path[draw=drawColor,line width= 2.3pt,line join=round] (335.65,174.39) --
	(335.65,168.62);

\path[draw=drawColor,line width= 2.3pt,line join=round] (330.82,168.62) --
	(340.47,168.62);

\path[draw=drawColor,line width= 2.3pt,line join=round] (346.90,177.52) --
	(356.55,177.52);

\path[draw=drawColor,line width= 2.3pt,line join=round] (351.72,177.52) --
	(351.72,171.64);

\path[draw=drawColor,line width= 2.3pt,line join=round] (346.90,171.64) --
	(356.55,171.64);

\path[draw=drawColor,line width= 2.3pt,line join=round] (362.98,178.29) --
	(372.62,178.29);

\path[draw=drawColor,line width= 2.3pt,line join=round] (367.80,178.29) --
	(367.80,173.12);

\path[draw=drawColor,line width= 2.3pt,line join=round] (362.98,173.12) --
	(372.62,173.12);

\path[draw=drawColor,line width= 2.3pt,line join=round] (379.05,181.66) --
	(388.70,181.66);

\path[draw=drawColor,line width= 2.3pt,line join=round] (383.88,181.66) --
	(383.88,176.09);

\path[draw=drawColor,line width= 2.3pt,line join=round] (379.05,176.09) --
	(388.70,176.09);

\path[draw=drawColor,line width= 2.3pt,line join=round] (395.13,185.19) --
	(404.78,185.19);

\path[draw=drawColor,line width= 2.3pt,line join=round] (399.95,185.19) --
	(399.95,179.09);

\path[draw=drawColor,line width= 2.3pt,line join=round] (395.13,179.09) --
	(404.78,179.09);

\path[draw=drawColor,line width= 2.3pt,line join=round] (411.21,185.95) --
	(420.85,185.95);

\path[draw=drawColor,line width= 2.3pt,line join=round] (416.03,185.95) --
	(416.03,178.80);

\path[draw=drawColor,line width= 2.3pt,line join=round] (411.21,178.80) --
	(420.85,178.80);

\path[draw=drawColor,line width= 2.3pt,line join=round] (427.28,187.38) --
	(436.93,187.38);

\path[draw=drawColor,line width= 2.3pt,line join=round] (432.11,187.38) --
	(432.11,178.50);

\path[draw=drawColor,line width= 2.3pt,line join=round] (427.28,178.50) --
	(436.93,178.50);

\path[draw=drawColor,line width= 2.3pt,line join=round] (443.36,189.28) --
	(453.01,189.28);

\path[draw=drawColor,line width= 2.3pt,line join=round] (448.18,189.28) --
	(448.18,178.73);

\path[draw=drawColor,line width= 2.3pt,line join=round] (443.36,178.73) --
	(453.01,178.73);
\definecolor{drawColor}{RGB}{16,120,149}

\path[draw=drawColor,line width= 2.3pt,line join=round] (459.44,205.22) --
	(469.08,205.22);

\path[draw=drawColor,line width= 2.3pt,line join=round] (464.26,205.22) --
	(464.26,191.77);

\path[draw=drawColor,line width= 2.3pt,line join=round] (459.44,191.77) --
	(469.08,191.77);

\path[draw=drawColor,line width= 2.3pt,line join=round] (475.51,225.18) --
	(485.16,225.18);

\path[draw=drawColor,line width= 2.3pt,line join=round] (480.34,225.18) --
	(480.34,209.57);

\path[draw=drawColor,line width= 2.3pt,line join=round] (475.51,209.57) --
	(485.16,209.57);

\path[draw=drawColor,line width= 2.3pt,line join=round] (491.59,226.39) --
	(501.24,226.39);

\path[draw=drawColor,line width= 2.3pt,line join=round] (496.41,226.39) --
	(496.41,208.94);

\path[draw=drawColor,line width= 2.3pt,line join=round] (491.59,208.94) --
	(501.24,208.94);

\path[draw=drawColor,line width= 2.3pt,line join=round] (507.67,228.59) --
	(517.31,228.59);

\path[draw=drawColor,line width= 2.3pt,line join=round] (512.49,228.59) --
	(512.49,208.07);

\path[draw=drawColor,line width= 2.3pt,line join=round] (507.67,208.07) --
	(517.31,208.07);

\path[draw=drawColor,line width= 2.3pt,line join=round] (523.74,233.37) --
	(533.39,233.37);

\path[draw=drawColor,line width= 2.3pt,line join=round] (528.57,233.37) --
	(528.57,210.17);

\path[draw=drawColor,line width= 2.3pt,line join=round] (523.74,210.17) --
	(533.39,210.17);

\path[draw=drawColor,line width= 2.3pt,line join=round] (539.82,240.83) --
	(549.47,240.83);

\path[draw=drawColor,line width= 2.3pt,line join=round] (544.64,240.83) --
	(544.64,215.37);

\path[draw=drawColor,line width= 2.3pt,line join=round] (539.82,215.37) --
	(549.47,215.37);

\path[draw=drawColor,line width= 2.3pt,line join=round] (555.90,249.95) --
	(565.54,249.95);

\path[draw=drawColor,line width= 2.3pt,line join=round] (560.72,249.95) --
	(560.72,220.95);

\path[draw=drawColor,line width= 2.3pt,line join=round] (555.90,220.95) --
	(565.54,220.95);

\path[draw=drawColor,line width= 2.3pt,line join=round] (571.98,261.80) --
	(581.62,261.80);

\path[draw=drawColor,line width= 2.3pt,line join=round] (576.80,261.80) --
	(576.80,229.34);

\path[draw=drawColor,line width= 2.3pt,line join=round] (571.98,229.34) --
	(581.62,229.34);

\path[draw=drawColor,line width= 2.3pt,line join=round] (588.05,270.16) --
	(597.70,270.16);

\path[draw=drawColor,line width= 2.3pt,line join=round] (592.88,270.16) --
	(592.88,235.66);

\path[draw=drawColor,line width= 2.3pt,line join=round] (588.05,235.66) --
	(597.70,235.66);

\path[draw=drawColor,line width= 2.3pt,line join=round] (604.13,272.25) --
	(613.78,272.25);

\path[draw=drawColor,line width= 2.3pt,line join=round] (608.95,272.25) --
	(608.95,234.88);

\path[draw=drawColor,line width= 2.3pt,line join=round] (604.13,234.88) --
	(613.78,234.88);

\path[draw=drawColor,line width= 2.3pt,line join=round] (620.21,285.04) --
	(629.85,285.04);

\path[draw=drawColor,line width= 2.3pt,line join=round] (625.03,285.04) --
	(625.03,240.57);

\path[draw=drawColor,line width= 2.3pt,line join=round] (620.21,240.57) --
	(629.85,240.57);

\path[draw=drawColor,line width= 2.3pt,line join=round] (636.28,292.33) --
	(645.93,292.33);

\path[draw=drawColor,line width= 2.3pt,line join=round] (641.11,292.33) --
	(641.11,237.46);

\path[draw=drawColor,line width= 2.3pt,line join=round] (636.28,237.46) --
	(645.93,237.46);

\path[draw=drawColor,line width= 2.3pt,line join=round] (652.36,298.77) --
	(662.01,298.77);

\path[draw=drawColor,line width= 2.3pt,line join=round] (657.18,298.77) --
	(657.18,228.92);

\path[draw=drawColor,line width= 2.3pt,line join=round] (652.36,228.92) --
	(662.01,228.92);

\path[draw=drawColor,line width= 2.3pt,line join=round] (668.44,332.90) --
	(678.08,332.90);

\path[draw=drawColor,line width= 2.3pt,line join=round] (673.26,332.90) --
	(673.26,232.32);

\path[draw=drawColor,line width= 2.3pt,line join=round] (668.44,232.32) --
	(678.08,232.32);

\path[] ( 77.13, 37.33) rectangle (706.70,364.33);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,406.52);
\definecolor{drawColor}{gray}{0.40}

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 77.13, 37.33) --
	( 77.13,364.33);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,406.52);
\definecolor{drawColor}{gray}{0.13}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.60] at ( 69.93, 46.68) {-0.2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.60] at ( 69.93,106.14) {-0.1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.60] at ( 69.93,165.59) {0.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.60] at ( 69.93,225.05) {0.1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.60] at ( 69.93,284.50) {0.2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  1.60] at ( 69.93,343.96) {0.3};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,406.52);
\definecolor{drawColor}{gray}{0.40}

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 73.13, 52.19) --
	( 77.13, 52.19);

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 73.13,111.65) --
	( 77.13,111.65);

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 73.13,171.10) --
	( 77.13,171.10);

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 73.13,230.56) --
	( 77.13,230.56);

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 73.13,290.01) --
	( 77.13,290.01);

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 73.13,349.47) --
	( 77.13,349.47);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,406.52);
\definecolor{drawColor}{gray}{0.40}

\path[draw=drawColor,line width= 0.8pt,line join=round] ( 77.13, 37.33) --
	(706.70, 37.33);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,406.52);
\definecolor{drawColor}{gray}{0.40}

\path[draw=drawColor,line width= 0.8pt,line join=round] (142.72, 33.33) --
	(142.72, 37.33);

\path[draw=drawColor,line width= 0.8pt,line join=round] (303.49, 33.33) --
	(303.49, 37.33);

\path[draw=drawColor,line width= 0.8pt,line join=round] (464.26, 33.33) --
	(464.26, 37.33);

\path[draw=drawColor,line width= 0.8pt,line join=round] (625.03, 33.33) --
	(625.03, 37.33);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,406.52);
\definecolor{drawColor}{gray}{0.13}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.60] at (142.72, 19.11) {-20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.60] at (303.49, 19.11) {-10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.60] at (464.26, 19.11) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.60] at (625.03, 19.11) {10};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,406.52);
\definecolor{drawColor}{gray}{0.27}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.06] at ( 30.16,200.83) {Estimated Effect};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (722.70,406.52);
\definecolor{drawColor}{gray}{0.27}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  2.06] at ( 16.00,376.33) {\bfseries Estimated impact of Walmart on Local Retail Employment};
\end{scope}
\end{tikzpicture}

### 2023-10-26 latex-slides/slides.tex
Use real figure for slides

@@
     \begin{column}{.54\textwidth}
-      \includegraphics[width=\textwidth]{img/kanagawa.jpg}
+      \includegraphics[width=\textwidth]{figures/plot_did2s_retail_slides.pdf}
     \end{column}
@@
 % or else it will have white space
-\imageframe{img/kanagawa_16_9.png}
+\imageframe{figures/plot_did2s_retail_slides.pdf}
 
@@
 
-\begin{frame}{Figure}{}
-  The \texttt{adjustbox} environment helps resize figures/tables
-
-  \medskip
-  \begin{adjustbox}{width = 0.7\textwidth, center}
-    \includegraphics{img/kanagawa_16_9.png}
+\begin{frame}{Figure}
+  \begin{adjustbox}{width = 0.75\textwidth, center}
+    \includegraphics{figures/plot_did2s_retail_slides.pdf}
   \end{adjustbox}
+  \note{The \texttt{adjustbox} environment helps resize figures/tables}
 \end{frame}

### 2023-10-26 latex-slides/slides.tex
Update table to better highlight features

@@
 
-  \medskip
+  \bigskip
   \begin{table}[h]
     \centering
-    \begin{tabular}{lc}
+    \begin{tabular}{l cc}
       \toprule
-      & (1) \\
+      & (1) & (2) \\
       \midrule
-      \rowcolor<2>{alice!15!white}Treatment dummy & \cellcolor<1>{accent!15!white} 0.0694* \\
-      \rowcolor<2>{alice!15!white}& (0.0401) \\
-      \rowcolor<3>{alice!15!white} Constant & -1.2238*** \\
-      \rowcolor<3>{alice!15!white} & (0.0764)  \\
+      Treatment dummy & \cellcolor<1>{accent!15!white} 0.0694* & \cellcolor<2>{accent!15!white} 0.0713** \\
+      & (0.0401) & (0.0381) \\
       \hline
-      Observations & 1,673  \\
-      R-squared & 0.0401 \\
-
+      \rowcolor<3>{accent!15!white} State Fixed Effects & & $\checkmark$ \\
+      Observations & 1,673 & 1,673 \\
       \bottomrule
@@
 
-        \only<1>{
+        \only<2>{
           \marktopleft{ex1}Handling of Complaints & 0.692$^{***}$& 0.682$^{***}$ \\ 
@@
         }
-        \only<2>{
+        \only<1>{
           Handling of Complaints & 0.692$^{***}$& 0.682$^{***}$ \\ 

### 2024-01-19 latex-article/article.tex
Add biblatex option
Fix enumerate subitem and subsubitem color

@@
 \usepackage{math}
+\addbibresource{references.bib}
 
@@
 \author{
-  Author One\thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.} 
+  Author One%
+  \thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.} 
   \ and 
-  Author Two\thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.}
+  Author Two%
+  \thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.}
 }
@@
 I tried to make the theme minimal and beautiful while able to do all the things that I want it to do.
-These include making it easy to make figures/tables with notes; have powerful math commands; have nice readable typography; make co-authoring in a document easy; have a nice looking bibliography; and make appendices easy.\kyle{I'm including this comment for coauthors.
+These include making it easy to make figures/tables with notes; have powerful math commands; have nice readable typography; make co-authoring in a document easy; have a nice looking bibliography; and make appendices easy.
+\kyle{I'm including this comment for coauthors.
 If I switch above to \texttt{togglefalse}, this will dissapear.} I'll show off these things, but make sure to check the source code alongside to see how simple it is to typset with this.
@@
 \newpage
-\bibliography{references.bib}
+% \bibliography{references.bib}
+\printbibliography
 % ------------------------------------------------------------------------------

### 2024-01-26 pandoc-template/article.qmd

---
title: "This is a test" 
author: "Joshua F. Allen"
date: "`r format(Sys.time(), '%F')`"
format:
 #docx:
  #reference-doc: reference.docx
 pdf:
    template: template.tex
    toc: false
bibliography: ref/ref.bib
fontsize: 12pt
mainfont: Lato
link-citations: yes
linkcolor: dark-maroon
urlcolor: dark-maroon
indent: true
geometry: margin=2cm 
reference-section-title: References
---
# Section
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum @angristMostlyHarmlessEconometrics2009.

# Empirical Section

## Identification Strategy

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum [@acemogluColonialOriginsComparative2001]

### 2024-07-04 latex-article/article.tex
Automate thumbnails for readme (h/t @andrewheiss)

@@
 \documentclass[12pt]{article}
-\usepackage{paper}
-\usepackage{math}
+\usepackage{paper,math}
 \addbibresource{references.bib}
 
-\title{Example Paper\thanks{\acknlowledgements}}
+\title{Example Paper Title\thanks{\acknlowledgements}}
 \author{
-  Author One%
-  \thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.} 
-  \ and 
-  Author Two%
-  \thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.}
+  Author One\\ {\itshape\large Affiliation}
+  \and 
+  Author Two\\ {\itshape\large Affiliation}
 }
-\date{\textsc{\today}}
+\date{\today}
 \def\acknlowledgements{%
-  Acknlowedgements
+  One: \href{mailto:email@gmail.com}{email@gmail.com}. 
+  Two: \href{mailto:email@gmail.com}{email@gmail.com}. 
+  Acknlowedgements start here
+}
+\hypersetup{
+  pdftitle = {Example Paper Title},
+  pdfauthor = {Author One, Author Two},
 }
@@
   \par~\par\noindent
-  {\color{asher}JEL-Classification:} ...
+  {\color{zinc700}Keywords:} ...
   \par\noindent
-  {\color{asher}Keywords:} ...
+  {\color{zinc700}JEL-Classification:} ...
   \par\vspace{-2.5mm}
 \end{abstract}
-
 \newpage
@@
 These include making it easy to make figures/tables with notes; have powerful math commands; have nice readable typography; make co-authoring in a document easy; have a nice looking bibliography; and make appendices easy.
-\kyle{I'm including this comment for coauthors.
-If I switch above to \texttt{togglefalse}, this will dissapear.} I'll show off these things, but make sure to check the source code alongside to see how simple it is to typset with this.
+I'll show off these things, but make sure to check the source code alongside to see how simple it is to typset with this. 
+\kyle{I'm including this comment for coauthors. If I switch above to \texttt{togglefalse}, this will dissapear.}
 
-See below for \autoref{thm:residue_thm}, the regression specification (\autoref{eq:fe_reg}), \autoref{tab:summ_stat}, \autoref{fig:event_timing}, appendix \autoref{tab:reg1}.
+See below for \autoref{thm:residue_thm}, the regression specification (\ref{eq:fe_reg}), \autoref{tab:summ_stat}, \autoref{fig:event_timing}, appendix \autoref{tab:reg1}.
 Of course, make sure to touch up on your micro theory with \citet{mas1995microeconomic}.
@@
 $$\P \quad \P[i] \quad \P{X_i} \quad \P[i]{D_i} \quad \P{\bar{X}_n > \bar{X}}{\mu = \mu_0} \quad \P[\mu]{X}{D = 1}$$
-$$\cov{X_n, Y_n} \quad \var[i](\bar{X}_n)$$
+$$\cov{X_n, Y_n} \quad \var[i](\bar{X}_n) \quad \diag{x_i}$$
 
@@
 \newpage
-% \bibliography{references.bib}
 \printbibliography
+% \bibliography{references.bib} % Uncomment this if using `natbib`
 % ------------------------------------------------------------------------------
@@
 % ------------------------------------------------------------------------------
-\newpage
-\appendix
+\newpage~\appendix
 % ------------------------------------------------------------------------------
@@
 
+\citet{mas1995microeconomic}
+
 % ------------------------------------------------------------------------------
@@
 
-In this table example, the table is narrower than textwidth, so I adjust the \texttt{\textbackslash note} width.
+The main regression equation is 
+\begin{equation}
+  y_i = \bm{X}_i \beta + u_i.
+\end{equation}
+
+Results are presented in \autoref{tab:reg1}. In this table example, the table is narrower than textwidth, so I adjust the \texttt{\textbackslash note} width.
 

### 2024-07-04 latex-slides/slides.tex
Small changes
Small update to table of contents
Automate thumbnails for readme (h/t @andrewheiss)

@@
 \usepackage{slides,math}
-% \geometry{paperwidth=168mm,paperheight=94.5mm}
 
-% Define `accent`/`accent2` colors for theme customization
-% I recommend changing the top slider on this: 
-% https://hslpicker.com/#1e9400
-\definecolor{accent}{HTML}{006896}
-\definecolor{accent2}{HTML}{940034}
+% Optionally define `accent`/`accent2` colors for theme customization
+% I recommend changing the top slider on this: https://hslpicker.com/#1e9400
+\definecolor{accent}{HTML}{940034}
+\definecolor{accent2}{HTML}{006896}
 
@@
 \addbibresource{references.bib}
+
 \begin{document}
@@
 
-% \vspace{2.5mm}
-% {\footnotesize $^*$ A bit of extra info here. Add an asterich to title or author}
+% \bottomleft{\footnotesize $^*$A bit of extra info here. Add an asterich to title or author}
 \end{frame}
@@
 
-\begin{frame}{Components}{Bullet Points \& Button}\label{main1}
+\begin{frame}{Components}\label{main1}
   This section highlights commonly used components and their theming
@@
     \beamergotobutton{Button 2} 
-    \beamergotobutton{Button 3}
   }
@@
   \begin{columns}[T]
-    \begin{column}{.54\textwidth}
+    \begin{column}{.6\textwidth}
       \includegraphics[width=\textwidth]{figures/plot_did2s_retail_slides.pdf}
@@
     \hfill
-    \begin{column}{.46\textwidth}
+    \begin{column}{.4\textwidth}
       \begin{itemize}
@@
   \bigskip
-  \begin{table}[h]
-    \centering
+  \begin{center}
+    {\footnotesize\textsc{Outcome:} Log of Real Per Capita Income \\}
+
     \begin{tabular}{l cc}
@@
     \end{tabular}
-  \end{table}
+  \end{center}
 \end{frame}
@@
   \begin{column}{.4\textwidth}
+    \tabletitle{Job Satisfaction Score}
+
     \begin{adjustbox}{max width = \textwidth, center}

### 2024-07-04 referee-response/responses.tex
Make referee response document simpler
Automate thumbnails for readme (h/t @andrewheiss)

@@
 
-% (hide by switching to `\boolfalse`)
-\booltrue{INCLUDETODOS}
-
 % Reference main document ------------------------------------------------------
 % Note: I compile to `auxiliary/` to avoid cluttering the main directory. You might neeed to delete `auxiliary/`
-% \usepackage{xr}
+% Note: The numbering of the main document is colored, but not clickable which is kind of confusing. Not sure if I like this approach or not
+% \usepackage{xr,xr-hyper}
 % \externaldocument[main-]{auxiliary/article}
@@
 
-\noindent Thank you for the additional suggestions. The reviewer's comment is marked with a left border. Our responses follow below each comment.
+\noindent We would like to thank the referees for their time and detailed feedback on our paper.
+We have done our best to respond to each and every comment.
+Below, the reviewer's comment is marked with a left border.
+Our responses follow below each comment.
 
-\section*{Summary of Revisions}
+\section{Summary of Revisions}
+
+The major changes in this draft include ....
 
 % ------------------------------------------------------------------------------
-\NewRef{Referee 1}{R1}
+\vspace*{\bigskipamount}\NewRef{Referee 1}{R1}
+% ------------------------------------------------------------------------------
+
+\begin{refcomment}
+  Full text of the referee's comment. It will automatically create a \texttt{\textbackslash subsection} with the comment number.
+\end{refcomment}
+
+\kyle{
+  Thoughts / plan of action. These can be hidden by toggling \texttt{INCLUDETODOS} to \texttt{\textbackslash boolfalse}. 
+}
+
+Response
+
+\begin{refcomment}
+  Comment 
+\end{refcomment}
+
+Response
+
+% ------------------------------------------------------------------------------
+\vspace*{\bigskipamount}\NewRef{Referee 2}{R2}
 % ------------------------------------------------------------------------------
@@
 
-\begin{todos}
-  Thoughts / plan of action. These can be hidden by toggling \texttt{INCLUDETODOS} to \texttt{\textbackslash boolfalse}. 
-\end{todos}
-
-\begin{response}
-  Response
-\end{response}
-
-\begin{refcomment}
-  Comment 
-\end{refcomment}
-
-\begin{todos}
-  Thoughts / plan of action. 
-\end{todos}
-
-\begin{response}
-  Response
-\end{response}
-
 % ------------------------------------------------------------------------------
-\NewRef{Referee 2}{R2}
+\newpage
+\section*{How to use this template}
 % ------------------------------------------------------------------------------
 
+There are two main commands provided by the document.
+First, for each referee, a  \texttt{\textbackslash section} is created using the \texttt{\textbackslash NewRef\{Name\}\{Abbreviation\}} command.
+The \texttt{Name} is what will be displayed by the section and \texttt{Abbreviation} is what will label each comment.
+
+Within each section, each referee comment will be written using \texttt{\textbackslash begin\{refcomment\} ...
+\textbackslash end\{refcomment\}}.
+This command automatically numbers the comments and labels it using the \texttt{Abbreviation} from the \texttt{NewRef} declaration.
+Responses to the comment should go below the \texttt{refcomment} block.
+
 \end{document}

### 2024-07-04 render.R

@@ -1,0 +1,100 @@
+#' Credit to https://github.com/andrewheiss/hikmah-academic-quarto/tree/main
+
+# %%
+library(tidyverse)
+library(magick)
+library(fs)
+
+file_delete(dir_ls("thumbnails/"))
+dir_create("thumbnails/")
+
+# %%
+# @param tile Number of images per row
+thumbify <- function(to_convert, which_pages = TRUE, tile = 3) {
+  template_name <- path_split(to_convert)[[1]][1]
+
+  # Convert each rendered PDF to a collage and save as PNG
+  pages <- image_read_pdf(to_convert)
+
+  if (isTRUE(which_pages)) {
+    which_pages <- seq_len(length(pages))
+  }
+  pages_split <- split(which_pages, ceiling(seq_along(which_pages) / tile))
+
+  images <- c()
+  for (i in seq_along(pages_split)) {
+    curr_pages <- pages_split[[i]]
+    thumbnail_name <- path("thumbnails/", sprintf("%s-%s.png", template_name, i))
+
+    pages[curr_pages] |>
+      image_montage(
+        geometry = "x2000+25+35",
+        tile = tile,
+        bg = "grey92",
+        shadow = FALSE
+      ) |>
+      image_convert(format = "png") |>
+      image_write(thumbnail_name)
+
+    images <- c(images, thumbnail_name)
+  }
+
+  return(images)
+}
+
+# %%
+article_images <- thumbify(
+  "latex-article/article.pdf",
+  which_pages = TRUE,
+  tile = 3
+)
+slides_images <- thumbify(
+  "latex-slides/slides.pdf",
+  which_pages = c(1, 3, 9, 14, 18, 21),
+  tile = 3
+)
+response_images <- thumbify(
+  "referee-response/responses.pdf",
+  which_pages = TRUE,
+  tile = 3
+)
+
+
+# %%
+#| label: 'Create README.md images'
+readme <- xfun::read_utf8("README.md")
+
+article_md <- sprintf(
+  '[<img src="%s" style="width: 100.0%%" />](%s)',
+  article_images, article_images
+)
+insert_idx <- which(str_detect(readme, "<!--\\s+latex-article\\s+-->"))
+readme <- c(
+  readme[1:insert_idx[1]],
+  article_md,
+  readme[insert_idx[2]:length(readme)]
+)
+
+slides_md <- sprintf(
[…]

### 2024-09-22 render.R
Update README.md

@@ -50,7 +50,7 @@ article_images <- thumbify(
 )
 slides_images <- thumbify(
   "latex-slides/slides.pdf",
-  which_pages = c(1, 3, 9, 14, 18, 21),
+  which_pages = c(1, 3,11, 14, 18, 21),
   tile = 3
 )
 response_images <- thumbify(

### 2024-10-04 latex-slides/slides.tex
Add ability to use `lstlisting` for code blocks in slides
Add `page cs` coordinate system for overlays

@@
 
+\begin{frame}{Customizing template}
+  At the top of the template is two accent color definitions. Change these and they should populate throughout the slides.
+\end{frame}
+
 % ------------------------------------------------------------------------------
@@
   \begin{itemize}
-    \item Can emphasize with \alert{the alert command}
+    \item Can emphasize with \alert{the alert command} which uses the \texttt{accent2} color
 
@@
 
-\begin{frame}{Components}{Numbered Lists}
+\begin{frame}{Numbered Lists}
   You can also use numbered items that look a bit more professional
@@
 
-\begin{frame}{Components}{Citations}
+\begin{frame}{Citations}
   Topic 1: Spatial Frictions
@@
 
-\begin{frame}{Components}{Blocks}
+\begin{frame}{Colors}
+  I have a set of colors that I use:
+
+  \navy{navy},
+  \raspberry{raspberry},
+  \cranberry{cranberry},
+  \orange{orange},
+  \purple{purple},
+  \blue{blue},
+  \green{green},
+  \rose{rose}, and 
+  \yellow{yellow}
+
+  \bigskip
+  If you want to color text with them, use \texttt{\textbackslash colorname\{...\}}
+\end{frame}
+
+\begin{frame}{Color boxes}
+  You can also use color boxes. Some of the colors look ugly when made lighter, so I won't show them:
+
+  \bgNavy{bgNavy},
+  \bgRaspberry{bgRaspberry},
+  \bgCranberry{bgCranberry},
+  \bgOrange{bgOrange},
+  \bgPurple{bgPurple},
+  \bgGreen{bgGreen},
+  \bgYellow{bgYellow}
+
+  \bigskip
+  If you want to color text with them, use \texttt{\textbackslash bgColorname\{...\}}
+\end{frame}
+
+\begin{frame}{Highlight Math}
+  Can also highlight in an equation with \texttt{\textbackslash tcbhighmath[colback = bgColor]\{...\}}. If you don't include the brackets, it will default to \texttt{bgRaspberry}.
+
+  $$
+    \int_{ \tcbhighmath[colback = bgNavy]{\Omega} } f(x) \, dx \approx 
+    \frac{\tcbhighmath[colback = bgRaspberry]{ |\Omega| }}{N} 
+    \sum_{i=1}^{N} f( \tcbhighmath[colback = bgPurple]{ X_i } )
+  $$
+\end{frame}
+
+\begin{frame}[fragile]{Code listings}
+  The \texttt{codeblock} environment lets you copy text verbatim. It is important you use \texttt{[fragile]} as a frame option in beamer
+
+\begin{codeblock}
+library(fixest)
+feols(mpg ~ 1, data = mtcars)
+#> OLS estimation, Dep. Var.: mpg
+#> Observations: 32
+#>             Estimate Std. Error t value  Pr(>|t|)    
+#> (Intercept)  20.0906    1.06542 18.8569 < 2.2e-16 ***
+#> ---
+#> Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
+\end{codeblock}
+\end{frame}
+
+\begin{frame}{Blocks}
   \begin{block}{Theorem 1}
@@
 
-\begin{frame}{Components}{Blocks}
+\begin{frame}{Blocks}
+  If you want something more colorful, use \texttt{colornameBlock}
   \begin{purpleBlock}{}
@@
 
-\begin{frame}{Components}{Colors}
-  \navy{Test sentence with \textbackslash navy\{...\}}
-
-  \purple{Test sentence with \textbackslash purple\{...\}}
-
-  \orange{Test sentence with \textbackslash orange\{...\}}
-
-  \teal{Test sentence with \textbackslash teal\{...\}}
-
-  \kelly{Test sentence with \textbackslash kelly\{...\}}
-
-  \ruby{Test sentence with \textbackslash ruby\{...\}}
-
-  \alice{Test sentence with \textbackslash alice\{...\}}
-
-  \daisy{Test sentence with \textbackslash daisy\{...\}}
-
-  \coral{Test sentence with \textbackslash coral\{...\}}
-
-  \cranberry{Test sentence with \textbackslash color\{cranbery\}}
-\end{frame}
-
-\begin{frame}{Components}{Two Columns}
+\begin{frame}{Two Columns}
   \begin{columns}[T]
@@
       \vspace{0pt}
-      {\color{accent}\rule{\linewidth}{2pt}}
+      % {\color{zinc400}\rule{\linewidth}{2pt}}
       Column 1
@@
     \begin{column}{.50\textwidth}
-      {\color{accent}\rule{\linewidth}{2pt}}
+      % {\color{zinc400}\rule{\linewidth}{2pt}}
       Column 2
@@
 
-\begin{frame}{Components}{Two Columns with Figure}
+\begin{frame}{Two Columns with Figure}
   \begin{columns}[T]
@@
     \begin{column}{.4\textwidth}
-      \begin{itemize}
-      \item A point about the figure that is potentially important.
-      \item Another point about the figure that is also potentially important.
-      \end{itemize}
+      A point about the figure that is potentially important.
+
+      \bigskip
+      Another point about the figure that is also potentially important.
     \end{column}
@@
 
+    \bigskip
     \begin{tabular}{l cc}
@@
       \midrule
-      Treatment dummy & \cellcolor<1>{accent!15!white} 0.0694* & \cellcolor<2>{accent!15!white} 0.0713** \\
+      Policy Enacted $= 1$ & \cellcolor<1>{accent!15!white} 0.0694* & \cellcolor<2>{accent!15!white} 0.0713** \\
       & (0.0401) & (0.0381) \\
@@
   \begin{column}{.4\textwidth}
-    \tabletitle{Job Satisfaction Score}
-
     \begin{adjustbox}{max width = \textwidth, center}
@@
 
-% 4:3 ratio for figures
-% or else it will have white space
-\imageframe{figures/plot_did2s_retail_slides.pdf}
-
 \begin{frame}{Figure}{Full-size Figures}
@@
 
+% Try to make figures the correct aspect ratio otherwise white will be filled in around the image
+\imageframe{figures/plot_did2s_retail_slides.pdf}
+
 \begin{frame}{Figure}
+  \begin{figure}
     \begin{adjustbox}{width = 0.75\textwidth, center}
@@
     \end{adjustbox}
-  \note{The \texttt{adjustbox} environment helps resize figures/tables}
+
+    \vspace*{-\medskipamount}
+    \note{0.75\textwidth}{The \texttt{adjustbox} environment helps resize figures/tables}
+  \end{figure}
+\end{frame}
+
+\section{Advanced Tools}
+
+\begin{frame}[fragile]{Overlaying objects}
+  This template provides some tools to make overlaying text / objects over the slides easier (an e.g.
+of this is the \texttt{\textbackslash bottomleft} overlay buttons).
+This feature is heavily inspired from Keenan Crane's excellent slides.
+
+  \bigskip
+  To use this, you can 
+  \begin{codeblock}[tex]
+\begin{tikzpicture}[remember picture, overlay]
+  \node [text width = 0.3\textwidth] at (page cs: x, y)
+\end{tikzpicture}
+  \end{codeblock}
+  where \texttt{x, y} are the x and y coordinates of the slide and are between 0.0 and 1.0.
+
+\end{frame}
+
+\begin{frame}{}
+  \medskip\medskip
+  \parbox[]{0.8\textwidth}{
+
+    \textit{Proof.} First note that, since the $X_i$ are independent,
+    \[
+      \text{Var} \left( \overline{X}_N \right) = \text{Var} \left( \frac{1}{N} \sum_{i=1}^{N} X_i \right) = \frac{1}{N^2} \sum_{i=1}^{N} \text{Var}(X_i) = \frac{\sigma^2}{N}.
+    \]
+
+    From Chebyshev's inequality, we then have
+    \[
+      P\left( |\overline{X}_N - \mu| \geq \varepsilon \right) \leq \frac{\text{Var}[\overline{X}_N]}{\varepsilon^2} = \frac{\sigma^2}{N^2 \varepsilon^2},
+    \]
+    and
+    \[
+      \lim_{N \to \infty} \frac{\sigma^2}{N^2 \varepsilon^2} = 0.
+    \]
+
+  }
+
+  % \devgrid{}
+
+  \begin{tikzpicture}[remember picture, overlay]
+    \coordinate (arrow1_a) at (page cs:0.8, 0.37);
+    \coordinate (arrow1_b) at (page cs:0.7, 0.21);
+    \draw (arrow1_a) edge[zinc500, out = 100, in = 0, line width = 0.6mm, -Stealth] (arrow1_b);
+
+    \coordinate (arrow2_a) at (page cs:0.72, 0.54);
+    \coordinate (arrow2_b) at (page cs:0.57, 0.54);
+    \draw (arrow2_a) edge[zinc500, out = -150, in = -40, line width = 0.6mm, -Stealth] (arrow2_b);
+
+    \node [text width = 0.34\textwidth, rotate = 1] at (page cs:0.8,0.44) {
+      \begin{tcolorbox}[
+        enhanced,
+        width = \textwidth,
+        colback = white,
+        colframe = zinc300, 
+        boxrule = 0.4mm,
+        arc = 0.5mm,
+        % sharp corners, 
+        left = 0.5mm, right = 0.5mm,
+        top = 1mm, bottom = 1mm,
+        fuzzy shadow = {0mm}{-0.5mm}{-1pt}{0.2mm}{zinc300},
+        fontupper = \rmfamily,
+        % drop fuzzy shadow
+      ]
+        \setstretch{1}
+        {\small
+          \textbf{In summary:} averaging reduces variance; 
+          Chebyshev says that random variables with small variance will be close to their mean.
+        }
+      \end{tcolorbox}
+    };
+
+  \end{tikzpicture}
+\end{frame}
+
+\begin{frame}{Example of labelling equations}
+  % \devgrid
+
+  We can use monte carlo simulation to draw $N$ observations from the domain $\Omega$:
+
+  \medskip
+  $$
+    \int_{ \Omega } f(x) \, dx \approx 
+    \frac{\tcbhighmath{ |\Omega| }}{N} 
+    \sum_{i=1}^{N} f( \tcbhighmath{ X_i } )
+  $$
+
+  \begin{tikzpicture}[remember picture, overlay]
+    \node [anchor = south, text width = 0.12\textwidth] at (page cs:0.45,0.375) {
+      \begin{center}
+        \setstretch{0.7}
+        {\footnotesize\color{raspberry} \emph{volume of domain}}
+      \end{center}
+    };
+
+    \node [anchor = north, text width = 0.1\textwidth] at (page cs:0.65,0.41) {
+      \begin{center}
+        \setstretch{0.7}
+        {\footnotesize\color{raspberry} \emph{Draw from $\Omega$}}
+      \end{center}
+    };
+  \end{tikzpicture}
+\end{frame}
+
+\begin{frame}{}
+  \devgrid
+
+  It can be a bit tedious to try and place these elements.
+For that reason, I added \texttt{\textbackslash devgrid} command that will lay every 0.1 unit of the slide.
+Counting will get you in the ball park and manual tweaking will finish the job.
+
+  % Absolute positioned tikzpicture
+  \begin{tikzpicture}[remember picture, overlay]
+    \node[anchor = north west] (topleft)
+      at (page cs:0.0, 0.0) { $\blacksquare$ };
+    \node[anchor = north east] (topright)
+      at (page cs:1.0, 0.0) { $\blacksquare$ };
+    \node[anchor = south west] (bottomleft) 
+      at (page cs:0.0, 1.0) { $\blacksquare$ };
+    \node[anchor = south east] (bottomright) 
+      at (page cs:1.0, 1.0) { $\blacksquare$ };
+  \end{tikzpicture}
 \end{frame}

### 2024-10-04 render.R

@@ -50,13 +50,13 @@ article_images <- thumbify(
 )
 slides_images <- thumbify(
   "latex-slides/slides.pdf",
-  which_pages = c(1, 3,11, 14, 18, 21),
+  which_pages = c(1, 4, 9, 10, 11, 18, 23, 26, 30),
   tile = 3
 )
 response_images <- thumbify(
   "referee-response/responses.pdf",
-  which_pages = TRUE,
-  tile = 3
+  which_pages = c(1, 2),
+  tile = 2
 )
 
 
